### 2024-10-26 Manuscript.qmd
Add files via upload

---
title: "What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses"
author:
  - name: Thomas Reiter
    email: t.reiter@psy.lmu.de
  - name: Philipp Sterner
    email: p.sterner@psy.lmu.de
format: pdf
floatsintext: yes
editor: visual
---

# Introduction

In the social sciences, conjoint analyses are a powerful research design to assess preferences in humans.
Under the popular special case of *forced choice designs*, participants are presented with two options of choice form which they have to choose one, for example certain products in marketing research, or two potential candidates in political research on voting behavior.
The two possible options are characterized by certain *attributes* (also: treatments), which can have different *attribute levels* (treatment levels), for example the attribute color of a car might have levels white, black, and blue.
By randomly mixing the attribute levels and "forcing" participants to choose one of two options across multiple rounds, researchers are able to estimate the relative importance that participants give to certain attribute levels.

Arguably the most often estimated causal quantity in conjoint analyses is the *average marginal component effect* (AMCE).
The AMCE is the effect of a specific attribute level of interest compared to another level of the same attribute, holding equal the joint distribution of all other attributes and averaged over this joint distribution as well as the sampling distribution from the population CITE.
This quantity is estimable by regression models and provides us an effect of an attribute on the probability that a certain option (or profile) will be chosen.
As the name AMCE suggestes, this estimate is an average.
That is, potential differences in effects among participants cannot be considered directly.
However, this *effect heterogeneity* is often of interest, when trying to determine whether an attribute is equally important to all participants regardless of background covariates (e.g., age, gender, education, etc.) or whether there are subgroup differences.
Ultimately, it is a question of generalisation of results to the entire population and, even more advanced, of causal mechanisms in choice behavior.

The simplest approach to take into account potential effect heterogeneity in conjoint analyses is to estimate the AMCE-models in different subgroups, for example a model for all male and female participants.
Altough appealing due to its simplicity, this approach quickly reaches its limits and has additional downsides.
First, it is not clear how to a priori define the subgroups let alone how and where to include certain interactions.
If a continuous covariate age is included in the data, arbitrary splits into distinct groups are necessary.
Potential interaction effects would have to be included manually with the likely chance to miss important ones.
Needless to say, sample sizes in the subgroups are always smaller than in the whole sample as well, increasing the uncertainty in estimations.
This leads to a second issue: conjoint data can quickly become high-dimensional due to many different pairings of different attribute levels (across attributes).
Consequently, there are more combinations of attribute levels (and thus, possible options) that should be presented to participants than there are actual rounds of choosing per participant.
This leads to some kind of "double high-dimensionality issue": there are many different attribute (level) combinations *and* many potential covariates characterizing the participants.
This results in a number of possible interactions that are untractable for classical methods (these interactions correspond to the effect heterogeneity mentioned above).

# New Approaches to Handle Effect Heterogeneity under High-Dimensionality

To remedy the downsides of the "naive" subgroup approach outline above, researchers developed more advanced methods based on machine learning.
Most notable in this regard are (a) an approach based on *Bayesian additive regression trees* (in the following called *cjbart* CITE), (b) an approach based on Bayesian mixture of regularized logistic regressions (*FactorHet* CITE), and (c) a testing approach based on conditional randomization tests (*CRT* CITE).
In this article, we focus on the explanation and demonstration of cjbart.
At the end of this section, we briefly delineate similarities and differences in these three approaches.

The premise of cjbart as introduced by CITE is that there are several *nested causal quantities* underlying the AMCE.
Specifically, the AMCE can be decomposed into an individual-level (i.e., participant-level), round-level, and observation-level marginal component effect (IMCE, RMCE, and OMCE, respectively).
Let us consider *N* individuals choosing between *J* profiles across *K* rounds (where in the simplest case of binary choices $J = 2$).
In each round, an individual *i* is presented with *J* profiles in which the attribute levels of *L* attributes are assigned randomly.
In the final data set, there are $N \times J \times K$ rows and $L + X$ columns (with *X* being the covariates characterizing the individuals).
From these data we now want to estimate the causal parameters of interest, that is, AMCE, IMCE, RMCE, and OMCE.
Nested in the AMCE described above, the IMCE is the change in probability that subject *i* choses a profile given a specific attribute level (compared to a reference category), again averaged over the effects of all other attributes.
This corresponds to subgroup analyses of the AMCE with the convenient addition that the IMCE considers conditional effects based on all possible individual-level covariates.
By inspecting the IMCE, effect heterogeneity due to non-randomized characterisitics (i.e., the covariates) can be identified.
The IMCE further contains the two lower-level quantities RMCE and OMCE.
Because for each participant, there are usually multiple rounds of observations (i.e., choices), the RMCE can be obtained as the effect of an attribute within a specific round *k* of the experiment for a given individual *i*.
Lastly, the OMCE is estimated by additionally conditioning on a specific profile-level (i.e., if $J = 2$, by conditioning on one of the two profiles).
As CITE note, the OMCE does not contain too much substantial information.
It is, however, of statistical importance: assuming the OMCE is an independent random draw from an individual-level distribution, we can aggregate the OMCEs to estimate the IMCEs.

In the following, we explain how the IMCEs are estimated.
IMCEs can be considered the most important quantity for our purpose of investigating effect heterogeneity because it allows us to analyze how attribute importances differ depending on participant covariates.
CITE propose a three-step estimation procedure.

## Step 1: Modeling Potential Heterogeneity

In a first step, potential effect heterogeneity is modeled.
Specifically, some function is estimated that relates the attribute levels of the *L* attributes that were shown to subject *i* in the $k^{th}$ round in profile *j* and the covariate vector $X_i$ to the observed binary outcome $Y_{ijk}$ (which is equal to 1 if the profile was chosen and equal to 0 if it was not chosen).
CITE detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functionial relationship could be used as well.
BART is...

EXPLAIN THREE STEP PROCEDURE OF ESTIMATING OMCES AND THEN IMCES WITH BART.

EXPLAIN HOW RFs ARE USED TO ESTIMATE VIMP

EXPLAIN HOW DTs ARE USED TO INVESTIGATE HETEROGENEITY IN IMCEs AND WHICH COVARIATES ARE DRIVERS

-Vorgeschlagene neue Modelle in der Literatur 
-cjBart
-Idee des Modells/der Modelle 
-weitere Modelle:
	-factorHet + idee kurz
	-CRT + idee kurz
Warum cjBart → das Modell stark machen

# Data, Research Question, and Method
-Die Daten 
-Fragestellung 
-bisherige Forschung

# Results
-Ergebnisse 
cjBart Ergebnisse

# Integration of Results
-Einordnung der Ergebnisse
-Vergleich mit factorHet
-Vergleich mit “normaler” Subgruppen Analyse

# Discussion
Discussion & Limitations
-Tuning 
-Wie viele Covariates (inference vs. exploration)
-Stabilität

# Conclusion

### 2024-10-26 Manuscript.qmd
Add files via upload

@@
 floatsintext: yes
-editor: visual
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 Specifically, some function is estimated that relates the attribute levels of the *L* attributes that were shown to subject *i* in the $k^{th}$ round in profile *j* and the covariate vector $X_i$ to the observed binary outcome $Y_{ijk}$ (which is equal to 1 if the profile was chosen and equal to 0 if it was not chosen).
-CITE detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functionial relationship could be used as well.
+CITE detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functional relationship could be used as well.
 BART is...
@@
 
--Vorgeschlagene neue Modelle in der Literatur 
--cjBart
--Idee des Modells/der Modelle 
--weitere Modelle:
-	-factorHet + idee kurz
-	-CRT + idee kurz
-Warum cjBart → das Modell stark machen
+-Vorgeschlagene neue Modelle in der Literatur -cjBart -Idee des Modells/der Modelle -weitere Modelle: -factorHet + idee kurz -CRT + idee kurz Warum cjBart → das Modell stark machen
 
 # Data, Research Question, and Method
--Die Daten 
--Fragestellung 
--bisherige Forschung
+
+-Die Daten -Fragestellung -bisherige Forschung
 
 # Results
--Ergebnisse 
-cjBart Ergebnisse
+
+-Ergebnisse cjBart Ergebnisse
 
 # Integration of Results
--Einordnung der Ergebnisse
--Vergleich mit factorHet
--Vergleich mit “normaler” Subgruppen Analyse
+
+-Einordnung der Ergebnisse -Vergleich mit factorHet -Vergleich mit “normaler” Subgruppen Analyse
 
 # Discussion
-Discussion & Limitations
--Tuning 
--Wie viele Covariates (inference vs. exploration)
--Stabilität
+
+Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität
 

### 2024-10-27 1b_Analysis_cjbart.R
Restructuring the Repo

@@ -9,7 +9,7 @@ library(cjbart)
 # setwd(dirname(rstudioapi::getSourceEditorContext()$path))
 
 ### Load Data 
-cj_tidy <- readRDS("Ukraine Conjoint Data/cj_tidy.rds")
+cj_tidy <- readRDS("0_Ukraine_Conjoint_Data/cj_tidy.rds")
 
 # get additional covariate data 
 add_covars <- 

### 2024-10-28 1b_Analysis_cjbart.R
updates to analysis file

@@ -13,11 +13,11 @@ cj_tidy <- readRDS("0_Ukraine_Conjoint_Data/cj_tidy.rds")
 
 # get additional covariate data 
 add_covars <- 
-  readRDS("Ukraine Conjoint Data/CJ_Ukraine_NewCovariates.Rds")
+  readRDS("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.Rds")
 # get additional covariate data --> same data different files types?
 library(haven)
 add_covars2 <- 
-  haven::read_dta("Ukraine Conjoint Data/CJ_Ukraine_NewCovariates.dta")
+  haven::read_dta("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.dta")
 rm(add_covars2)
 
 
@@ -73,12 +73,11 @@ fit_cjbart <- cjbart(data = cj_tidy,
                      cores = 4)
 
 
-saveRDS(fit_cjbart, "fit_cjbart_add_covars.rds")
-fit_cjbart <- readRDS("fit_cjbart_add_covars.rds")
+# saveRDS(fit_cjbart, "1c_Model_Objects/fit_cjbart_add_covars.rds")
+fit_cjbart <- readRDS("1c_Model_Objects/fit_cjbart_add_covars.rds")
 
 
 # Get IMCEs
-t1 <- Sys.time()
 imces <- IMCE(data = cj_tidy,
               keep_omce = TRUE,
               model = fit_cjbart, 
@@ -92,7 +91,7 @@ imces <- IMCE(data = cj_tidy,
                           , "Territ_Cession"
                           , "Polit_Self_Det_UKR"
                           ), 
-              ref_levels = c('25,000'
+              ref_levels = c('12,500'
                              , '25,000.'
                              , '4,000'
                              , '50B'
@@ -105,10 +104,10 @@ imces <- IMCE(data = cj_tidy,
               # ,method = 'parametric'
               , cores = 4
 )
-t2 <- Sys.time()
 
-saveRDS(imces, "imces_all_new_add_covars.rds")
-# imces <- readRDS("imces_all_new_add_covars.rds")
+saveRDS(imces, "1c_Model_Objects/2024-10-27_imces_all_new_add_covars.rds")
+imces_4 <- readRDS("1c_Model_Objects/imces_all_new.rds")
+imces <- readRDS("1c_Model_Objects/2024-10-27_imces_all_new_add_covars.rds")
 
 
 # Get VarImps
[…]

### 2024-10-29 Manuscript files/Manuscript.qmd
Chapter 2

--- 2024-10-26 Manuscript.qmd
@@
 
+## cjbart
+
 The premise of cjbart as introduced by CITE is that there are several *nested causal quantities* underlying the AMCE.
@@
 
-## Step 1: Modeling Potential Heterogeneity
+### Step 1: Modeling Potential Heterogeneity
 
@@
 CITE detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functional relationship could be used as well.
-BART is...
+BART is a supervised learning model based on a boosting procedure: many small decision trees are trained subsequently, each one aiming to explain the residual variance of the outcome variable which was not explained by all previous trees.
+The "Bayesian part" in BART is that parameters are seen as random variables (instead of constants, as would be the case in frequentist approaches).
+An advantage of BART is its robustness to the choice of hyperparameters (e.g., the number of individual trees) but they could be tuned if necessary, for example by cross-validation.
+The data that is used to train the BART are the data resulting from the conjoint experiment; that is, the different choices of profiles as well as the covariates, which are invariant at the individual-level.
+
+### Step 2: Predicting Counterfactual Outcomes
+
+In a second step, the estimated function from step 1 (i.e., the trained BART model) is used to predict counterfactual outcomes by changing the values of attribute levels.
+These predictions are counterfactual because they did not happen --- but we assess what would have been chosen had a certain attribute level been set to a different attribute level of the same attribute.
+This is done repeatedly by drawing multiple times from a predicted posterior distribution, once with the altered attribute level and once with the reference level of the same attribute.
+By subtracting these results and averaging them over the multiple draws of the posterior, we arrive at a parameter estimate of the OMCE (i.e., observation-level effects).
+
+### Step 3: Calculating IMCEs
+
+Following the nested causal quantities structure outlines above, IMCEs are calculated by averaging the OMCEs for each individual.
+Specifically, the OMCE estimates from step 2 are summed and divided by $J \times K$, that is, the number of profiles times the number of rounds (which is the number of total observations).
+
+## Identification of Heterogeneity
+
+As mentioned, the main reason why we employ these complicated procedures is because we want to estimate heterogeneous treatment effect.
+More specifically, we want to assess whether the effects of certain attribute levels of choice behavior are different across individuals.
+CITE provide two methods that yield information about which covariates are associated with heterogeneity in effects of attribute levels.
 
@@
 
--Vorgeschlagene neue Modelle in der Literatur -cjBart -Idee des Modells/der Modelle -weitere Modelle: -factorHet + idee kurz -CRT + idee kurz Warum cjBart → das Modell stark machen
+-Vorgeschlagene neue Modelle in der Literatur 
+-cjBart 
+-Idee des Modells/der Modelle 
+-weitere Modelle: 
+-factorHet + idee kurz 
+-CRT + idee kurz 
+Warum cjBart  
+das Modell stark machen
 

### 2024-10-30 Manuscript files/Manuscript.qmd
More work on cjbart section

@@
 CITE provide two methods that yield information about which covariates are associated with heterogeneity in effects of attribute levels.
+Both methods are tree-based which is especially suitable to investigate heterogeneity because trees partition a data set into increasingly homogeneous groups.
+Thereby, they can reveal covariates that drive the heterogeneity as these covariates will be used for splitting the data.
 
-EXPLAIN THREE STEP PROCEDURE OF ESTIMATING OMCES AND THEN IMCES WITH BART.
+### Tool 1: Random Forest Variable Importance
 
-EXPLAIN HOW RFs ARE USED TO ESTIMATE VIMP
+The first tool uses random forests, an ensemble of decision trees, to investigate which covariates are the important ones in the prediction of differences in the IMCE distributions for all attribute-levels (i.e., the effect heterogeneity).
+Specifically, for each attribute level, a random forest is trained where the covariates $X_i$ are used as predictors.
+Subsequently, variable importance measures (VIMPs) are derived to assess which covariates are driving the data partitioning.
+Briefly, the VIMPs are calculated by permuting the covariates (i.e., by introducing random noise to its values).
+If predictions change noticeably, this is an indication that the covariate is important for predicting the outcome (i.e., IMCE distributions).
+Of note, this is done separately for every combination of covariate and attribute level because the importance of a certain covariate may differ with respect to different attribute levels.
+This results in a comprehensive VIMP-heatmap, which we show in the results section.
 
-EXPLAIN HOW DTs ARE USED TO INVESTIGATE HETEROGENEITY IN IMCEs AND WHICH COVARIATES ARE DRIVERS
+### Tool 2:
 
--Vorgeschlagene neue Modelle in der Literatur 
--cjBart 
--Idee des Modells/der Modelle 
 -weitere Modelle: 

### 2024-11-13 Manuscript files/Manuscript.qmd
Finished chapter cjbart Started chapter data and research question

@@
 
-Arguably the most often estimated causal quantity in conjoint analyses is the *average marginal component effect* (AMCE).
+Arguably the most commonly estimated causal quantity in conjoint analyses is the *average marginal component effect* (AMCE).
 The AMCE is the effect of a specific attribute level of interest compared to another level of the same attribute, holding equal the joint distribution of all other attributes and averaged over this joint distribution as well as the sampling distribution from the population CITE.
@@
 
-The first tool uses random forests, an ensemble of decision trees, to investigate which covariates are the important ones in the prediction of differences in the IMCE distributions for all attribute-levels (i.e., the effect heterogeneity).
+The first tool uses random forests, an ensemble of decision trees, to investigate which covariates are the important ones in the prediction of differences in the IMCE distributions for all attribute levels (i.e., the effect heterogeneity).
 Specifically, for each attribute level, a random forest is trained where the covariates $X_i$ are used as predictors.
@@
 Of note, this is done separately for every combination of covariate and attribute level because the importance of a certain covariate may differ with respect to different attribute levels.
-This results in a comprehensive VIMP-heatmap, which we show in the results section.
+This results in a comprehensive VIMP-heatmap, which we show as an example in the results section.
 
@@
 
--weitere Modelle: 
--factorHet + idee kurz 
--CRT + idee kurz 
-Warum cjBart  
-das Modell stark machen
+By combining many weak decision trees, random forest have the advantage of increased predictive performance.
+However, this advantage comes at the cost of interpretability.
+Each tree only considers a random subset of predictor variables (in our case: subject-level covariates) and is trained on a bootstrap sample.
+Thus, CITE suggest a complementary analysis with single decision trees which are grown for a specific attribute level.
+In this analysis, a decision tree predicts IMCEs for this specific attribute level, again using subject-level covariates as predictors.
+The partitions within the tree can be readily investigated and interpreted as heterogeneity in IMCEs because only one model is fit to the data set and all predictor variables are considered for splitting.
+Importantly, to keep decision trees interpretable (i.e., to not let them grow too deep), they have to be pruned by setting a complexity parameter controlling the depth.
+CITE suggest to set this parameter such that the tree only continues to split the data if the increase in explained variance of the IMCE (i.e., $R^2$) is at least 0.02 to 0.04.
+The predictions in the terminal nodes of the tree correspond to conditional AMCEs, which would normally be assessed by estimating AMCEs in subgroups.
+However, by using decision trees, which are an exploratory tool by design, no subgroups have to be specified in advance.
+Even further, trees might even identify interaction effects between multiple covariates, for example by splitting twice on two different variables (e.g., Germans older than 30 years).
 
-# Data, Research Question, and Method
+# Data and Research Question
 
--Die Daten -Fragestellung -bisherige Forschung
+In the following, we showcase the application of cjbart to data provided by Prof. Dr. Paul Thurner and Fabian Haggerty from the Geschwister-Scholl-Institute of Political Science, LMU Munich.
+The data were first described in CITE.
+In their work, CITE aimed at investigating which attributes citizens from five different NATO-member countries (United States [US], United Kingdom [UK], Germany, Italy, and France) deem important when deciding whether Ukraine should be supported economically and militarily against the Russian aggression.
+For this, CITE conducted a conjoint experiment where participants from the five countries chose one of two possible profiles. 
+In these profiles, nine different attributes with varying attribute levels were manipulated randomly to indicate the consequences that a support of Ukraine would entail if the profile was chosen.
+The different attributes and their corresponding levels are shown in TABLE.
+Additionally, subject-level covariates were assessed, for example, participants' age, gender, political orientation, or their country of origin (of the five mentioned above).
+
+To investigate which attributes and attribute levels matter when people decide whether Ukraine should be supported in their defense endeavors, CITE estimated AMCEs as well as marginal means for subgroup analyses.
+THEIR RESULTS.
+
+As described above, this approach comes with the disadvantage that the potentially complex heterogeneity of attribute effects cannot be assessed.
+Additionally, subgroup analyses can only be carried out for a priori defined groups.
+
+# Method
 
@@
 
+-weitere Modelle: 
+-factorHet + idee kurz 
+-CRT + idee kurz 
+Warum cjBart  
+das Modell stark machen
+
 # Conclusion

### 2024-11-25 Manuscript files/Manuscript.qmd
cjbart simulation replication code adjustments changes to manuscript

@@
 In the social sciences, conjoint analyses are a powerful research design to assess preferences in humans.
-Under the popular special case of *forced choice designs*, participants are presented with two options of choice form which they have to choose one, for example certain products in marketing research, or two potential candidates in political research on voting behavior.
+Under the popular special case of *forced choice designs*, participants are presented with two options of choice from which they have to choose one, for example certain products in marketing research, or two potential candidates in political research on voting behavior.
 The two possible options are characterized by certain *attributes* (also: treatments), which can have different *attribute levels* (treatment levels), for example the attribute color of a car might have levels white, black, and blue.
@@
 This quantity is estimable by regression models and provides us an effect of an attribute on the probability that a certain option (or profile) will be chosen.
-As the name AMCE suggestes, this estimate is an average.
+As the name AMCE suggests, this estimate is an average.
 That is, potential differences in effects among participants cannot be considered directly.
 However, this *effect heterogeneity* is often of interest, when trying to determine whether an attribute is equally important to all participants regardless of background covariates (e.g., age, gender, education, etc.) or whether there are subgroup differences.
-Ultimately, it is a question of generalisation of results to the entire population and, even more advanced, of causal mechanisms in choice behavior.
+Ultimately, it is a question of generalization of results to the entire population and, even more advanced, of causal mechanisms in choice behavior.
 
 The simplest approach to take into account potential effect heterogeneity in conjoint analyses is to estimate the AMCE-models in different subgroups, for example a model for all male and female participants.
-Altough appealing due to its simplicity, this approach quickly reaches its limits and has additional downsides.
+Although appealing due to its simplicity, this approach quickly reaches its limits and has additional downsides.
 First, it is not clear how to a priori define the subgroups let alone how and where to include certain interactions.
@@
 This leads to some kind of "double high-dimensionality issue": there are many different attribute (level) combinations *and* many potential covariates characterizing the participants.
-This results in a number of possible interactions that are untractable for classical methods (these interactions correspond to the effect heterogeneity mentioned above).
+This results in a number of possible interactions that are intractable for classical methods (these interactions correspond to the effect heterogeneity mentioned above).
 
@@
 
-To remedy the downsides of the "naive" subgroup approach outline above, researchers developed more advanced methods based on machine learning.
+To remedy the downsides of the "naive" subgroup approach outlined above, researchers developed more advanced methods based on machine learning.
 Most notable in this regard are (a) an approach based on *Bayesian additive regression trees* (in the following called *cjbart* CITE), (b) an approach based on Bayesian mixture of regularized logistic regressions (*FactorHet* CITE), and (c) a testing approach based on conditional randomization tests (*CRT* CITE).
@@
 From these data we now want to estimate the causal parameters of interest, that is, AMCE, IMCE, RMCE, and OMCE.
-Nested in the AMCE described above, the IMCE is the change in probability that subject *i* choses a profile given a specific attribute level (compared to a reference category), again averaged over the effects of all other attributes.
+Nested in the AMCE described above, the IMCE is the change in probability that subject *i* choses a profile given a specific attribute level (compared to a reference level of the same attribute), again averaged over the effects of all other attributes.
 This corresponds to subgroup analyses of the AMCE with the convenient addition that the IMCE considers conditional effects based on all possible individual-level covariates.
-By inspecting the IMCE, effect heterogeneity due to non-randomized characterisitics (i.e., the covariates) can be identified.
+By inspecting the IMCE, effect heterogeneity due to non-randomized characteristics (i.e., the covariates) can be identified.
 The IMCE further contains the two lower-level quantities RMCE and OMCE.
@@
 
-As mentioned, the main reason why we employ these complicated procedures is because we want to estimate heterogeneous treatment effect.
-More specifically, we want to assess whether the effects of certain attribute levels of choice behavior are different across individuals.
+As mentioned, the main reason why we employ these complicated procedures is because we want to estimate heterogeneous treatment effects.
+More specifically, we want to assess whether the effects of certain attribute levels on choice behavior are different across individuals.
 CITE provide two methods that yield information about which covariates are associated with heterogeneity in effects of attribute levels.
@@
 
-### Tool 2:
+### Tool 2: Single Decision Tree Partitioning
 
@@
 
+Daten noch etwas besser beschreiben N, Studie etc.
+
 # Method
+Data of the above conjoint experiment was fit using the previously described cjbart approach and package.
+First, we fitted a *reduced model* based on a reduced data set (i.e.
+reduced model) only containing the profile attributes and subject-level covariates age, country, gender, and left-right-3 (i.e., political orientation categorized into the 3 categories left, middle, right).
+We then fitted a second *extended model* using a more extensive data set (i.e., extended model) with subject-level covariates additionally including subjects' agreement on different more specific statements regarding political or XXX statements (e.g., EXAMPLE).
+This results in trained BART models that were used to make the (counterfactual) predictions needed for calculating the quantities of interest such as IMCEs or AMCEs.
+
+In the next step, these (counterfactual) predictions were used to calculate OMCEs.
+These were aggregated to the different individual- and attribute specific IMCEs.
+We used the reference levels as specified in Table X.
+
+To better understand the associations of different subject-level covariates and individual effects of specific attributes (i.e., IMCEs) we used the two approaches proposed by CITE. 
+For this, a random forest model was fit on the IMCEs using the respective individuals' subject-level covariates. 
+We then used decision trees to more thoroughly investigate the relationships of specific IMCEs and covariates for which the previous step suggested relevant contribution to the prediction.
+As already proposed in CITE, we found complexity parameter values (cp) between 0.02 and 0.04 to yield useful results.
+Usage of larger cp values resulted in overly simplified trees often consisting of only a single root node.
+Smaller cp values, on the other hand, often resulted in overly deep trees with little differentiation across many terminal nodes providing too specific interpretations.
 
 # Results
+@fig-varimps-red displays the variable importance measures for the subject-level covariates as extracted from the reduced model.
+Variable Importances are colorized using heatmap-like colorcoding with stronger red (vs.
+white) color indicating larger importance measures.
 
--Ergebnisse cjBart Ergebnisse
+![Red VarImps](figures/RF_VarImps_red.png){#fig-varimps-red}
+
+The random forest variable importances as extracted from the extended model are displayed in @gif-varimps-ext.
+
+![Ext VarImps](figures/RF_VarImps_ext.png){#fig-varimps-ext}
+
+Figures X-Y depict the more specific decision trees that were fitted to better understand how different subject level covariates contribute to the observed effect heterogeneity.
 
 # Integration of Results
+-Einordnung der Ergebnisse 
+-Country in general important as seen in the reduced model 
+-association with country for almost all IMCEs 
+--> Trees: mostly UK vs Rest (then more specific associations)
+--> Gender relevant for perc. gdp. milit & civ. killed UKR 
+--> Left-Right-Relevant for perc. gdp econ
 
--Einordnung der Ergebnisse -Vergleich mit factorHet -Vergleich mit “normaler” Subgruppen Analyse
+-When using additional covariates results change quite a bit
+--> country still relevant but rather for the risk nuke and civ killed 
+--> gender also still for civ killed
+--> especially the 3 questions q10_10, q15_7 and q3_3 are also relevant
+--> describe questions and interpret
+
+-Vergleich mit factorHet 
+- short description of factor het results
+
+-Vergleich mit “normaler” Subgruppen Analyse
 

### 2024-11-25 1a_Analysis_FactorHet.R

@@ -69,7 +69,11 @@ fit_FH_3$information_criterion$N
 
 predict(fit_FH_3)
 
+# Load saved factorhet objects
+fit_FH_2 <- readRDS('1c_Model_Objects/00_archive/fit_FH_2F.rds')
+fit_FH_2 <- readRDS('1c_Model_Objects/00_archive/fit_FH_3F.rds')
 
+# Plot Stuff 
 FactorHet::marginal_AME(fit_FH_3) # fast
 FactorHet::posterior_by_moderators(fit_FH_3) # fast
 FactorHet::marginal_AMIE(fit_FH_3) # takes some time

### 2024-11-25 1b_Analysis_cjbart.R

@@ -1,9 +1,15 @@
 ################################################################################
-####### FACTOR HET 
+####### CJBART 
 ################################################################################
 
 ### Load Packages
 library(cjbart)
+library(haven)
+library(tidytext)
+library(dplyr)
+library(ggplot2)
+library(rpart)
+library(rpart.plot) # standard built-in plot function used in the paper
 
 ### Set WD
 # setwd(dirname(rstudioapi::getSourceEditorContext()$path))
@@ -15,7 +21,6 @@ cj_tidy <- readRDS("0_Ukraine_Conjoint_Data/cj_tidy.rds")
 add_covars <- 
   readRDS("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.Rds")
 # get additional covariate data --> same data different files types?
-library(haven)
 add_covars2 <- 
   haven::read_dta("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.dta")
 rm(add_covars2)
@@ -31,6 +36,7 @@ which(!colnames(add_covars) %in% colnames(cj_tidy))
 add_covars_new <- add_covars[,which(!colnames(add_covars) %in% 
                                       colnames(cj_tidy))]
 
+# join the new covariate data
 cj_tidy <- merge(cj_tidy,
                  add_covars_new,
                  by.x = "c_id",
@@ -50,37 +56,72 @@ colnames(cj_tidy)[which(colnames(cj_tidy) %in% c(paste0("attr",1:9)))] <-
     "Risk_Nuke",
     "Territ_Cession",
     "Polit_Self_Det_UKR")
-# get cols as characters(needed for imces)
-# cj_tidy$Sold_killed_UKR <- as.character(cj_tidy$Sold_killed_UKR)
-# cj_tidy$Sold_killed_RUS <- as.character(cj_tidy$Sold_killed_RUS)
-# cj_tidy$Civ_killed_UKR <- as.character(cj_tidy$Civ_killed_UKR)
-# cj_tidy$Infra_Destr_UKR <- as.character(cj_tidy$Infra_Destr_UKR)
-# cj_tidy$Perc_GDP_milit <- as.character(cj_tidy$Perc_GDP_milit)
-# cj_tidy$Perc_GDP_econ <- as.character(cj_tidy$Perc_GDP_econ)
[…]

### 2024-11-25 1c_cjbart_testscript.R

@@ -1,0 +1,245 @@
+# Re-Do the simulation of the paper
+rm(list = ls())
+simdat = function(n = 500, rounds = 5, profiles_per_round = 2){
+
+n = 500
+rounds = 5 
+profiles_per_round = 2
+obs = n*rounds*profiles_per_round
+
+  obs = n*rounds*profiles_per_round
+  
+  # Get profile attributes
+  a1 = sample(c('a','b'), 
+              obs, 
+              replace = T, 
+              prob = c(.5, .5))
+  a2 = sample(c('c','d'), 
+              obs, 
+              replace = T, 
+              prob = c(.5, .5))
+  a3 = sample(c('e','f'), 
+              obs, 
+              replace = T, 
+              prob = c(.5, .5))
+  
+  # Get the profile attribute dataframe
+  participants_full = rep(1:n, each = rounds*profiles_per_round)
+  rounds_full = rep(rep(1:rounds, each = profiles_per_round), n)
+  profiles_full = rep(1:profiles_per_round, n*rounds)
+  
+  # Get subject level covariates
+  c1_vec <- rbinom(n, 1, 0.5)          # Binary covariate for each user
+  c2_vec <- runif(n, -1, 1)
+  
+  # Repeat covariates to match the number of observations per user
+  c1_full <- rep(c1_vec, each = rounds * profiles_per_round)
+  c2_full <- rep(c2_vec, each = rounds * profiles_per_round)
+  
+  # Combine df
+  df = data.frame(participants_full,
+                  rounds_full,
+                  profiles_full,
+                  a1, a2, a3,
+                  c1_full, c2_full)
+  colnames(df) = c('user_id', 'round_id', 'profile_id', 
+                   'a1', 'a2', 'a3',
+                   'c1', 'c2')
+  
+  # Calculate Changes in Utilities
+  # df$delta_U1 = mapply(function(c1) 
+  #   ifelse(c1 == 1, rnorm(1,1,1), rnorm(1,-1,1)), df$c1)
+  # df$delta_U2 = mapply(function(c2) 
+  #   rnorm(1, mean = abs(c2 - 0.2), sd = 1), df$c2)
+  # df$delta_U3 = rnorm(obs,0,0.5)
+  
+  
+  # Calculate Changes in Utilities per user
+  # Generate delta_U1, delta_U2, delta_U3 for each user
[…]

### 2024-11-25 1e_cjbart_demo.R

@@ -1,0 +1,28 @@
+set.seed(89)
+library(ggplot2)
+library(cjbart)
+
+subjects <- 100
+rounds <- 5
+profiles <- 2
+obs <- subjects*rounds*profiles
+
+fake_data <- data.frame(A = sample(c("a1","a2","a3"), obs, replace = TRUE),
+                        B = sample(c("b1","b2","b3"), obs, replace = TRUE),
+                        C = sample(c("c1","c2","c3"), obs, replace = TRUE),
+                        D = sample(c("d1","d2","d3"), obs, replace = TRUE),
+                        E = sample(c("e1","e2","e3"), obs, replace = TRUE),
+                        
+                        covar1 = rep(runif(subjects, 0 ,1),
+                                     each = rounds),
+                        covar2 = rep(sample(c(1,0),
+                                            subjects,
+                                            replace = TRUE),
+                                     each = rounds),
+                        
+                        id1 = rep(1:subjects, each=rounds),
+                        stringsAsFactors = TRUE)
+
+fake_data$Y <- ifelse(fake_data$E == "e2",
+                      rbinom(obs, 1, fake_data$covar1),
+                      sample(c(0,1), obs, replace = TRUE))

### 2024-11-25 1f_OnlineReplication.R

@@ -1,0 +1,104 @@
+set.seed(seed)
+
+subjects = 500
+rounds = 5
+
+
+# Define individual-level utilities
+utilities <- data.frame(id = 1:subjects,
+                        c1 = rbinom(subjects, 1, 0.5),
+                        c2 = runif(subjects, -1,1)) %>% 
+  mutate(X1_1 = ifelse(c1 == 1, 
+                       rnorm(subjects, 1, sd = 1),
+                       rnorm(subjects, -1, sd = 1)),
+         X2_1 = rnorm(subjects, abs(c2-0.2), sd = 1),
+         X3_1 = rnorm(subjects, 0,sd = 0.5))
+
+# Use utilities to determine hypothetical conjoint behaviour
+conjoint_data <- data.frame(id = rep(1:subjects, each = rounds*2),
+                            round = rep(1:rounds, each = 2),
+                            profile = 1:2,
+                            X1 = rbinom(subjects*rounds*2, 1, 0.5),
+                            X2 = rbinom(subjects*rounds*2, 1, 0.5),
+                            X3 = rbinom(subjects*rounds*2, 1, 0.5)) %>% 
+  left_join(utilities, by = "id") %>% 
+  mutate(U = X1*X1_1 + X2*X2_1 + X3*X3_1 + rnorm(subjects*rounds*2, 0,0.0005)) %>% 
+  group_by(id, round) %>%
+  mutate(Y = ifelse(U == max(U),1,0)) %>% 
+  ungroup()
+
+# Mutate data for cleaner presentation
+train_data <- conjoint_data %>% select(id, X1, X2, X3, c1, c2, Y) %>% 
+  mutate(X1 = ifelse(X1 == 1, "A1: Binary heterogeneity (c1)","a"),
+         X2 = ifelse(X2 == 1, "A2: Interval heterogeneity (c2)","c"),
+         X3 = ifelse(X3 == 1, "A3: Random heterogeneity","e"))
+
+
+
+
+
+set.seed(89)
+
+# Function for simulating subject preferences and resulting conjoint data
+preference_sim <- function(subjects = 500, rounds = 5, seed = 89) {
+  
+  set.seed(seed)
+  
+  # Define individual-level utilities
+  utilities <- data.frame(id = 1:subjects,
+                          c1 = rbinom(subjects, 1, 0.5),
+                          c2 = runif(subjects, -1,1)) %>% 
+    mutate(X1_1 = ifelse(c1 == 1, 
[…]

### 2024-11-25 1g_cjbart_age_categorical.R

@@ -1,0 +1,341 @@
+################################################################################
+####### CJBART 
+################################################################################
+
+### Load Packages
+library(cjbart)
+library(haven)
+library(tidytext)
+library(dplyr)
+library(ggplot2)
+library(rpart)
+library(rpart.plot) # standard built-in plot function used in the paper
+
+### Set WD
+# setwd(dirname(rstudioapi::getSourceEditorContext()$path))
+
+### Load Data 
+cj_tidy <- readRDS("0_Ukraine_Conjoint_Data/cj_tidy.rds")
+
+# get additional covariate data 
+add_covars <- 
+  readRDS("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.Rds")
+# get additional covariate data --> same data different files types?
+add_covars2 <- 
+  haven::read_dta("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.dta")
+rm(add_covars2)
+
+
+### Join the add_covars with the cj_tidy data 
+# for this, create c_id (country_id) variable in add_covars
+add_covars$country_id <- paste0(add_covars$Country, 
+                                "_",
+                                add_covars$ID)
+# Remove the covars in add_covars that are already present in cj_tidy
+which(!colnames(add_covars) %in% colnames(cj_tidy))
+add_covars_new <- add_covars[,which(!colnames(add_covars) %in% 
+                                      colnames(cj_tidy))]
+
+# join the new covariate data
+cj_tidy <- merge(cj_tidy,
+                 add_covars_new,
+                 by.x = "c_id",
+                 by.y = "country_id", 
+                 all.x = T) # left join
+
+
+
+# Rename Attributes
+colnames(cj_tidy)[which(colnames(cj_tidy) %in% c(paste0("attr",1:9)))] <-
+  c("Sold_killed_UKR",
+    "Sold_killed_RUS",
+    "Civ_killed_UKR",
+    "Infra_Destr_UKR",
+    "Perc_GDP_milit",
+    "Perc_GDP_econ",
+    "Risk_Nuke",
+    "Territ_Cession",
+    "Polit_Self_Det_UKR")
+
+
+# Recode age to categoricals 
+# get age into 4 groups, <30, <=50, <=70, >70
+cj_tidy$age_cat <- ifelse(cj_tidy$age > 70, 4,
+                          ifelse(cj_tidy$age <= 70, 3,
[…]

### 2024-11-26 Manuscript files/Manuscript.qmd
updates to figure embeddings

@@
 # Results
-@fig-varimps-red displays the variable importance measures for the subject-level covariates as extracted from the reduced model.
+@fig-varimps-ext displays the variable importance measures for the subject-level covariates as extracted from the cjbart model.
 Variable Importances are colorized using heatmap-like colorcoding with stronger red (vs.
@@
 
-![Red VarImps](figures/RF_VarImps_red.png){#fig-varimps-red}
+![Ext VarImps](figures/RF_VarImps_ext_v2.png){#fig-varimps-ext}
 
-The random forest variable importances as extracted from the extended model are displayed in @gif-varimps-ext.
+@image-panel depicts 4 decision trees that were fitted to better understand how different subject level covariates contribute to the observed effect heterogeneity.
+These exemplary decision trees were selected regarding content and interpretation and to highlight how single decision tress can be utilized for model interpretation.
 
-![Ext VarImps](figures/RF_VarImps_ext.png){#fig-varimps-ext}
+```{r image-panel, echo=FALSE, fig.align='center'}
+#| fig-cap: "Exemplary deicision trees for predicting IMCEs based on Covariates."
+library(gridExtra)
+library(grid)
+library(png)
 
-Figures X-Y depict the more specific decision trees that were fitted to better understand how different subject level covariates contribute to the observed effect heterogeneity.
+# Load the images from your laptop
+img1 <- rasterGrob(png::readPNG("figures/DecTree_ext_Civ_killed_Ukr_16k.png"), interpolate = TRUE)
+img2 <- rasterGrob(png::readPNG("figures/DecTree_ext_RUS_Sold_killed_100k.png"), interpolate = TRUE)
+img3 <- rasterGrob(png::readPNG("figures/DecTree_ext_Risk_Nuke_Moderate.png"), interpolate = TRUE)
+img4 <- rasterGrob(png::readPNG("figures/DecTree_ext_Territ_Cession_8perc.png"), interpolate = TRUE)
 
-# Integration of Results
+# Create subfigure captions
+label1 <- textGrob("a) Ukrainian Civilians Killed (16k vs. 4k)", 
+                   x = 0.05, y = 0.95, hjust = 0, vjust = 1, gp = gpar(fontsize = 8, fontface = "bold"))
+label2 <- textGrob("b) Russian Soldiers killed (100k vs. 25k)", 
+                   x = 0.05, y = 0.95, hjust = 0, vjust = 1, gp = gpar(fontsize = 8, fontface = "bold"))
+label3 <- textGrob("c) Risk of Nuclear Strike (10% vs. 0%)", 
+                   x = 0.05, y = 0.95, hjust = 0, vjust = 1, gp = gpar(fontsize = 8, fontface = "bold"))
+label4 <- textGrob("d) Territorial Cession (2014 LoC (8%)) vs. None", 
+                   x = 0.05, y = 0.95, hjust = 0, vjust = 1, gp = gpar(fontsize = 8, fontface = "bold"))
+
+# Combine images and captions
+panel1 <- arrangeGrob(img1, top = label1)
+panel2 <- arrangeGrob(img2, top = label2)
+panel3 <- arrangeGrob(img3, top = label3)
+panel4 <- arrangeGrob(img4, top = label4)
+
+# Add a blank grob as a spacer
+spacer <- textGrob("", gp = gpar(fontsize = 5))
+
+# Arrange the panels in a 2x2 grid with space between rows
+grid <- grid.arrange(
+  arrangeGrob(panel1, panel2, ncol = 2),
+  spacer, 
+  arrangeGrob(panel3, panel4, ncol = 2),
+  nrow = 3, heights = c(0.45, 0.1, 0.45) 
+)
+
+```
+
+<!-- This is how it should work using quarto syntax but doesnt display captions properly and is weirdly centered -->
+<!-- ::::{#fig-group_label layout-ncol=2 layout-nrow=2} -->
+
+<!-- :::{#firstcol .column width="50%"} -->
+
+<!-- ![test1](figures/DecTree_ext_Civ_killed_Ukr_16k.png){#fig-civ_UKR} -->
+
+<!-- ![test2](figures/DecTree_ext_RUS_Sold_killed_100k.png){#fig-sold_RUS} -->
+<!-- ::: -->
+
+<!-- :::{#secondcol .column width="50%"} -->
+
+<!-- ![test3](figures/DecTree_ext_Risk_Nuke_Moderate.png){#fig-nuke} -->
+<!-- ![test4](figures/DecTree_ext_Territ_Cession_8perc.png){#fig-territ} -->
+<!-- ::: -->
+
+<!-- Exemplary Single Decision Tree Partitions for Predicting IMCEs -->
+<!-- :::: -->
+
+# Discussion
+
+## Integration of Results
 -Einordnung der Ergebnisse 
@@
 
--Vergleich mit factorHet 
-- short description of factor het results
+<!-- -Vergleich mit factorHet eher raus -->
+<!-- - short description of factor het results  -->
 
--Vergleich mit “normaler” Subgruppen Analyse
+-Vergleich mit “normaler” Subgruppen Analyse --> aka vergleich mit deren paper
 
-# Discussion
-
+## Methodological Discussion
 Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität

### 2024-11-26 1b_Analysis_cjbart.R

@@ -222,7 +222,6 @@ var_imps_ext <- readRDS("1c_Model_Objects/2024-11-18_var_imps_ext.rds")
 # plot(var_imps_ext)
 
 var_imps_ext <- readRDS("1c_Model_Objects/2024-11-18_var_imps_ext.rds")
-var_imps_ext_2 <- readRDS("1c_Model_Objects/2024-11-18_var_imps_ext_2.rds")
 
 #### Custom plot (prettier)
 # plot_data <- var_imps_red$results # reduced covariate set
@@ -243,6 +242,20 @@ custom_labels <- c("Sold_killed_UKR" = "Sold\nkilled\nUKR",
 plot_data[which(plot_data$covar == 'age'), 'covar'] <- "Age"
 plot_data[which(plot_data$covar == 'gender'), 'covar'] <- "Gender"
 plot_data[which(plot_data$covar == 'leftright3'), 'covar'] <- "Left-Right-3"
+
+# Rename Questionnaire Covariates
+plot_data[which(plot_data$covar == 'Q5'), 'covar'] <- "Weapons matter\nfor election 4"  # 
+plot_data[which(plot_data$covar == 'q10_2'), 'covar'] <- "Anti Weapon\ndeliveries 7"# 
+plot_data[which(plot_data$covar == 'q10_6'), 'covar'] <- "General Weapon\nfor defense 7"# 
+plot_data[which(plot_data$covar == 'q10_8'), 'covar'] <- "Weapons if\nciv. casualties  7"#
+plot_data[which(plot_data$covar == 'q10_10'), 'covar'] <- "Weapons if\n infra. destr. 7"
+plot_data[which(plot_data$covar == 'Q11'), 'covar'] <- "Anti Nato 5"  # 
+plot_data[which(plot_data$covar == 'q1617_RUS'), 'covar'] <- "Empathy RUS 7"  # 
+plot_data[which(plot_data$covar == 'q1617_USA'), 'covar'] <- "Anti USA 7"  # 
+plot_data[which(plot_data$covar == 'QV_Ukraine'), 'covar'] <- "Political Agenda:\nWar Ukraine 7"  # 
+plot_data[which(plot_data$covar == 'q3_3'), 'covar'] <- "Scared\nby War 7"
+plot_data[which(plot_data$covar == 'Q15_1'), 'covar'] <- "for Peace 01:\nUKR NATO Waiver"
[…]

### 2024-11-27 Manuscript files/Manuscript.qmd
updates

@@
 # Results
+Global AMCEs
+
 @fig-varimps-ext displays the variable importance measures for the subject-level covariates as extracted from the cjbart model.
@@
 
-@image-panel depicts 4 decision trees that were fitted to better understand how different subject level covariates contribute to the observed effect heterogeneity.
-These exemplary decision trees were selected regarding content and interpretation and to highlight how single decision tress can be utilized for model interpretation.
+@image-panel depicts 4 exemplary decision trees that were fitted to better understand how different subject level covariates contribute to effect heterogeneity.
+These decision trees were selected based on content-related and interpretational criteria and to highlight how single decision tress can be utilized for model interpretation.
 
@@
 ## Integration of Results
--Einordnung der Ergebnisse 
--Country in general important as seen in the reduced model 
--association with country for almost all IMCEs 
---> Trees: mostly UK vs Rest (then more specific associations)
---> Gender relevant for perc. gdp. milit & civ. killed UKR 
---> Left-Right-Relevant for perc. gdp econ
 

### 2024-11-27 1b_Analysis_cjbart.R

@@ -10,6 +10,10 @@ library(dplyr)
 library(ggplot2)
 library(rpart)
 library(rpart.plot) # standard built-in plot function used in the paper
+library(dplyr)
+library(tidyr)
+library(ggtext)
+
 
 ### Set WD
 # setwd(dirname(rstudioapi::getSourceEditorContext()$path))
@@ -180,7 +184,152 @@ imces_ext <- IMCE(data = cj_tidy[, vars_ext],
 )
 
 # saveRDS(imces_ext, "1c_Model_Objects/2024-11-18_imces_ext_2.rds")
-imces_ext2 <- readRDS("1c_Model_Objects/2024-11-18_imces_ext_2.rds")
+imces_ext <- readRDS("1c_Model_Objects/2024-11-18_imces_ext.rds")
+
+
+
+###' *Plot Distribution of IMCEs* 
+# plot(imces_ext) # plots IMCEs ordered by size (not what we want)
+# Extract data frames from the results
+imces_ext <- readRDS("1c_Model_Objects/2024-11-18_imces_ext.rds")
+attribute_levels <- imces_ext$att_levels # attribute levels
+imce_df <- imces_ext$imce # point estimates
+imce_lower_df <- imces_ext$imce_lower 
+imce_upper_df <- imces_ext$imce_upper
+att_lookup <- imces_ext$att_lookup
+
+
+# Reshape IMCE data from wide to long format
+imce_long <- imce_df %>%
+  select(all_of(c(attribute_levels, 'c_id'))) %>%
+  pivot_longer(cols = -c_id, names_to = "Level", values_to = "IMCE")
+
+imce_lower_long <- imce_lower_df %>%
+  select(all_of(c(attribute_levels, 'c_id'))) %>%
+  pivot_longer(cols = -c_id, names_to = "Level", values_to = "Lower")
+
+imce_upper_long <- imce_upper_df %>%
+  select(all_of(c(attribute_levels, 'c_id'))) %>%
+  pivot_longer(cols = -c_id, names_to = "Level", values_to = "Upper")
+
+# Combine IMCE estimates and confidence intervals
+imce_combined <- imce_long %>%
+  left_join(imce_lower_long, by = c("c_id", "Level")) %>%
+  left_join(imce_upper_long, by = c("c_id", "Level"))
+
+# Merge with att_lookup to get Attribute names
+imce_combined <- imce_combined %>%
+  left_join(att_lookup, by = c("Level" = "Level"))
+
+# Calculate mean IMCE and confidence intervals for each attribute level
[…]

### 2024-11-27 1b_Analysis_cjbart.R
updates

@@ -246,15 +246,15 @@ desired_orders_df <- data.frame(
                 rep("Risk_Nuke", 2),
                 rep("Territ_Cession", 3),
                 rep("Polit_Self_Det_UKR", 2)),
-  Level = c("50,000", "25,000",
-            "100,000", "50,000.",
-            "16,000", "8,000",
-            "200B", "100B",
-            "0.3% of GDP", "0.2% of GDP",
-            "0.3% of GDP.", "0.2% of GDP.",
-            "Moderate (10%)", "Low (5%)",
-            "2023 LoC (16%)", "2014 LoC (8%)", "Crimea (4%)",
-            "Russian influence", "No EU/NATO"),
+  Level = c("25,000", "50,000", 
+            "50,000.", "100,000", 
+            "8,000", "16,000", 
+            "100B", "200B",
+            "0.2% of GDP", "0.3% of GDP", 
+            "0.2% of GDP.", "0.3% of GDP.", 
+            "Low (5%)", "Moderate (10%)", 
+            "Crimea (4%)", "2014 LoC (8%)", "2023 LoC (16%)",
+            "No EU/NATO", "Russian influence"),
   global_order = 1:19
 )
 
@@ -262,13 +262,10 @@ desired_orders_df <- data.frame(
 plot_data <- plot_data %>%
   left_join(desired_orders_df, by = c("Attribute", "Level"))
 
-# Remove any rows that do not have a desired order (if any)
-plot_data <- plot_data %>% 
-  filter(!is.na(global_order))
-
 # Reorder the levels of AttributeLevel according to global_order
 plot_data$AttributeLevel <- factor(plot_data$AttributeLevel, 
                                    levels = plot_data$AttributeLevel[order(-plot_data$global_order)])
+plot_data <- plot_data[order(plot_data$global_order), ]
 
 # Define baseline levels with IMCE = 0
 baseline_levels <- data.frame(
@@ -298,6 +295,7 @@ plot_data <- plot_data %>%
 
 # Reorder AttributeLevel factor based on updated global_order
 plot_data$AttributeLevel <- factor(plot_data$AttributeLevel, levels = plot_data$AttributeLevel[order(-plot_data$global_order)])
+plot_data <- plot_data[order(plot_data$global_order), ]
 
 # plot_data_legacy <- plot_data
 plot_data <- plot_data_legacy
@@ -306,7 +304,7 @@ plot_data <- plot_data_legacy
[…]

### 2024-11-27 Manuscript files/Manuscript.qmd
Attr table and some methods section

@@
 In their work, CITE aimed at investigating which attributes citizens from five different NATO-member countries (United States [US], United Kingdom [UK], Germany, Italy, and France) deem important when deciding whether Ukraine should be supported economically and militarily against the Russian aggression.
-For this, CITE conducted a conjoint experiment where participants from the five countries chose one of two possible profiles. 
+For this, CITE conducted a conjoint experiment where $N = 10,011$ participants from the five countries chose one of two possible profiles. 
 In these profiles, nine different attributes with varying attribute levels were manipulated randomly to indicate the consequences that a support of Ukraine would entail if the profile was chosen.
-The different attributes and their corresponding levels are shown in TABLE.
-Additionally, subject-level covariates were assessed, for example, participants' age, gender, political orientation, or their country of origin (of the five mentioned above).
+The different attributes, their corresponding levels, and the reference categories we used for our analyses are shown in TABLE.
+Additionally, subject-level covariates were assessed, for example, participants' age, gender, political orientation, or their country of origin (of the five countries mentioned above).
+
+```{r attributes, echo=FALSE}
+#| output: asis
+library(kableExtra)
+
+attrib <- data.frame(Attribute = c("Number of Ukrainian soldiers killed?",
+                                   "Number of Russian soldiers killed?",
+                                   "Number of Ukrainian civilians killed?",
+                                   "Value of destroyed infrastructure in Ukraine?",
+                                   "[Country] contribution to military aid to Ukraine?",
+                                   "[Country] contribution to economic aid to Ukraine?",
+                                   "Risk of a Russian nuclear strike on Ukraine?",
+                                   "How much political self-determination of Ukraine?",
+                                   "Territorial cessions of Ukraine to Russia?"),
+                     Attribute_Levels = c("1. 12,500 <br> 2. 25,000 <br> 3. 50,000",
+                                          "1. 25,000 <br> 2. 50,000 <br> 3. 100,000",
+                                          "1. 4,000 <br> 2. 8,000 <br> 3. 16,000",
+                                          "1. $50B <br> 2. $100B <br> 3. $200B",
+                                          "1. X bn (0.1% of [Country] GDP) <br> 2. X bn (0.2% of [Country] GDP) <br> 3. X bn (0.3% of [Country] GDP)",
+                                          "1. X bn (0.1% of [Country] GDP) <br> 2. X bn (0.2% of [Country] GDP) <br> 3. X bn (0.3% of [Country] GDP)",
+                                          "1. Not present (0%) <br> 2. Low (5%) <br> 3. Moderate (10%)",
+                                          "1. Full self-determination <br> 2. No NATO/EU membership <br> 3. Russian influence over Ukr. gov.",
+                                          "1. No cessions of territory <br> 2. Crimea (ca. 4% of land) <br> 3. 2014 Line of Conflict (ca. 8%) <br> 4. 2023 Line of Conflict (ca. 16%)"),
+                     Reference = c("12,500",
+                                   "25,000",
+                                   "4,000",
+                                   "$50B",
+                                   "0.1% of GDP",
+                                   "0.1% of GDP",
+                                   "Not present (0%)",
+                                   "Full self-determination",
+                                   "No cessions of territory"))
+
+knitr::kable(attrib, 
+             format = "html", 
+             col.names = c("Attribute", "Attribute Levels", "Reference Category"), 
+             escape = FALSE,
+             caption = "Attributes, attribute levels, and reference categories used in the analyses.")
+
+```
 
 To investigate which attributes and attribute levels matter when people decide whether Ukraine should be supported in their defense endeavors, CITE estimated AMCEs as well as marginal means for subgroup analyses.
-THEIR RESULTS.
+The results of their analyses will be outlined below, where we compare them to the results of our analyses using cjbart.
+As described above, the "classical" approach of estimating AMCEs and conducting subgroup analyses comes with the disadvantage that the potentially complex heterogeneity of attribute effects cannot be assessed.
+Additionally, subgroup analyses can only be carried out for a priori defined groups.
+If covariates have many different levels, it quickly becomes unfeasible to carry out all subgroup analyses.
+If covariates are continuous, it might even be impossible, unless arbitrarily chosen splits to discretize the data are performed.
 
-As described above, this approach comes with the disadvantage that the potentially complex heterogeneity of attribute effects cannot be assessed.
-Additionally, subgroup analyses can only be carried out for a priori defined groups.
-
-Daten noch etwas besser beschreiben N, Studie etc.
+Thus, the goal of this project is to complement the existing results reported by CITE with an exploratory analysis.
+Using cjbart, we are able to scrutinize the data for heterogeneity of attribute effects.
+Additionally, using the decision tree approach described above, we perform exploratory subgroup analyses.
+The goal of these analyses is to identify which groups differ in their preferences regarding specific attribute levels.
 
 # Method
-Data of the above conjoint experiment was fit using the previously described cjbart approach and package.
-First, we fitted a *reduced model* based on a reduced data set (i.e.
-reduced model) only containing the profile attributes and subject-level covariates age, country, gender, and left-right-3 (i.e., political orientation categorized into the 3 categories left, middle, right).
-We then fitted a second *extended model* using a more extensive data set (i.e., extended model) with subject-level covariates additionally including subjects' agreement on different more specific statements regarding political or XXX statements (e.g., EXAMPLE).
-This results in trained BART models that were used to make the (counterfactual) predictions needed for calculating the quantities of interest such as IMCEs or AMCEs.
+Data of the above conjoint experiment was modeled by the previously described cjbart approach.
+For this, we used the R package *cjbart* described in CITE.
+We fitted a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
+A list of all covariates, including their type, can be found in TABLE.
+This resulted in a trained BART model that was used to make the (counterfactual) predictions needed for calculating the quantities of interest, such as IMCEs or AMCEs.
 
 In the next step, these (counterfactual) predictions were used to calculate OMCEs. 
-These were aggregated to the different individual- and attribute specific IMCEs.
-We used the reference levels as specified in Table X.
+These were aggregated to the different individual- and attribute-specific IMCEs.
 
-To better understand the associations of different subject-level covariates and individual effects of specific attributes (i.e., IMCEs) we used the two approaches proposed by CITE. 
-For this, a random forest model was fit on the IMCEs using the respective individuals' subject-level covariates. 
+To better understand the associations of different subject-level covariates and individual effects of specific attributes (i.e., IMCEs), we used the two tree-based approaches proposed by CITE. 
+For this, a random forest model was first fit, predicting the IMCEs using the respective individuals' subject-level covariates. 
 We then used decision trees to more thoroughly investigate the relationships of specific IMCEs and covariates for which the previous step suggested relevant contribution to the prediction. 
@@
 Usage of larger cp values resulted in overly simplified trees often consisting of only a single root node. 
-Smaller cp values, on the other hand, often resulted in overly deep trees with little differentiation across many terminal nodes providing too specific interpretations.
+Smaller cp values, on the other hand, often resulted in overly deep trees with little differentiation across many terminal nodes, making the interpretation of substantive differences too difficult. 
+In the next section, we present the results of these analyses, followed by a discussion and comparison to the results reported by CITE.
 

### 2024-11-28 Manuscript files/Manuscript.qmd
Tables

@@
 In these profiles, nine different attributes with varying attribute levels were manipulated randomly to indicate the consequences that a support of Ukraine would entail if the profile was chosen.
-The different attributes, their corresponding levels, and the reference categories we used for our analyses are shown in TABLE.
+The different attributes, their corresponding levels, and the reference categories we used for our analyses are shown in @tbl-attributes.
 Additionally, subject-level covariates were assessed, for example, participants' age, gender, political orientation, or their country of origin (of the five countries mentioned above).
@@
 #| output: asis
+#| label: tbl-attributes
 library(kableExtra)
@@
 This resulted in a trained BART model that was used to make the (counterfactual) predictions needed for calculating the quantities of interest, such as IMCEs or AMCEs.
+
+```{r covariates, echo=FALSE}
+#| output: asis
+library(kableExtra)
+
+attrib <- data.frame(Attribute = c("Number of Ukrainian soldiers killed?",
+                                   "Number of Russian soldiers killed?",
+                                   "Number of Ukrainian civilians killed?",
+                                   "Value of destroyed infrastructure in Ukraine?",
+                                   "[Country] contribution to military aid to Ukraine?",
+                                   "[Country] contribution to economic aid to Ukraine?",
+                                   "Risk of a Russian nuclear strike on Ukraine?",
+                                   "How much political self-determination of Ukraine?",
+                                   "Territorial cessions of Ukraine to Russia?"),
+                     Attribute_Levels = c("1. 12,500 <br> 2. 25,000 <br> 3. 50,000",
+                                          "1. 25,000 <br> 2. 50,000 <br> 3. 100,000",
+                                          "1. 4,000 <br> 2. 8,000 <br> 3. 16,000",
+                                          "1. $50B <br> 2. $100B <br> 3. $200B",
+                                          "1. X bn (0.1% of [Country] GDP) <br> 2. X bn (0.2% of [Country] GDP) <br> 3. X bn (0.3% of [Country] GDP)",
+                                          "1. X bn (0.1% of [Country] GDP) <br> 2. X bn (0.2% of [Country] GDP) <br> 3. X bn (0.3% of [Country] GDP)",
+                                          "1. Not present (0%) <br> 2. Low (5%) <br> 3. Moderate (10%)",
+                                          "1. Full self-determination <br> 2. No NATO/EU membership <br> 3. Russian influence over Ukr. gov.",
+                                          "1. No cessions of territory <br> 2. Crimea (ca. 4% of land) <br> 3. 2014 Line of Conflict (ca. 8%) <br> 4. 2023 Line of Conflict (ca. 16%)"),
+                     Reference = c("12,500",
+                                   "25,000",
+                                   "4,000",
+                                   "$50B",
+                                   "0.1% of GDP",
+                                   "0.1% of GDP",
+                                   "Not present (0%)",
+                                   "Full self-determination",
+                                   "No cessions of territory"))
+
+knitr::kable(attrib, 
+             format = "html", 
+             col.names = c("Attribute", "Attribute Levels", "Reference Category"), 
+             escape = FALSE,
+             caption = "Attributes, attribute levels, and reference categories used in the analyses.")
+
+```
 

### 2024-11-28 Manuscript files/Manuscript.qmd
updates to plots and manuscripts

@@
 # Results
-Global AMCEs
+In @fig-amces we present the AMCEs estimated by averaging the IMCEs calculated using the cjbart model.
+
+![AMCEs](figures/AMCEs.png){#fig-amces}
 
@@
 
-@image-panel depicts 4 exemplary decision trees that were fitted to better understand how different subject level covariates contribute to effect heterogeneity.
+@fig-imagepanel depicts 4 exemplary decision trees that were fitted to better understand how different subject level covariates contribute to effect heterogeneity.
 These decision trees were selected based on content-related and interpretational criteria and to highlight how single decision tress can be utilized for model interpretation.
@@
 #| fig-cap: "Exemplary deicision trees for predicting IMCEs based on Covariates."
+#| label: fig-imagepanel
 library(gridExtra)
@@
 ## Integration of Results
+For AMCEs, theoretically most favorable events served as baseline.
+As can be seen, increased attribute levels (i.e., less favourable events) were usually linked to significantly decreased levels of support.
+For example, increasing the risk of a nuclear strike from the reference level 'Not present (0%)' to 'Moderate (10%)' decreased the average probability of a participant choosing the latter profile by about -8.5%.
+The AMCE point estimates were in line with the AMCEs reported in CITE, which is why we refrain from an in-depth discussion here and refer the interested reader to CITE.
+HIER WAS DAZU SCHREIBEN DAS WIR HÖHERE SEs HABEN? DAZU SCHREIBEN DIE HALT IN IHREM PAPER EH GAR NIX
 
--When using additional covariates results change quite a bit
---> country still relevant but rather for the risk nuke and civ killed 
---> gender also still for civ killed
---> especially the 3 questions q10_10, q15_7 and q3_3 are also relevant
---> describe questions and interpret
+As a next step, we predicted the subject-level IMCEs using the subject-level covariates.
+Based on this random forest model, we then calculated variable importance measures which served as indicators for variables associated with effect heterogeneity.
+We found the highest variable importance values for the subject-level covariates Country, Geneder, and the items asking participants about whether they generally support supply of weapons to countries defending themselves against other country's invasions (Q10_10) and whether the Ukraine should make any concessions in order to achieve peace (Q15_7).
+
+These variable importance measures do not provide any more interpretability than which covariates in general seem to matter, which is why we further substantiated the previous analysis by fitting single decision trees to different IMCEs.
+IMCEs for this were selected due to content-related purposes and to highlight how decision trees facilitate interpretation of effect heterogeneity.
+As can be seen in @image-panel (upper left panel), for participants from countries different to the UK the probability to select a given profile decreased by -12.5% if the respective profile was associated with 16,000 (vs.
+4,000) Ukrainian civilian casualties.
+For participants from the UK, the larger number of civilian casualties was also linked to a lower profile selection probability, although, the attribute level was less influential for their decision.
+In general, we saw the UK vs other countries split in many different trees possibly indicating slight differences in attitudes towards weapon supplies across these countries.
+Moreover, whether participants were female (within both UK and Non-UK subgroups) predicted
+
+Apart from this, participants' attitude about whether the Ukraine should make any concessions to Russia if this would lead to a peace agreement predicted some level of effect heterogeneity to an interesting extent.
+For example.
+with regards to Russian soldiers killed, people that selected that the Ukraine should not make any concessions, on average were more likely to select profiles with a larger number of Russian military casualties (100,000 vs.
+25,000).
+Interestingly, out of the investigated IMCE decision trees this was the only case for which we observed splits resulting in nodes with different signs meaning that the probability of profile selection decreased in one child node and increased in the other.
+These results have however, to be interpreted with caution as the split cannot be interpreted as a sign of significant differences.
+As for this result, though having different signs, the differences in probability are still small (less than 2%) and close to zero.
+Lastly, for the attribute of how much cession of Ukrainian territory a selected profile would result in, we once again found the general attitude towards Ukrainian concessions to predict effect heterogeneity.
+People that selected, that Ukraine should make no concessions, were 16% less likely to select profiles with the 'comparably moderate negative outcome' of Ukraine loosing 8% of their territory (resembling the 2014 Line of Conflict) (vs.
+reference level 'None (0%)').
+For people that did not select the no concessions option, profile selection probabilities for the same attribute level decreased by only 2.4%.
 
@@
 <!-- - short description of factor het results  -->
+
+<!-- -Vergleich mit “normaler” Subgruppen Analyse aka vergleich mit deren paper -->
+However, as already outlined in many other papers, these AMCEs cannot be used to reason about absolute profile selection probabilities but are relative in nature.
+Accordingly a given AMCE has always to be interpreted as change in profile selection probability *relative to a given reference level* of the same attribute.
+This still holds when comparing IMCEs across different subsets of participants, no matter whether these partitions were or are said-to-be defined theory-based or were generated by data (as in the previous approach).
+Accordingly the average IMCEs in the different terminal nodes of the decision trees always are relative to the baseline profile selection probability taking into account the reference level *and* the subgroups of participants.
+The often applied approach of calculating Marginal Means, on the other hand, provides marginalized profile selection probabilities for different attribute levels.
+This allows for straightforward reading off the absolute profile selection probabilities.
+However, as marginal means are solely descriptive, they do not allow for any causal interpretation.
+Accordingly, whether AMCEs or MMs are used should be guided by the kind of conclusions that shall be made.
+As in the present case, the goal was to understand how different subject-level covariates affect decisions-making among different weapon supply attributes, AMCEs provide the right choice for answering this question.
 

### 2024-11-28 1b_Analysis_cjbart.R

@@ -235,37 +235,6 @@ plot_data <- imce_combined %>%
 plot_data <- plot_data %>%
   mutate(AttributeLevel = paste(Attribute, Level, sep = " - "))
 
-# Create the desired order data frame
-desired_orders_df <- data.frame(
-  Attribute = c(rep("Sold_killed_UKR", 2),
-                rep("Sold_killed_RUS", 2),
-                rep("Civ_killed_UKR", 2),
-                rep("Infra_Destr_UKR", 2),
-                rep("Perc_GDP_milit", 2),
-                rep("Perc_GDP_econ", 2),
-                rep("Risk_Nuke", 2),
-                rep("Territ_Cession", 3),
-                rep("Polit_Self_Det_UKR", 2)),
-  Level = c("25,000", "50,000", 
-            "50,000.", "100,000", 
-            "8,000", "16,000", 
-            "100B", "200B",
-            "0.2% of GDP", "0.3% of GDP", 
-            "0.2% of GDP.", "0.3% of GDP.", 
-            "Low (5%)", "Moderate (10%)", 
-            "Crimea (4%)", "2014 LoC (8%)", "2023 LoC (16%)",
-            "No EU/NATO", "Russian influence"),
-  global_order = 1:19
-)
-
-# Merge desired order into plot_data
-plot_data <- plot_data %>%
-  left_join(desired_orders_df, by = c("Attribute", "Level"))
-
-# Reorder the levels of AttributeLevel according to global_order
-plot_data$AttributeLevel <- factor(plot_data$AttributeLevel, 
-                                   levels = plot_data$AttributeLevel[order(-plot_data$global_order)])
-plot_data <- plot_data[order(plot_data$global_order), ]
 
 # Define baseline levels with IMCE = 0
 baseline_levels <- data.frame(
@@ -283,48 +252,104 @@ baseline_levels <- data.frame(
 plot_data <- plot_data %>%
   bind_rows(baseline_levels)
 
-# Update global order to ensure baselines are first within their attributes
+
+# Create the desired order data frame
+desired_orders_df <- data.frame(
+  Attribute = c(rep("Sold_killed_UKR", 3),
+                rep("Sold_killed_RUS", 3),
+                rep("Civ_killed_UKR", 3),
+                rep("Infra_Destr_UKR", 3),
+                rep("Perc_GDP_milit", 3),
+                rep("Perc_GDP_econ", 3),
[…]

### 2024-11-28 Manuscript files/Manuscript.qmd
Tables attributes and covs

@@
 format: pdf
+pdf-engine: xelatex
+header-includes:
+  - \usepackage{array}
+  - \usepackage{ragged2e}
+  - \setlength{\extrarowheight}{2pt}
+  - \renewcommand{\arraystretch}{1.5}  # Adjust row spacing
 floatsintext: yes
@@
 We fitted a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
-A list of all covariates, including their type, can be found in TABLE.
+A list of all covariates, including their type, can be found in @tbl-covariates.
 This resulted in a trained BART model that was used to make the (counterfactual) predictions needed for calculating the quantities of interest, such as IMCEs or AMCEs.
@@
 ```{r covariates, echo=FALSE}
-#| output: asis
+#| echo: false
+#| results: asis
+#| label: tbl-covariates
+
+library(knitr)
 library(kableExtra)
 
-attrib <- data.frame(Attribute = c("Number of Ukrainian soldiers killed?",
-                                   "Number of Russian soldiers killed?",
-                                   "Number of Ukrainian civilians killed?",
-                                   "Value of destroyed infrastructure in Ukraine?",
-                                   "[Country] contribution to military aid to Ukraine?",
-                                   "[Country] contribution to economic aid to Ukraine?",
-                                   "Risk of a Russian nuclear strike on Ukraine?",
-                                   "How much political self-determination of Ukraine?",
-                                   "Territorial cessions of Ukraine to Russia?"),
-                     Attribute_Levels = c("1. 12,500 <br> 2. 25,000 <br> 3. 50,000",
-                                          "1. 25,000 <br> 2. 50,000 <br> 3. 100,000",
-                                          "1. 4,000 <br> 2. 8,000 <br> 3. 16,000",
-                                          "1. $50B <br> 2. $100B <br> 3. $200B",
-                                          "1. X bn (0.1% of [Country] GDP) <br> 2. X bn (0.2% of [Country] GDP) <br> 3. X bn (0.3% of [Country] GDP)",
-                                          "1. X bn (0.1% of [Country] GDP) <br> 2. X bn (0.2% of [Country] GDP) <br> 3. X bn (0.3% of [Country] GDP)",
-                                          "1. Not present (0%) <br> 2. Low (5%) <br> 3. Moderate (10%)",
-                                          "1. Full self-determination <br> 2. No NATO/EU membership <br> 3. Russian influence over Ukr. gov.",
-                                          "1. No cessions of territory <br> 2. Crimea (ca. 4% of land) <br> 3. 2014 Line of Conflict (ca. 8%) <br> 4. 2023 Line of Conflict (ca. 16%)"),
-                     Reference = c("12,500",
-                                   "25,000",
-                                   "4,000",
-                                   "$50B",
-                                   "0.1% of GDP",
-                                   "0.1% of GDP",
-                                   "Not present (0%)",
-                                   "Full self-determination",
-                                   "No cessions of territory"))
+covs <- data.frame(
+  Covariates = c(
+    "Country",
+    "Age",
+    "Gender",
+    "Political Orientation",
+    "The political agenda should focus <br> on the war against Ukraine.",
+    "How scared are you by the <br> Russian war against Ukraine?",
+    "Does military support of [country] matter <br> regarding your current voting intention?",
+    "The US-American imperialism is <br> the real threat to world peace.",
+    "I can see why Russia feels <br> threatened by the West.",
+    "Would you say that your general opinion <br> of the NATO is very positive, slightly positive, neither positive nor negative, slightly negative, or very negative?",
+    "Ukraine should waive a NATO <br> membership if this would bring peace.",
+    "Ukraine should not make <br> any cessions to achieve peace.",
+    "Trading or deliveries of weapons <br> between countries should be prohibited.",
+    "If a country is being attacked and <br> the aggressor is targeting civilians, <br> [country] should provide military support.",
+    "If a country is being attacked and <br> the aggressor is targeting critical <br> infrastructure (e.g., hospitals or electricity <br> and water supply), [country] should provide military support.",
+    "If a country is being attacked (without <br> actual fault) and the aggressor is taking <br> away its land, [country] should provide <br> military support."
+  ),
+  Scale_level = c(
+    "Categorical with 5 levels: <br> Germany, UK, USA, France, Italy",
+    "Continuous",
+    "Categorical with 2 levels: <br> male and female",
+    "Categorical with 3 levels: <br> left, middle, right",
+    "Categorical: 6-point Likert scale",
+    "Categorical: 7-point Likert scale <br> (<em>not scared at all</em> to <em>very scared</em>)",
+    "Categorical: 4-point Likert scale <br> (<em>matters a lot</em> to <em>does not matter at all</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 5-point Likert scale <br> (<em>very positive</em> to <em>very negative</em>)",
+    "Categorical with 2 levels: yes and no",
+    "Categorical with 2 levels: yes and no",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)"
+  )
+)
 
-knitr::kable(attrib, 
+knitr::kable(covs, 
              format = "html", 
-             col.names = c("Attribute", "Attribute Levels", "Reference Category"), 
+             col.names = c("Covariates", "Scale Level"), 
              escape = FALSE,
-             caption = "Attributes, attribute levels, and reference categories used in the analyses.")
+             caption = "Covariates and corresponding scale levels used in the analyses.")
 

### 2024-11-28 Manuscript files/Manuscript.qmd
Formatting

--- 2024-11-28 Manuscript files/Manuscript.qmd
@@
 # Method
+
 Data of the above conjoint experiment was modeled by the previously described cjbart approach.
@@
 ```{r covariates, echo=FALSE}
-#| output: asis
+#| echo: false
+#| results: asis
+#| label: tbl-covariates
+
+library(knitr)
 library(kableExtra)
 
-attrib <- data.frame(Attribute = c("Number of Ukrainian soldiers killed?",
-                                   "Number of Russian soldiers killed?",
-                                   "Number of Ukrainian civilians killed?",
-                                   "Value of destroyed infrastructure in Ukraine?",
-                                   "[Country] contribution to military aid to Ukraine?",
-                                   "[Country] contribution to economic aid to Ukraine?",
-                                   "Risk of a Russian nuclear strike on Ukraine?",
-                                   "How much political self-determination of Ukraine?",
-                                   "Territorial cessions of Ukraine to Russia?"),
-                     Attribute_Levels = c("1. 12,500 <br> 2. 25,000 <br> 3. 50,000",
-                                          "1. 25,000 <br> 2. 50,000 <br> 3. 100,000",
-                                          "1. 4,000 <br> 2. 8,000 <br> 3. 16,000",
-                                          "1. $50B <br> 2. $100B <br> 3. $200B",
-                                          "1. X bn (0.1% of [Country] GDP) <br> 2. X bn (0.2% of [Country] GDP) <br> 3. X bn (0.3% of [Country] GDP)",
-                                          "1. X bn (0.1% of [Country] GDP) <br> 2. X bn (0.2% of [Country] GDP) <br> 3. X bn (0.3% of [Country] GDP)",
-                                          "1. Not present (0%) <br> 2. Low (5%) <br> 3. Moderate (10%)",
-                                          "1. Full self-determination <br> 2. No NATO/EU membership <br> 3. Russian influence over Ukr. gov.",
-                                          "1. No cessions of territory <br> 2. Crimea (ca. 4% of land) <br> 3. 2014 Line of Conflict (ca. 8%) <br> 4. 2023 Line of Conflict (ca. 16%)"),
-                     Reference = c("12,500",
-                                   "25,000",
-                                   "4,000",
-                                   "$50B",
-                                   "0.1% of GDP",
-                                   "0.1% of GDP",
-                                   "Not present (0%)",
-                                   "Full self-determination",
-                                   "No cessions of territory"))
+covs <- data.frame(
+  Covariates = c(
+    "Country",
+    "Age",
+    "Gender",
+    "Political Orientation",
+    "The political agenda should focus <br> on the war against Ukraine.",
+    "How scared are you by the <br> Russian war against Ukraine?",
+    "Does military support of [country] matter <br> regarding your current voting intention?",
+    "The US-American imperialism is <br> the real threat to world peace.",
+    "I can see why Russia feels <br> threatened by the West.",
+    "Would you say that your general opinion <br> of the NATO is very positive, slightly positive, neither positive nor negative, slightly negative, or very negative?",
+    "Ukraine should waive a NATO <br> membership if this would bring peace.",
+    "Ukraine should not make <br> any concessions to achieve peace.",
+    "Trading or deliveries of weapons <br> between countries should be prohibited.",
+    "If a country is being attacked and <br> the aggressor is targeting civilians, <br> [country] should provide military support.",
+    "If a country is being attacked and <br> the aggressor is targeting critical <br> infrastructure (e.g., hospitals or electricity <br> and water supply), [country] should provide military support.",
+    "If a country is being attacked (without <br> actual fault) and the aggressor is taking <br> away its land, [country] should provide <br> military support."
+  ),
+  Scale_level = c(
+    "Categorical with 5 levels: <br> Germany, UK, USA, France, Italy",
+    "Continuous",
+    "Categorical with 2 levels: <br> male and female",
+    "Categorical with 3 levels: <br> left, middle, right",
+    "Categorical: 6-point Likert scale",
+    "Categorical: 7-point Likert scale <br> (<em>not scared at all</em> to <em>very scared</em>)",
+    "Categorical: 4-point Likert scale <br> (<em>matters a lot</em> to <em>does not matter at all</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 5-point Likert scale <br> (<em>very positive</em> to <em>very negative</em>)",
+    "Categorical with 2 levels: yes and no",
+    "Categorical with 2 levels: yes and no",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)",
+    "Categorical: 7-point Likert scale <br> (<em>do not agree at all</em> to <em>completely agree</em>)"
+  )
+)
 
-knitr::kable(attrib, 
+knitr::kable(covs, 
              format = "html", 
-             col.names = c("Attribute", "Attribute Levels", "Reference Category"), 
+             col.names = c("Covariates", "Scale Level"), 
              escape = FALSE,
-             caption = "Attributes, attribute levels, and reference categories used in the analyses.")
+             caption = "Covariates and corresponding scale levels used in the analyses.")
 
@@
 # Results
+
 In @fig-amces we present the AMCEs estimated by averaging the IMCEs calculated using the cjbart model.
@@
 ## Integration of Results
+
 For AMCEs, theoretically most favorable events served as baseline. 
@@
 ## Methodological Discussion
+
 Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität

### 2024-11-29 Manuscript files/Manuscript.qmd
Meth Discussion

@@
 @fig-varimps-ext displays the variable importance measures for the subject-level covariates as extracted from the cjbart model. 
-Variable Importances are colorized using heatmap-like colorcoding with stronger red (vs.
-white) color indicating larger importance measures.
+Variable Importances are colorized using heatmap-like colorcoding with stronger red (vs. white) color indicating larger importance measures.
 
@@
 As can be seen, increased attribute levels (i.e., less favourable events) were usually linked to significantly decreased levels of support. 
-For example, increasing the risk of a nuclear strike from the reference level 'Not present (0%)' to 'Moderate (10%)' decreased the average probability of a participant choosing the latter profile by about -8.5%.
+For example, increasing the risk of a nuclear strike from the reference level 'Not present (0%)' to 'Moderate (10%)' decreased the average probability of a participant choosing the latter profile by about 8.5 percentage points.
 The AMCE point estimates were in line with the AMCEs reported in CITE, which is why we refrain from an in-depth discussion here and refer the interested reader to CITE.
@@
 Based on this random forest model, we then calculated variable importance measures which served as indicators for variables associated with effect heterogeneity. 
-We found the highest variable importance values for the subject-level covariates Country, Geneder, and the items asking participants about whether they generally support supply of weapons to countries defending themselves against other country's invasions (Q10_10) and whether the Ukraine should make any concessions in order to achieve peace (Q15_7).
+We found the highest variable importance values for the subject-level covariates country, gender, and the items asking participants about whether they generally support supply of weapons to countries defending themselves against other country's invasions (Q10_10) and whether Ukraine should make any concessions in order to achieve peace (Q15_7).
 
@@
 Apart from this, participants' attitude about whether the Ukraine should make any concessions to Russia if this would lead to a peace agreement predicted some level of effect heterogeneity to an interesting extent.
-For example.
-with regards to Russian soldiers killed, people that selected that the Ukraine should not make any concessions, on average were more likely to select profiles with a larger number of Russian military casualties (100,000 vs.
+For example, with regard to Russian soldiers killed, people who responded that Ukraine should not make any concessions, on average were more likely to select profiles with a larger number of Russian military casualties (100,000 vs.
 25,000).
 Interestingly, out of the investigated IMCE decision trees this was the only case for which we observed splits resulting in nodes with different signs meaning that the probability of profile selection decreased in one child node and increased in the other.
-These results have however, to be interpreted with caution as the split cannot be interpreted as a sign of significant differences. 
-As for this result, though having different signs, the differences in probability are still small (less than 2%) and close to zero. 
+These results have, however, to be interpreted with caution as the split cannot be interpreted as a sign of statistically significant differences. 
+As for this result, though having different signs, the differences in probability are still small (less than 2 percentage points) and close to zero. 
 Lastly, for the attribute of how much cession of Ukrainian territory a selected profile would result in, we once again found the general attitude towards Ukrainian concessions to predict effect heterogeneity.
-People that selected, that Ukraine should make no concessions, were 16% less likely to select profiles with the 'comparably moderate negative outcome' of Ukraine loosing 8% of their territory (resembling the 2014 Line of Conflict) (vs.
+People who responded that Ukraine should make no concessions were 16 percentage points less likely to select profiles with the 'comparably moderate negative outcome' of Ukraine loosing 8% of their territory (resembling the 2014 Line of Conflict) (vs.
 reference level 'None (0%)').
-For people that did not select the no concessions option, profile selection probabilities for the same attribute level decreased by only 2.4%.
+For people that did not select the no concessions option, profile selection probabilities for the same attribute level decreased by only 2.4 percentage points.
 
@@
 
-Discussion & Limitations -Tuning -Wie viele Covariates (inference vs. exploration) -Stabilität
+The methodological advantages of cjbart over existing methods to estimate AMCEs and conduct subgroup analyses have been discussed above.
+To briefly recap, cjbart can estimate complex relations regarding attribute level importances, thereby taking potential effect heterogeneity into account.
+Using tree-based follow up analyses, variable importance measures (i.e., which covariates matter for which attribute level) can be calculated.
+Additionally, users can calculate IMCE differences predicted by person-level covariates to investigate heterogeneity in an exploratory manner.
+In closing, we now discuss some important methodological points and potential limitations that should be kept in mind when applying cjbart to conjoint designs.
+
+First, cjbart is, like all tree-based methods, a rather exploratory method.
+This allows for a data-driven investigation of effect heterogeneity without a priori specification of subgroups (when combined with follow-up analyses).
+However, it also impedes a confirmatory approach to answering hypotheses about underlying theories.
+For the follow-up analyses using single decision trees, any reasoning from effects of covariates on IMCEs (e.g., people who oppose concessions for peace agreement favor larger territory cessions less) must be done with caution.
+That is, they cannot readily be interpreted as directed nor as a causal effect of covariates on IMCEs.
+The "naive" approach of investigating attribute levels that stand out in the variable importance heatmap (like we did above), is useful for *hypothesis generation*.
+Effects that were found and that seem to align with political theory could now be investigated in more detail.
+Using appropriate study designs (e.g., experimental settings) or modeling strategies (e.g., confounder adjustment) would now be necessary to investigate the direction of effects and to approach the hypotheses in a more causal manner.
+
+Second, and closely related, while the decision trees offer an easy interpretation of subgroup differences, they do not provide information on whether these differences are statistically significant.
+This is because decision trees as implemented by CITE and also in our article base their split decision on a maximal reduction of *impurity*.
+That is, the goal of decision trees is to partition the data so that observations in the resulting nodes are as homogeneous as possible (in the sense of reduced variance in nodes).
+These splitting decisions are, however, not based on statistical inference.
+Consequently, any two given terminal nodes that show differences (in IMCEs, in our case) do not necessarily show statistically significant differences.
+Domain expertise when interpreting the results is needed to reason about whether the differences are practically meaningful.
+For example, for the result of changed signs in IMCEs reported above, it is a theoretical and content related question whether the difference of around 2 percentage points is relevant.
+A possible extension would be to use a different decision tree algorithm, for example conditional inference trees CITE.
+These types of trees base their split decisions on non-parametric hypotheses tests.
+Nonetheless, domain expertise would still be needed to assess whether a statistically significant split is substantially meaningful.
+
+Third, more simulated and empirical research on cjbart is needed to properly assess the stability of its solutions.
+Internally, the *cjbart()* function as implemented by CITE calls the *mc-pbart()* function from the *BART* package CITE.
+This function estimates complex relations using the BART model described above and uses a seed (which defaults to 99).
+Thus, when repeatedly used on the same data, users should always receive the same results (of AMCEs).
+Simulation studies should be conducted to assess the variability in results when seeds are changed.
+Additional variance in results is then introduced when using random forests to assess variable importances.
+This step should be included in these simulations to investigate whether, and if yes, how strongly changes in BART results are perpetuated in the variable importance results.
+Other factors that might influence cjbarts results are the specific settings of hyperparameters.
+Hyperparameters are second-order parameters that cannot be estimated by the data but that have to be set prior to estimating the model.
+Examples of hyperparameters of the cjbart model are the number of individual trees that are grown sequentially and the number of cut points that are investigated (i.e., the number of "segments" of, for example, age for which a split is considered).
+In our analyses, we used the default values of these hyperparameters (50 trees and 100 cut points).
+However, it would also be possible to tune these values, that is, to try out different settings and choose the most optimal values (with respect to some evaluation metric).
+Because tuning hyperparameters can be computationally expensive, it is an interesting topic of future methodological research to assess whether tuning in the case of cjbart is worth the additional computational burden.
+Tuning hyperparameters would also be possible for the random forest when calculating variable importances.
+However, random forests have been shown to have good performance with default values of its hyperparameters (CITE), so we believe the focus should be on the hyperparameters of the upstream BART model.
+
+HIER NOCH EIN PAAR SÄTZE ZU ANDEREN BEIDEN METHODEN; VORTEILE; NACHTEILE; WARUM BEI UNS CJBART
 

### 2024-11-29 Manuscript files/Manuscript.qmd
Meth discussion

@@
 
-HIER NOCH EIN PAAR SÄTZE ZU ANDEREN BEIDEN METHODEN; VORTEILE; NACHTEILE; WARUM BEI UNS CJBART
-
--weitere Modelle: 
--factorHet + idee kurz 
--CRT + idee kurz 
-Warum cjBart  
-das Modell stark machen
+Forth and last, cjbart is not the only method to take potential heterogeneity in attribute level effects into account.
+As mentioned in the introduction, two other methods are FactorHet by CITE and the CRT approach by CITE.
+FactorHet works based on a Bayesian mixture of regularized logistic regression analyses.
+The goal is to identify maximally heterogeneous groups of respondents for which similar patterns of attribute level effects apply.
+The membership probability to belong to a certain group, also called cluster, is modeled as a function of the person-level covariates.
+This allows users to investigate person characteristics (like country of origin or age) that are indicative of belonging to certain patterns of attribute level effects.
+While this yields interpretable results with regard to the question of "what matters to whom", it has the important downside that the number of clusters is a hyperparameter that has to be set prior to estimating the model.
+Thus, the question arises which model to select.
+It might be a good strategy to estimate the model with different numbers of clusters and then use domain expertise and interpretability
+to choose a solution.
+However, this should be made with caution to not let post-hoc explanation guide the decision.
+Future research concering FactorHet could develop model selection strategies, like information criteria, that are comparable across solutions with differing numbers of clusters and allow for a statistical decision.
+The other method, CRT by CITE, is a statistical hypothesis testing approach based on conditional randomization tests.
+The goal of this approach is to assess a specific attribute of interest influences participants' choice behavior in any way, given all the other attributes.
+The advantage of CRT is that this answers the most basic question one can ask in conjoint experiments, while being assumption-free.
+This is due to the fact that the underlying testing approach works solely on the randomization of attributes.
+However, in these analyses, it remains challenging to investigate the influence of person-level covariates on individual-level preferences (i.e., IMCEs).
+Taken together, all novel approaches have their own strengths and weaknesses when trying to unravel heterogeneity in attribute level effects.
+As in every statistical analyses, the choice of methods and models crucially depends on the research question and desired inferences one wants to make.
+Because our goal was to complement the existing analyses reported by CITE with a maximally exploratory approach, potentially informing future more confirmatory research, we found that cjbart best fits this purpose.
 

### 2024-12-03 Manuscript files/Manuscript.qmd
updates to manuscript TR

@@
 This quantity is estimable by regression models and provides us an effect of an attribute on the probability that a certain option (or profile) will be chosen.
+<!-- TR: compared to the probability of a baseline attribute level -->
 As the name AMCE suggests, this estimate is an average.
@@
 First, it is not clear how to a priori define the subgroups let alone how and where to include certain interactions.
+<!-- often lack of theory, risk of multiple testing issue -->
 If a continuous covariate age is included in the data, arbitrary splits into distinct groups are necessary.
 Potential interaction effects would have to be included manually with the likely chance to miss important ones.
+<!-- TR: with this issue increasing exponentially if subgroups are to be defined based on multiple covariates -->
 Needless to say, sample sizes in the subgroups are always smaller than in the whole sample as well, increasing the uncertainty in estimations.
+<!-- Vielleicht diesen allgemeinen high-dim part weiter nach oben zu den attribut levels? -->
+<!-- dann kann man das Fass mit der double high dimensionality hier aufmachen so nach dem Motto, dass die noch kleineren Subgruppen hier das Problem noch schlimmer machen? -->
 This leads to a second issue: conjoint data can quickly become high-dimensional due to many different pairings of different attribute levels (across attributes).
@@
 From these data we now want to estimate the causal parameters of interest, that is, AMCE, IMCE, RMCE, and OMCE.
-Nested in the AMCE described above, the IMCE is the change in probability that subject *i* choses a profile given a specific attribute level (compared to a reference level of the same attribute), again averaged over the effects of all other attributes.
+Nested in the AMCE described above, the IMCE is the change in probability that subject *i* chooses a profile given a specific attribute level (compared to a reference level of the same attribute), again averaged over the effects of all other attributes.
 This corresponds to subgroup analyses of the AMCE with the convenient addition that the IMCE considers conditional effects based on all possible individual-level covariates.
@@
 CITE detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functional relationship could be used as well.
-BART is a supervised learning model based on a boosting procedure: many small decision trees are trained subsequently, each one aiming to explain the residual variance of the outcome variable which was not explained by all previous trees.
+<!-- habe hier noch ein bisschen was dazu geschrieben  -->
+BART is a supervised learning model somewhat similar to a boosting procedure: across multiple iterations B, K small decision trees are trained subsequently, each one aiming to explain the residual variance of the outcome variable which was not explained by the K-1 previously grown trees.
+Moreover, the trees in subsequent iterations are not 'freshly grown' to fit the residuals but instead are grown by randomly perturbing the very same tree of the previous iteration.
 The "Bayesian part" in BART is that parameters are seen as random variables (instead of constants, as would be the case in frequentist approaches).
+Moreover, priors are placed on growing the trees to favor shallow trees and leaf values close to zero.
+<!-- auch noch was zu MCMC?  -->
 An advantage of BART is its robustness to the choice of hyperparameters (e.g., the number of individual trees) but they could be tuned if necessary, for example by cross-validation.
@@
 
-By combining many weak decision trees, random forest have the advantage of increased predictive performance.
+By combining many weak decision trees, random forests have the advantage of increased predictive performance.
 However, this advantage comes at the cost of interpretability.

### 2024-12-04 Manuscript files/Manuscript.qmd
TR: Updates to Manuscript

@@
 
-Following the nested causal quantities structure outlines above, IMCEs are calculated by averaging the OMCEs for each individual.
+Following the nested structure of causal quantities outlines above, IMCEs are calculated by averaging the OMCEs for each individual.
 Specifically, the OMCE estimates from step 2 are summed and divided by $J \times K$, that is, the number of profiles times the number of rounds (which is the number of total observations).
+<!-- Sollen wir (wie im Paper) noch dazuschreiben, dass man basierend auf den Posterior Draws der OMCEs auch Credibility Intervals basteln kann, dann würde vielleicht auch der Bayesian Aspekt nochmal betont werden -->
 
@@
 Briefly, the VIMPs are calculated by permuting the covariates (i.e., by introducing random noise to its values).
+<!-- nit: is random noise introduced (in terms of: added) or more the complete information on the variable destroyed by permuting all the values in X -->
 If predictions change noticeably, this is an indication that the covariate is important for predicting the outcome (i.e., IMCE distributions).
@@
 
+<!-- falls wir Platz sparen oder die Tabelle auf eine Seite bekommen wollen: Reference Category mit Asterisk oder so anzeichnen, dann haben wir nur 2 Spalten und weniger Zeilenumbrüche vermutlich -->
+<!-- Sollen wir hier noch ihre theoretischen 4 Cluster kurz reinschreiben?
+Also im Text oder in der Tabelle?
+Diese Aufteilung in Human Costs, Costs of Aid, Strategic Risks, Containment of Aggression (resolve)?
+-->
 ```{r attributes, echo=FALSE}
@@
 
+These AMCEs are supplemented with the AMCEs reported in the original preprint by CITE, presented in @fig-amces-preprint.
+
+![Preprint AMCEs](figures/AMCEs_Original_Preprint.png){#fig-amces-preprint}
+
 @fig-varimps-ext displays the variable importance measures for the subject-level covariates as extracted from the cjbart model. 
@@
 The AMCE point estimates were in line with the AMCEs reported in CITE, which is why we refrain from an in-depth discussion here and refer the interested reader to CITE.
-HIER WAS DAZU SCHREIBEN DAS WIR HÖHERE SEs HABEN? DAZU SCHREIBEN DIE HALT IN IHREM PAPER EH GAR NIX
+HIER WAS DAZU SCHREIBEN, DASS WIR HÖHERE SEs HABEN? DAZU SCHREIBEN DIE HALT IN IHREM PAPER EH GAR NIX
 
-As a next step, we predicted the subject-level IMCEs using the subject-level covariates. 
-Based on this random forest model, we then calculated variable importance measures which served as indicators for variables associated with effect heterogeneity. 
+As a next step, we fit a random forest model to predict subject-level IMCEs using the subject-level covariates. 
+Based on this model, we then calculated variable importance measures which served as indicators for variables associated with effect heterogeneity. 
+<!-- Wie sollen wir hier auf die Items referenzieren? brauchen vermutlich Item Kurznamen -->
 We found the highest variable importance values for the subject-level covariates country, gender, and the items asking participants about whether they generally support supply of weapons to countries defending themselves against other country's invasions (Q10_10) and whether Ukraine should make any concessions in order to achieve peace (Q15_7).
 
-These variable importance measures do not provide any more interpretability than which covariates in general seem to matter, which is why we further substantiated the previous analysis by fitting single decision trees to different IMCEs.
-IMCEs for this were selected due to content-related purposes and to highlight how decision trees facilitate interpretation of effect heterogeneity. 
-As can be seen in @image-panel (upper left panel), for participants from countries different to the UK the probability to select a given profile decreased by -12.5% if the respective profile was associated with 16,000 (vs.
+As already outlined, these variable importance measures do not provide any more interpretability than which covariates in general seem to matter.
+This is why we further substantiated the previous analysis by fitting single decision trees to different IMCEs. 
+IMCEs for this were selected based on contentual characteristics and to highlight how decision trees facilitate interpretation of effect heterogeneity. 
+As can be seen in @image-panel (panel a), for participants from countries different to the UK the probability to select a given profile decreased by -12.5 percentage points if the respective profile was associated with 16,000 (vs.
 4,000) Ukrainian civilian casualties.
 For participants from the UK, the larger number of civilian casualties was also linked to a lower profile selection probability, although, the attribute level was less influential for their decision. 
-In general, we saw the UK vs other countries split in many different trees possibly indicating slight differences in attitudes towards weapon supplies across these countries. 
-Moreover, whether participants were female (within both UK and Non-UK subgroups) predicted
+In general, many trees performed splits based on whether participants were from the UK or the other countries included. 
+For example, this was also the case for the attribute regarding the risk of a nuclear strike when comparing the risk of '10%' with the reference level of '0%' (@image-panel (panel c).
+These UK versus Non-UK splits possibly indicate slight differences in attitudes towards weapon supplies across these countries. 
+Moreover, for female participants (within both UK and Non-UK subgroups) the probability for selecting profiles with 16,000 vs.
+4,000 Ukrainian civilian casualties, decreased stronger than for male participants, although differences were less pronounced than for the country covariate.
 
 Apart from this, participants' attitude about whether the Ukraine should make any concessions to Russia if this would lead to a peace agreement predicted some level of effect heterogeneity to an interesting extent.
-For example, with regard to Russian soldiers killed, people who responded that Ukraine should not make any concessions, on average were more likely to select profiles with a larger number of Russian military casualties (100,000 vs.
+For example, with regard to Russian soldiers killed (@image-panel (panel b), people who responded that Ukraine should not make any concessions, had a higher probability to select profiles with a larger number of Russian military casualties (100,000 vs.
 25,000).
 Interestingly, out of the investigated IMCE decision trees this was the only case for which we observed splits resulting in nodes with different signs meaning that the probability of profile selection decreased in one child node and increased in the other.
-These results have, however, to be interpreted with caution as the split cannot be interpreted as a sign of statistically significant differences. 
-As for this result, though having different signs, the differences in probability are still small (less than 2 percentage points) and close to zero. 
-Lastly, for the attribute of how much cession of Ukrainian territory a selected profile would result in, we once again found the general attitude towards Ukrainian concessions to predict effect heterogeneity.
+<!-- @Philipp: hast du hier gut ne Quelle, mit der wir einfach sagen können dass die Bäume basierend auf Impurity splitten und das eben nicht signifikanz bedeutet -->
+These results have, however, to be interpreted with caution as the split cannot be interpreted as a sign of statistically significant differences between the terminal nodes. 
+Moreover, for this result, though having different signs, the differences in probability are still small (less than 2 percentage points) and close to zero. 
+Lastly, for the attribute regarding how much cession of Ukrainian territory a selected profile would result in (@image-panel (panel d), we once again found the general attitude towards Ukrainian concessions to predict effect heterogeneity.
 People who responded that Ukraine should make no concessions were 16 percentage points less likely to select profiles with the 'comparably moderate negative outcome' of Ukraine loosing 8% of their territory (resembling the 2014 Line of Conflict) (vs.
@@
 <!-- -Vergleich mit “normaler” Subgruppen Analyse aka vergleich mit deren paper -->
-However, as already outlined in many other papers, these AMCEs cannot be used to reason about absolute profile selection probabilities but are relative in nature. 
+However, as already outlined by many authors (CITE), thes above AMCEs cannot be used to reason about absolute profile selection probabilities but instead are relative in nature. 
 Accordingly a given AMCE has always to be interpreted as change in profile selection probability *relative to a given reference level* of the same attribute. 
-This still holds when comparing IMCEs across different subsets of participants, no matter whether these partitions were or are said-to-be defined theory-based or were generated by data (as in the previous approach).
+This still holds when comparing IMCEs across different subsets of participants, no matter whether these partitions were (or were said-to-be) defined theory-based (as in classical subgroup analysis) or generated in a more data-driven manner (as in the previous approach).
 Accordingly the average IMCEs in the different terminal nodes of the decision trees always are relative to the baseline profile selection probability taking into account the reference level *and* the subgroups of participants.
-The often applied approach of calculating Marginal Means, on the other hand, provides marginalized profile selection probabilities for different attribute levels. 
+Accordingly, in order to reason about the absolute selection probability for a given attribute level using the associated AMCE, the absolute selection probability for the respective reference level must be known.
+The often applied approach of calculating Marginal Means, provides exactly these marginalized absolute profile selection probabilities for different attribute levels. 
 This allows for straightforward reading off the absolute profile selection probabilities. 
 However, as marginal means are solely descriptive, they do not allow for any causal interpretation. 
-Accordingly, whether AMCEs or MMs are used should be guided by the kind of conclusions that shall be made. 
-As in the present case, the goal was to understand how different subject-level covariates affect decisions-making among different weapon supply attributes, AMCEs provide the right choice for answering this question.
-
--Vergleich mit “normaler” Subgruppen Analyse --> aka vergleich mit deren paper
+Accordingly, whether AMCEs or Marginal Means are used should be guided by the kind of conclusions that shall be made. 
+As in the present case, the goal was to understand how different subject-level covariates affect decisions-making in the presence of different weapon supply attributes, AMCEs provide the right choice for answering this question.
 
@@
 Internally, the *cjbart()* function as implemented by CITE calls the *mc-pbart()* function from the *BART* package CITE.
+<!-- Nur auf Mac ... :D  -->
 This function estimates complex relations using the BART model described above and uses a seed (which defaults to 99).
@@
 This allows users to investigate person characteristics (like country of origin or age) that are indicative of belonging to certain patterns of attribute level effects.
+<!-- Sollen wir hier einfach die Plots noch irgendwie in einen Appendix packen?
+ist zwar nicht Paper-Style aber so als Bericht ja vielleicht nich schlecht?
+Nachdem wir uns die Arbeit ja gemacht haben, könnte man das ja vielleicht schon machen?
+-->
 While this yields interpretable results with regard to the question of "what matters to whom", it has the important downside that the number of clusters is a hyperparameter that has to be set prior to estimating the model.
@@
 However, this should be made with caution to not let post-hoc explanation guide the decision.
-Future research concering FactorHet could develop model selection strategies, like information criteria, that are comparable across solutions with differing numbers of clusters and allow for a statistical decision.
+Future research concerning FactorHet could develop model selection strategies, like information criteria, that are comparable across solutions with differing numbers of clusters and allow for a statistical decision.
 The other method, CRT by CITE, is a statistical hypothesis testing approach based on conditional randomization tests.
-The goal of this approach is to assess a specific attribute of interest influences participants' choice behavior in any way, given all the other attributes.
+The goal of this approach is to assess whether a specific attribute of interest influences participants' choice behavior in any way, given all the other attributes.
 The advantage of CRT is that this answers the most basic question one can ask in conjoint experiments, while being assumption-free.
@@
 Taken together, all novel approaches have their own strengths and weaknesses when trying to unravel heterogeneity in attribute level effects.
-As in every statistical analyses, the choice of methods and models crucially depends on the research question and desired inferences one wants to make.
+As in every statistical analysis, the choice of methods and models crucially depends on the research question and desired inferences one wants to make.
 Because our goal was to complement the existing analyses reported by CITE with a maximally exploratory approach, potentially informing future more confirmatory research, we found that cjbart best fits this purpose.

### 2024-12-04 1b_Analysis_cjbart.R

@@ -95,13 +95,16 @@ vars_ext = c(
 #####' *Fit the models*
 ### Fit the reduced model
 set.seed(13.9238239)
+
+# function has default seed 99 implented 
 fit_cjbart_red = cjbart(data = cj_tidy[, vars_red], 
                         Y = "y",
                         type = "choice", 
                         id = "c_id", 
                         round = "task", 
                         use_round = TRUE, 
-                        cores = 4)
+                        cores = 4,
+                        seed = 99)
 
 # saveRDS(fit_cjbart_red, "1c_Model_Objects/2024-11-18_fit_cjbart_red_2.rds")
 fit_cjbart_red <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_red.rds")
@@ -115,6 +118,7 @@ fit_cjbart_ext6_noround = cjbart(data = cj_tidy[, vars_ext],
                         id = "c_id", 
                         # round = "task", 
                         # use_round = TRUE, 
+                        seed = 99,
                         cores = 4)
 
 saveRDS(fit_cjbart_ext6_noround, "1c_Model_Objects/2024-11-18_fit_cjbart_ext6_noround.rds")

### 2024-12-04 Manuscript files/Manuscript.qmd
updates to plots

@@
                                    "Risk of a Russian nuclear strike on Ukraine?",
-                                   "How much political self-determination of Ukraine?",
-                                   "Territorial cessions of Ukraine to Russia?"),
+                                   "Territorial cessions of Ukraine to Russia?",
+                                   "How much political self-determination of Ukraine?"),
                      Attribute_Levels = c("1. 12,500 <br> 2. 25,000 <br> 3. 50,000",
@@
                                           "1. Not present (0%) <br> 2. Low (5%) <br> 3. Moderate (10%)",
-                                          "1. Full self-determination <br> 2. No NATO/EU membership <br> 3. Russian influence over Ukr. gov.",
-                                          "1. No cessions of territory <br> 2. Crimea (ca. 4% of land) <br> 3. 2014 Line of Conflict (ca. 8%) <br> 4. 2023 Line of Conflict (ca. 16%)"),
+                                          "1. No cessions of territory <br> 2. Crimea (ca. 4% of land) <br> 3. 2014 Line of Conflict (ca. 8%) <br> 4. 2023 Line of Conflict (ca. 16%)",
+                                          "1. Full self-determination <br> 2. No NATO/EU membership <br> 3. Russian influence over Ukr. gov."),
                      Reference = c("12,500",
@@
                                    "Not present (0%)",
-                                   "Full self-determination",
-                                   "No cessions of territory"))
+                                   "No cessions of territory",
+                                   "Full self-determination"))
 
@@
 
-![AMCEs](figures/AMCEs.png){#fig-amces}
+![AMCEs](figures/AMCEs_as_cjbart.png){#fig-amces}
 
@@
 
+<!-- Aproach to get the 2 figures on the same page...  -->
+<!-- ::: {.figure} -->
+<!--   ![AMCEs](figures/AMCEs_as_cjbart.png){#fig-amces width="100%"} -->
+
+<!--   ![Preprint AMCEs](figures/AMCEs_Original_Preprint.png){#fig-amces-preprint width="100%"} -->
+
+<!-- ::: -->
+
 @fig-varimps-ext displays the variable importance measures for the subject-level covariates as extracted from the cjbart model. 
@@
 
-![Ext VarImps](figures/RF_VarImps_ext_v2.png){#fig-varimps-ext}
+![Ext VarImps](figures/RF_VarImps_ext_v3.png){#fig-varimps-ext}
 

### 2024-12-04 1b_Analysis_cjbart.R

@@ -78,7 +78,7 @@ vars_red = c(
 vars_ext = c(
   # General variables
   'y', 'c_id', 
-  # 'task',
+  'task',
   # Attributes
   "Sold_killed_UKR", "Sold_killed_RUS", "Civ_killed_UKR",
   "Infra_Destr_UKR", "Perc_GDP_milit", "Perc_GDP_econ",
@@ -112,17 +112,19 @@ fit_cjbart_red <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_red.rds")
 
 ### Fit the extended model
 set.seed(123)
-fit_cjbart_ext6_noround = cjbart(data = cj_tidy[, vars_ext], 
+fit_cjbart_ext = cjbart(data = cj_tidy[, vars_ext], 
                         Y = "y",
                         # type = "choice", 
                         id = "c_id", 
-                        # round = "task", 
-                        # use_round = TRUE, 
+                        round = "task", 
+                        use_round = TRUE, 
                         seed = 99,
                         cores = 4)
 
-saveRDS(fit_cjbart_ext6_noround, "1c_Model_Objects/2024-11-18_fit_cjbart_ext6_noround.rds")
+# saveRDS(fit_cjbart_ext6_noround, "1c_Model_Objects/2024-11-18_fit_cjbart_ext6_noround.rds")
 fit_cjbart_ext <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
+
+
 
 
 #####' *Get IMCEs*
@@ -186,9 +188,176 @@ imces_ext <- IMCE(data = cj_tidy[, vars_ext],
                   # ,method = 'parametric'
                   , cores = 4
 )
+summary.cjbart(imces_ext)
 
 # saveRDS(imces_ext, "1c_Model_Objects/2024-11-18_imces_ext_2.rds")
 imces_ext <- readRDS("1c_Model_Objects/2024-11-18_imces_ext.rds")
+
+
+
+
+# Get AMCEs
+amces_ext <- AMCE(cj_tidy[, vars_ext], 
+              model = fit_cjbart_ext,
+              attribs = c("Sold_killed_UKR"
+                          , "Sold_killed_RUS"
+                          , "Civ_killed_UKR"
+                          , "Infra_Destr_UKR"
+                          , "Perc_GDP_milit"
+                          , "Perc_GDP_econ"
+                          , "Risk_Nuke"
+                          , "Territ_Cession"
+                          , "Polit_Self_Det_UKR"
+              ), 
[…]

### 2024-12-05 Manuscript files/Manuscript.qmd
Small changes

@@
 To remedy the downsides of the "naive" subgroup approach outlined above, researchers developed more advanced methods based on machine learning.
-Most notable in this regard are (a) an approach based on *Bayesian additive regression trees* (in the following called *cjbart* CITE), (b) an approach based on Bayesian mixture of regularized logistic regressions (*FactorHet* CITE), and (c) a testing approach based on conditional randomization tests (*CRT* CITE).
+Most notable in this regard are (a) an approach based on *Bayesian additive regression trees* (in the following called *cjbart* CITE), (b) an approach based on a Bayesian mixture of regularized logistic regressions (*FactorHet* CITE), and (c) a testing approach based on conditional randomization tests (*CRT* CITE).
 In this article, we focus on the explanation and demonstration of cjbart.
-At the end of this section, we briefly delineate similarities and differences in these three approaches.
+At the end of this article, we briefly delineate similarities and differences between these three approaches.
 
@@
 <!-- habe hier noch ein bisschen was dazu geschrieben  -->
-BART is a supervised learning model somewhat similar to a boosting procedure: across multiple iterations B, K small decision trees are trained subsequently, each one aiming to explain the residual variance of the outcome variable which was not explained by the K-1 previously grown trees.
+BART is a supervised learning model somewhat similar to a boosting procedure: across multiple iterations *B*, *M* small decision trees are trained subsequently, each one aiming to explain the residual variance of the outcome variable which was not explained by the $M-1$ previously grown trees.
 Moreover, the trees in subsequent iterations are not 'freshly grown' to fit the residuals but instead are grown by randomly perturbing the very same tree of the previous iteration.
 The "Bayesian part" in BART is that parameters are seen as random variables (instead of constants, as would be the case in frequentist approaches).
-Moreover, priors are placed on growing the trees to favor shallow trees and leaf values close to zero.
+Moreover, priors are placed on growing the trees to favor shallow trees and values in child nodes close to zero.
 <!-- auch noch was zu MCMC?  -->
@@
                                           "1. No cessions of territory <br> 2. Crimea (ca. 4% of land) <br> 3. 2014 Line of Conflict (ca. 8%) <br> 4. 2023 Line of Conflict (ca. 16%)",
-                                          "1. Full self-determination <br> 2. No NATO/EU membership <br> 3. Russian influence over Ukr. gov."),
-                     Reference = c("12,500",
-                                   "25,000",
-                                   "4,000",
-                                   "$50B",
-                                   "0.1% of GDP",
-                                   "0.1% of GDP",
-                                   "Not present (0%)",
-                                   "No cessions of territory",
-                                   "Full self-determination"))
+                                          "1. Full self-determination <br> 2. No NATO/EU membership <br> 3. Russian influence over Ukr. gov."))
 
@@
              format = "html", 
-             col.names = c("Attribute", "Attribute Levels", "Reference Category"), 
+             col.names = c("Attribute", "Attribute Levels"), 
              escape = FALSE,
-             caption = "Attributes, attribute levels, and reference categories used in the analyses.")
+             caption = "Attributes and attribute levels used in the analyses. (As reference category we used the first attribute level of each attribute)")
 
@@
 For this, we used the R package *cjbart* described in CITE.
-We fitted a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
+We fit a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
 A list of all covariates, including their type, can be found in @tbl-covariates.
@@
 @fig-varimps-ext displays the variable importance measures for the subject-level covariates as extracted from the cjbart model. 
-Variable Importances are colorized using heatmap-like colorcoding with stronger red (vs. white) color indicating larger importance measures.
+Variable importances are colorized using heatmap-like colorcoding with stronger red (vs. white) color indicating larger importance measures.
 
@@
 
-@fig-imagepanel depicts 4 exemplary decision trees that were fitted to better understand how different subject level covariates contribute to effect heterogeneity. 
+@fig-imagepanel depicts 4 exemplary decision trees that were fit to better understand how different subject level covariates contribute to effect heterogeneity. 
 These decision trees were selected based on content-related and interpretational criteria and to highlight how single decision tress can be utilized for model interpretation.
@@
 
-For AMCEs, theoretically most favorable events served as baseline. 
+For AMCEs, theoretically most favorable events served as reference categories (e.g., least amount of soldiers killed). 
 As can be seen, increased attribute levels (i.e., less favourable events) were usually linked to significantly decreased levels of support. 
@@
 The AMCE point estimates were in line with the AMCEs reported in CITE, which is why we refrain from an in-depth discussion here and refer the interested reader to CITE.
-HIER WAS DAZU SCHREIBEN, DASS WIR HÖHERE SEs HABEN? DAZU SCHREIBEN DIE HALT IN IHREM PAPER EH GAR NIX
 
@@
 Based on this model, we then calculated variable importance measures which served as indicators for variables associated with effect heterogeneity. 
-<!-- Wie sollen wir hier auf die Items referenzieren? brauchen vermutlich Item Kurznamen -->
-We found the highest variable importance values for the subject-level covariates country, gender, and the items asking participants about whether they generally support supply of weapons to countries defending themselves against other country's invasions (Q10_10) and whether Ukraine should make any concessions in order to achieve peace (Q15_7).
+We found the highest variable importance values for the subject-level covariates country, gender, and the items asking participants about whether they generally support supply of weapons to countries defending themselves against other country's invasions and whether Ukraine should make any concessions in order to achieve peace.
 
@@
 IMCEs for this were selected based on contentual characteristics and to highlight how decision trees facilitate interpretation of effect heterogeneity. 
-As can be seen in @image-panel (panel a), for participants from countries different to the UK the probability to select a given profile decreased by -12.5 percentage points if the respective profile was associated with 16,000 (vs.
+As can be seen in @fig-imagepanel (panel a), for participants from countries different to the UK the probability to select a given profile decreased by -12.5 percentage points if the respective profile was associated with 16,000 (vs.
 4,000) Ukrainian civilian casualties.
@@
 In general, many trees performed splits based on whether participants were from the UK or the other countries included. 
-For example, this was also the case for the attribute regarding the risk of a nuclear strike when comparing the risk of '10%' with the reference level of '0%' (@image-panel (panel c).
+For example, this was also the case for the attribute regarding the risk of a nuclear strike when comparing the risk of '10%' with the reference level of '0%' (@fig-imagepanel, panel c).
 These UK versus Non-UK splits possibly indicate slight differences in attitudes towards weapon supplies across these countries. 
@@
 Apart from this, participants' attitude about whether the Ukraine should make any concessions to Russia if this would lead to a peace agreement predicted some level of effect heterogeneity to an interesting extent.
-For example, with regard to Russian soldiers killed (@image-panel (panel b), people who responded that Ukraine should not make any concessions, had a higher probability to select profiles with a larger number of Russian military casualties (100,000 vs.
+For example, with regard to Russian soldiers killed (@fig-imagepanel, panel b), people who responded that Ukraine should not make any concessions, had a higher probability to select profiles with a larger number of Russian military casualties (100,000 vs.
 25,000).
@@
 Moreover, for this result, though having different signs, the differences in probability are still small (less than 2 percentage points) and close to zero. 
-Lastly, for the attribute regarding how much cession of Ukrainian territory a selected profile would result in (@image-panel (panel d), we once again found the general attitude towards Ukrainian concessions to predict effect heterogeneity.
+Lastly, for the attribute regarding how much cession of Ukrainian territory a selected profile would result in (@fig-imagepanel, panel d), we once again found the general attitude towards Ukrainian concessions to predict effect heterogeneity.
 People who responded that Ukraine should make no concessions were 16 percentage points less likely to select profiles with the 'comparably moderate negative outcome' of Ukraine loosing 8% of their territory (resembling the 2014 Line of Conflict) (vs.
@@
 
-<!-- -Vergleich mit factorHet eher raus -->
-<!-- - short description of factor het results  -->
-
-<!-- -Vergleich mit “normaler” Subgruppen Analyse aka vergleich mit deren paper -->
 However, as already outlined by many authors (CITE), thes above AMCEs cannot be used to reason about absolute profile selection probabilities but instead are relative in nature. 
@@
 This still holds when comparing IMCEs across different subsets of participants, no matter whether these partitions were (or were said-to-be) defined theory-based (as in classical subgroup analysis) or generated in a more data-driven manner (as in the previous approach).
-Accordingly the average IMCEs in the different terminal nodes of the decision trees always are relative to the baseline profile selection probability taking into account the reference level *and* the subgroups of participants.
-Accordingly, in order to reason about the absolute selection probability for a given attribute level using the associated AMCE, the absolute selection probability for the respective reference level must be known.
-The often applied approach of calculating Marginal Means, provides exactly these marginalized absolute profile selection probabilities for different attribute levels. 
+Accordingly the average IMCEs in the different terminal nodes of the decision trees are always relative to the baseline profile selection probability taking into account the reference level *and* the subgroups of participants.
+In order to reason about the absolute selection probability for a given attribute level using the associated AMCE, the absolute selection probability for the respective reference level must be known. 
+The often applied approach of calculating marginal means, provides exactly these marginalized absolute profile selection probabilities for different attribute levels. 
 This allows for straightforward reading off the absolute profile selection probabilities. 
 However, as marginal means are solely descriptive, they do not allow for any causal interpretation. 
-Accordingly, whether AMCEs or Marginal Means are used should be guided by the kind of conclusions that shall be made. 
-As in the present case, the goal was to understand how different subject-level covariates affect decisions-making in the presence of different weapon supply attributes, AMCEs provide the right choice for answering this question.
+Accordingly, whether AMCEs or marginal means are used should be guided by the kind of conclusions that shall be made. 
+As in the present case the goal was to understand how different subject-level covariates affect decisions-making in the presence of different weapon supply attributes, AMCEs are the right choice for answering this question.
 
@@
 Internally, the *cjbart()* function as implemented by CITE calls the *mc-pbart()* function from the *BART* package CITE.
-<!-- Nur auf Mac ... :D  -->
-This function estimates complex relations using the BART model described above and uses a seed (which defaults to 99).
+This function estimates complex relations using the BART model described above and uses a seed[^seed] (which defaults to 99).
 Thus, when repeatedly used on the same data, users should always receive the same results (of AMCEs).
@@
 
+[^seed]: It should be highlighted that the function-internal seed does not work on machines with a Windows operating system.
+Consequently, each function call to *cjbart()* might result in (slightly) different results.
+
 Forth and last, cjbart is not the only method to take potential heterogeneity in attribute level effects into account.
@@
 This allows users to investigate person characteristics (like country of origin or age) that are indicative of belonging to certain patterns of attribute level effects.
-<!-- Sollen wir hier einfach die Plots noch irgendwie in einen Appendix packen?
-ist zwar nicht Paper-Style aber so als Bericht ja vielleicht nich schlecht?
-Nachdem wir uns die Arbeit ja gemacht haben, könnte man das ja vielleicht schon machen?
--->
 While this yields interpretable results with regard to the question of "what matters to whom", it has the important downside that the number of clusters is a hyperparameter that has to be set prior to estimating the model.

### 2024-12-05 Manuscript files/Manuscript.qmd
updates

@@
 
-![Ext VarImps](figures/RF_VarImps_ext_v3.png){#fig-varimps-ext}
+![Ext VarImps](figures/RF_VarImps_ext_v4.png){#fig-varimps-ext}
 
@@
 
-```{r image-panel, echo=FALSE, fig.align='center'}
+```{r image-panel, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
 #| fig-cap: "Exemplary deicision trees for predicting IMCEs based on Covariates."

### 2024-12-05 1b_Analysis_cjbart.R

@@ -329,23 +329,28 @@ ggplot(plot_data, aes(x = AMCE,
                       color = Attribute)) +
   geom_vline(xintercept = 0) +
   # facet_col(.~Attribute) + 
-  geom_point() +
-  geom_errorbarh(aes(xmin = Lower, xmax = Upper), height = 0.2) +
+  geom_point(size = 2) +
+  geom_errorbarh(aes(xmin = Lower, xmax = Upper), 
+                 height = 0.5, 
+                 linewidth = 0.85) +
   labs(
     x = "AMCE Estimate",
     y = "",
-    title = "AMCE Estimates with 95% CIs") +
+    title = "") +
   theme_minimal() +
   guides(color = "none") +
   theme(
-    axis.text.y = element_text(size = 9),
-    axis.title.y = element_text(size = 12),
-    axis.title.x = element_text(size = 12),
-    plot.title = element_text(size = 14, face = "bold"),
+    axis.text.y = element_text(size = 14.5),
+    axis.text.x = element_text(size = 15),
+    # axis.title.y = element_text(size = 14),
+    axis.title.x = element_text(size = 15),
+    # plot.title = element_text(size = 14, face = "bold"),
     strip.placement = "outside",
     strip.background = element_rect(fill = "grey90", color = NA),
-    strip.text = element_text(face = "bold",
-                              size = rel(0.75), hjust = 0),
+    strip.text = element_text(face = "bold", 
+                              margin = margin(t = 1, b = 1),
+                              size = rel(1.2), 
+                              hjust = 0),
     panel.background = element_rect(fill = "white")) +
   ggforce::facet_col(facets = "Attribute", 
                      scales = "free_y", 
@@ -357,172 +362,6 @@ ggsave('Manuscript files/figures/AMCEs_as_cjbart.png', width = 12, height = 8)
 
 
 
-
-
-
-
-###' *Plot Distribution of IMCEs* 
-# plot(imces_ext) # plots IMCEs ordered by size (not what we want)
-# Extract data frames from the results
-imces_ext <- readRDS("1c_Model_Objects/2024-11-18_imces_ext.rds")
-attribute_levels <- imces_ext$att_levels # attribute levels
-imce_df <- imces_ext$imce # point estimates
-imce_lower_df <- imces_ext$imce_lower 
[…]

### 2024-12-09 00_Custom_Source/cjbart_custom.R
Updates to Manuscript
Additional Trees

Investigating of seed setting issue on win vs. unix systems

@@ -1,0 +1,793 @@
+# Convert character columns to factors with warning
+.char_to_fact <- function(data) {
+  
+  missing_factors <- sapply(data, is.character)
+  
+  if (sum(missing_factors) > 0) {
+    
+    missing_vars <- names(missing_factors)[missing_factors]
+    
+    data[,missing_vars] <- Map(as.factor, subset(data, select = missing_vars))
+    
+    # message("The following variables were converted to factors: ",
+    #         paste0(missing_vars, collapse = ", ")
+    # )
+    
+  }
+  
+  return(data)
+}
+
+# Suppress console output where verbose option not present
+.quiet <- function(x) {
+  
+  # Code from Hadley Wickham
+  # See: https://r.789695.n4.nabble.com/Suppressing-output-e-g-from-cat-td859876.html
+  
+  sink(tempfile())
+  on.exit(sink())
+  invisible(force(x))
+  
+}
+
+
+# Implementation of Rubin's combination rules
+.combine <- function(theta, var_theta) {
+  
+  m <- length(theta)
+  
+  Q_bar <- (1/m)*sum(theta)
+  U_bar <- (1/m)*sum(var_theta)
+  
+  demean <- (theta-Q_bar)^2
+  
+  B <- (1/(m-1)) * sum(demean)
+  
+  Q_bar_var <- U_bar + (1 + (1/m))*B
+  Q_bar_se <- sqrt(Q_bar_var)
+  
+  v_m <- (m-1)*(1+(U_bar/((1+m^-1)*B)))^2
+  
+  std_err = Q_bar_se
+  
+  return(std_err)
+  
+}
+
+
+
+
+
+#' Generate Conjoint Model Using BART
+#'
+#' @description A wrapper for the [BART::pbart()] function used for estimating heterogeneity in conjoint models
+#' @param data A data.frame, containing all attributes, controls, the outcome and id variables to analyze.
+#' @param Y Character string -- the outcome variable
+#' @param type Type of conjoint experiment -- either "choice" (for forced-choice outcomes) or "rating" (for interval ratings). If NULL (default), the function will attempt to automatically detect the outcome type.
+#' @param id Character string -- variable identifying individual respondents (optional)
+#' @param round Character string -- variable identifying rounds of the conjoint experiment
+#' @param use_round Boolean -- whether to include the round indicator column when training the BART model (default = \code{TRUE})
+#' @param cores Integer -- number of CPU cores used in model training
+#' @param ... Other arguments passed to [BART::mc.pbart()] if on a Unix-based system
[…]

### 2024-12-09 1a_Analysis_FactorHet.R

@@ -9,7 +9,7 @@ library(FactorHet)
 # setwd(dirname(rstudioapi::getSourceEditorContext()$path))
 
 ### Load Data 
-cj_tidy <- readRDS("Ukraine Conjoint Data/cj_tidy.rds")
+cj_tidy <- readRDS("0_Ukraine_Conjoint_Data/cj_tidy.rds")
 
 # Rename Attributes
 colnames(cj_tidy)[which(colnames(cj_tidy) %in% c(paste0("attr",1:9)))] <-
@@ -38,12 +38,14 @@ fit_FH_2 <- FactorHet_mbo(formula = y ~ Sold_killed_UKR + Sold_killed_RUS +
                                         group = ~ c_id, 
                                         task = ~ task,
                                         choice_order = ~ concept)
-saveRDS(fit_FH_2, "fit_FH_2F.rds")
-fit_FH_2 <- readRDS("fit_FH_2F.rds")
+saveRDS(fit_FH_2, "1c_Model_Objects/00_archive/fit_FH_2F.rds")
+fit_FH_2 <- readRDS("1c_Model_Objects/00_archive/fit_FH_2F.rds")
 AIC(fit_FH_2)
 BIC(fit_FH_2)
 
+# Plot Stuff 
 FactorHet::marginal_AME(fit_FH_2) # fast
+ggsave('Manuscript files/figures/2024-12-06_FactorHet_2C_AMCEs.png')
 FactorHet::posterior_by_moderators(fit_FH_2) # fast
 FactorHet::marginal_AMIE(fit_FH_2) # takes some time
 
@@ -60,8 +62,8 @@ fit_FH_3 <- FactorHet_mbo(formula = y ~ Sold_killed_UKR + Sold_killed_RUS +
                                         group = ~ c_id, 
                                         task = ~ task,
                                         choice_order = ~ concept)
-saveRDS(fit_FH_3, "fit_FH_3F.rds")
-fit_FH_3 <- readRDS("fit_FH_3F.rds")
+saveRDS(fit_FH_3, "1c_Model_Objects/00_archive/fit_FH_3F.rds")
+fit_FH_3 <- readRDS("1c_Model_Objects/00_archive/fit_FH_3F.rds")
 AIC(fit_FH_3)
 BIC(fit_FH_3)
 fit_FH_3$information_criterion$BIC
@@ -69,11 +71,9 @@ fit_FH_3$information_criterion$N
[…]

### 2024-12-09 1b_Analysis_cjbart.R

@@ -111,18 +111,38 @@ fit_cjbart_red <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_red.rds")
 
 
 ### Fit the extended model
-set.seed(123)
-fit_cjbart_ext = cjbart(data = cj_tidy[, vars_ext], 
+# set.seed(123)
+fit_cjbart_ext_s123 = cjbart(data = cj_tidy[, vars_ext], 
                         Y = "y",
                         # type = "choice", 
                         id = "c_id", 
                         round = "task", 
                         use_round = TRUE, 
-                        seed = 99,
+                        seed = 123,
                         cores = 4)
 
+
+
+# sNumber provides the seed, cNumber provides the cores used 
+# these 2 numbers determine the randomness in the BART tree building 
 # saveRDS(fit_cjbart_ext6_noround, "1c_Model_Objects/2024-11-18_fit_cjbart_ext6_noround.rds")
-fit_cjbart_ext <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
+# fit_cjbart_ext <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
+saveRDS(fit_cjbart_ext_s123, "1c_Model_Objects/2024-12-09_fit_cjbart_ext_s123_c4.rds")
+fit_cjbart_ext <- readRDS("1c_Model_Objects/2024-12-09_fit_cjbart_ext_s123_c4.rds")
+
+
+
+#' *Fit the model with the custom as-if-non-unix function*
+source('00_Custom_Source/cjbart_custom.R')
+set.seed(42)
+cfit_cjbart_es42_is123_v1 = cjbart_custom(data = cj_tidy[, vars_ext], 
+                             Y = "y",
+                             # type = "choice", 
+                             id = "c_id", 
+                             round = "task", 
+                             use_round = TRUE, 
+                             seed = 123,
+                             cores = 4)
 
 
 
@@ -621,7 +641,7 @@ rename_map <- c(
   "q10_2" = "Anti Weapon\ndeliveries 7",
   "q10_6" = "General Weapon\nfor defense 7",
   "q10_8" = "Weapons if\nciv. casualties  7",
-  "q10_10" = "Weapons if\n infra. destr. 7",
+  "q10_10" = "Weapons if infra. destr. 7",
   "Q11" = "Anti Nato 5",
[…]

### 2024-12-11 Manuscript files/Manuscript.qmd
Citations

@@
 floatsintext: yes
+bibliography: references.bib
 editor_options: 
@@
 Arguably the most commonly estimated causal quantity in conjoint analyses is the *average marginal component effect* (AMCE).
-The AMCE is the effect of a specific attribute level of interest compared to another level of the same attribute, holding equal the joint distribution of all other attributes and averaged over this joint distribution as well as the sampling distribution from the population CITE.
+The AMCE is the effect of a specific attribute level of interest compared to another level of the same attribute, holding equal the joint distribution of all other attributes and averaged over this joint distribution as well as the sampling distribution from the population [@robinson_how_2024].
 This quantity is estimable by regression models and provides us an effect of an attribute on the probability that a certain option (or profile) will be chosen.
@@
 To remedy the downsides of the "naive" subgroup approach outlined above, researchers developed more advanced methods based on machine learning.
-Most notable in this regard are (a) an approach based on *Bayesian additive regression trees* (in the following called *cjbart* CITE), (b) an approach based on a Bayesian mixture of regularized logistic regressions (*FactorHet* CITE), and (c) a testing approach based on conditional randomization tests (*CRT* CITE).
+Most notable in this regard are (a) an approach based on *Bayesian additive regression trees* [in the following called *cjbart*\; @robinson_how_2024], (b) an approach based on a Bayesian mixture of regularized logistic regressions [*FactorHet*\; @goplerud_estimating_2024], and (c) a testing approach based on conditional randomization tests [*CRT*\; @ham_using_2024].
 In this article, we focus on the explanation and demonstration of cjbart.
@@
 
-The premise of cjbart as introduced by CITE is that there are several *nested causal quantities* underlying the AMCE.
+The premise of cjbart as introduced by @robinson_how_2024 is that there are several *nested causal quantities* underlying the AMCE.
 Specifically, the AMCE can be decomposed into an individual-level (i.e., participant-level), round-level, and observation-level marginal component effect (IMCE, RMCE, and OMCE, respectively).
@@
 Lastly, the OMCE is estimated by additionally conditioning on a specific profile-level (i.e., if $J = 2$, by conditioning on one of the two profiles).
-As CITE note, the OMCE does not contain too much substantial information.
+As @robinson_how_2024 note, the OMCE does not contain too much substantial information.
 It is, however, of statistical importance: assuming the OMCE is an independent random draw from an individual-level distribution, we can aggregate the OMCEs to estimate the IMCEs.
@@
 IMCEs can be considered the most important quantity for our purpose of investigating effect heterogeneity because it allows us to analyze how attribute importances differ depending on participant covariates.
-CITE propose a three-step estimation procedure.
+@robinson_how_2024 propose a three-step estimation procedure.
 
@@
 Specifically, some function is estimated that relates the attribute levels of the *L* attributes that were shown to subject *i* in the $k^{th}$ round in profile *j* and the covariate vector $X_i$ to the observed binary outcome $Y_{ijk}$ (which is equal to 1 if the profile was chosen and equal to 0 if it was not chosen).
-CITE detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functional relationship could be used as well.
+@robinson_how_2024 detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functional relationship could be used as well.
 <!-- habe hier noch ein bisschen was dazu geschrieben  -->
@@
 More specifically, we want to assess whether the effects of certain attribute levels on choice behavior are different across individuals.
-CITE provide two methods that yield information about which covariates are associated with heterogeneity in effects of attribute levels.
+@robinson_how_2024 suggest two methods that yield information about which covariates are associated with heterogeneity in effects of attribute levels.
 Both methods are tree-based which is especially suitable to investigate heterogeneity because trees partition a data set into increasingly homogeneous groups.
@@
 Each tree only considers a random subset of predictor variables (in our case: subject-level covariates) and is trained on a bootstrap sample.
-Thus, CITE suggest a complementary analysis with single decision trees which are grown for a specific attribute level.
+Thus, @robinson_how_2024 suggest a complementary analysis with single decision trees which are grown for a specific attribute level.
 In this analysis, a decision tree predicts IMCEs for this specific attribute level, again using subject-level covariates as predictors.
@@
 Importantly, to keep decision trees interpretable (i.e., to not let them grow too deep), they have to be pruned by setting a complexity parameter controlling the depth.
-CITE suggest to set this parameter such that the tree only continues to split the data if the increase in explained variance of the IMCE (i.e., $R^2$) is at least 0.02 to 0.04.
+@robinson_how_2024 suggest to set this parameter such that the tree only continues to split the data if the increase in explained variance of the IMCE (i.e., $R^2$) is at least 0.02 to 0.04.
 The predictions in the terminal nodes of the tree correspond to conditional AMCEs, which would normally be assessed by estimating AMCEs in subgroups.
@@
 In the following, we showcase the application of cjbart to data provided by Prof. Dr. Paul Thurner and Fabian Haggerty from the Geschwister-Scholl-Institute of Political Science, LMU Munich.
-The data were first described in CITE.
-In their work, CITE aimed at investigating which attributes citizens from five different NATO-member countries (United States [US], United Kingdom [UK], Germany, Italy, and France) deem important when deciding whether Ukraine should be supported economically and militarily against the Russian aggression.
-For this, CITE conducted a conjoint experiment where $N = 10,011$ participants from the five countries chose one of two possible profiles. 
+The data were first described in @rudolph_citizens_2024.
+In their work, @rudolph_citizens_2024 aimed at investigating which attributes citizens from five different NATO-member countries (United States [US], United Kingdom [UK], Germany, Italy, and France) deem important when deciding whether Ukraine should be supported economically and militarily against the Russian aggression.
+For this, @rudolph_citizens_2024 conducted a conjoint experiment where $N = 10,011$ participants from the five countries chose one of two possible profiles. 
 In these profiles, nine different attributes with varying attribute levels were manipulated randomly to indicate the consequences that a support of Ukraine would entail if the profile was chosen.
@@
 
-To investigate which attributes and attribute levels matter when people decide whether Ukraine should be supported in their defense endeavors, CITE estimated AMCEs as well as marginal means for subgroup analyses.
+To investigate which attributes and attribute levels matter when people decide whether Ukraine should be supported in their defense endeavors, @rudolph_citizens_2024 estimated AMCEs as well as marginal means for subgroup analyses.
 The results of their analyses will be outlined below, where we compare them to the results of our analyses using cjbart.
@@
 
-Thus, the goal of this project is to complement the existing results reported by CITE with an exploratory analysis.
+Thus, the goal of this project is to complement the existing results reported by @rudolph_citizens_2024 with an exploratory analysis.
 Using cjbart, we are able to scrutinize the data for heterogeneity of attribute effects.
@@
 Data of the above conjoint experiment was modeled by the previously described cjbart approach.
-For this, we used the R package *cjbart* described in CITE.
-We fit a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different statements regarding political statements (e.g., EXAMPLE).
+For this, we used the R package *cjbart* described in @robinson_how_2024.
+We fit a BART model containing the profile attributes and various subject-level covariates: age, country, gender, and political orientation, and subjects' agreement on different political questions and statements (e.g., "The political agenda should focus on the war against Ukraine.").
 A list of all covariates, including their type, can be found in @tbl-covariates.
@@
 
-To better understand the associations of different subject-level covariates and individual effects of specific attributes (i.e., IMCEs), we used the two tree-based approaches proposed by CITE. 
+To better understand the associations of different subject-level covariates and individual effects of specific attributes (i.e., IMCEs), we used the two tree-based approaches proposed by @robinson_how_2024.
 For this, a random forest model was first fit, predicting the IMCEs using the respective individuals' subject-level covariates. 
 We then used decision trees to more thoroughly investigate the relationships of specific IMCEs and covariates for which the previous step suggested relevant contribution to the prediction. 
-As already proposed in CITE, we found complexity parameter values (cp) between 0.02 and 0.04 to yield useful results. 
+As already proposed in @robinson_how_2024, we found complexity parameter values (cp) between 0.02 and 0.04 to yield useful results. 
 Usage of larger cp values resulted in overly simplified trees often consisting of only a single root node. 
 Smaller cp values, on the other hand, often resulted in overly deep trees with little differentiation across many terminal nodes, making the interpretation of substantive differences too difficult. 
-In the next section, we present the results of these analyses, followed by a discussion and comparison to the results reported by CITE.
+In the next section, we present the results of these analyses, followed by a discussion and comparison to the results reported by @rudolph_citizens_2024.
 
@@
 
-These AMCEs are supplemented with the AMCEs reported in the original preprint by CITE, presented in @fig-amces-preprint.
+These AMCEs are supplemented with the AMCEs reported in the original article by @rudolph_citizens_2024, presented in @fig-amces-preprint.
 
@@
 For example, increasing the risk of a nuclear strike from the reference level 'Not present (0%)' to 'Moderate (10%)' decreased the average probability of a participant choosing the latter profile by about 8.5 percentage points.
-The AMCE point estimates were in line with the AMCEs reported in CITE, which is why we refrain from an in-depth discussion here and refer the interested reader to CITE.
+The AMCE point estimates were in line with the AMCEs reported in @rudolph_citizens_2024, which is why we refrain from an in-depth discussion here and refer the interested reader to their article.
 
@@
 Interestingly, out of the investigated IMCE decision trees this was the only case for which we observed splits resulting in nodes with different signs meaning that the probability of profile selection decreased in one child node and increased in the other.
-<!-- @Philipp: hast du hier gut ne Quelle, mit der wir einfach sagen können dass die Bäume basierend auf Impurity splitten und das eben nicht signifikanz bedeutet -->
-These results have, however, to be interpreted with caution as the split cannot be interpreted as a sign of statistically significant differences between the terminal nodes. 
+These results have, however, to be interpreted with caution as the split cannot be interpreted as a sign of statistically significant differences between the terminal nodes [e.g., @zeileis_model-based_2008].
 Moreover, for this result, though having different signs, the differences in probability are still small (less than 2 percentage points) and close to zero. 
@@
 
-However, as already outlined by many authors (CITE), thes above AMCEs cannot be used to reason about absolute profile selection probabilities but instead are relative in nature. 
+However, as already outlined by some authors [@goplerud_estimating_2024; @robinson_how_2024], the above AMCEs cannot be used to reason about absolute profile selection probabilities but instead are relative in nature.
 Accordingly a given AMCE has always to be interpreted as change in profile selection probability *relative to a given reference level* of the same attribute. 
@@
 Second, and closely related, while the decision trees offer an easy interpretation of subgroup differences, they do not provide information on whether these differences are statistically significant.
-This is because decision trees as implemented by CITE and also in our article base their split decision on a maximal reduction of *impurity*.
+This is because decision trees as implemented by @robinson_how_2024 and also in our article base their split decision on a maximal reduction of *impurity*.
 That is, the goal of decision trees is to partition the data so that observations in the resulting nodes are as homogeneous as possible (in the sense of reduced variance in nodes).
@@
 For example, for the result of changed signs in IMCEs reported above, it is a theoretical and content related question whether the difference of around 2 percentage points is relevant.
-A possible extension would be to use a different decision tree algorithm, for example conditional inference trees CITE.
+A possible extension would be to use a different decision tree algorithm, for example conditional inference trees [e.g., @hothorn_ctree_2015]
 These types of trees base their split decisions on non-parametric hypotheses tests.
@@
 Third, more simulated and empirical research on cjbart is needed to properly assess the stability of its solutions.
-Internally, the *cjbart()* function as implemented by CITE calls the *mc-pbart()* function from the *BART* package CITE.
+Internally, the *cjbart()* function as implemented by @robinson_how_2024 calls the *mc-pbart()* function from the *BART* package [@sparapani_nonparametric_2021].
 This function estimates complex relations using the BART model described above and uses a seed[^seed] (which defaults to 99).
@@
 Forth and last, cjbart is not the only method to take potential heterogeneity in attribute level effects into account.
-As mentioned in the introduction, two other methods are FactorHet by CITE and the CRT approach by CITE.
+As mentioned in the introduction, two other methods are FactorHet by @goplerud_estimating_2024 and the CRT approach by @ham_using_2024.
 FactorHet works based on a Bayesian mixture of regularized logistic regression analyses.
@@
 Future research concerning FactorHet could develop model selection strategies, like information criteria, that are comparable across solutions with differing numbers of clusters and allow for a statistical decision.
-The other method, CRT by CITE, is a statistical hypothesis testing approach based on conditional randomization tests.
+The other method, CRT by @ham_using_2024, is a statistical hypothesis testing approach based on conditional randomization tests.
 The goal of this approach is to assess whether a specific attribute of interest influences participants' choice behavior in any way, given all the other attributes.
@@
 As in every statistical analysis, the choice of methods and models crucially depends on the research question and desired inferences one wants to make.
-Because our goal was to complement the existing analyses reported by CITE with a maximally exploratory approach, potentially informing future more confirmatory research, we found that cjbart best fits this purpose.
+Because our goal was to complement the existing analyses reported by @rudolph_citizens_2024 with a maximally exploratory approach, potentially informing future more confirmatory research, we found that cjbart best fits this purpose.
 
 # Conclusion
+
+\newpage
+
+# References
+
+<!-- References will auto-populate in the refs div below -->
+
+::: {#refs}
+:::

### 2024-12-11 Manuscript files/Manuscript.qmd
Conclusion

@@
 
+Complementing the analyses reported in @rudolph_citizens_2024, we used the novel cjbart approach by @robinson_how_2024 to scrutinize the present conjoint data for effect heterogeneity.
+Specifically, we found that the importance of certain attributes (levels) differed with regard to country, where differences were most pronounced for the distinction UK vs. the other four countries.
+For example, for all five countries selection probabilities decreased with increasing civilian casualties but the effect was stronger for non-UK participants.
+Similarly, the opinion that Ukraine should not make any concessions to Russia to end the aggression predicted some heterogeneity.
+People who oppose concessions favored profiles that were associated with higher numbers of killed Russian soldiers, while for concession proponents the selection probability decreased.
+
+With AMCE estimates similar to the primary analysis reported by @rudolph_citizens_2024, we believe that the newly developed cjbart-method provides a powerful tool to investigate effect heterogeneity in high-dimensional conjoint data.
+As with any new method, further methodological research is needed to assess to capabilities of the method under different conditions.
+Most importantly, the results of cjbart should always be interpreted as what they are: an exploratory peek into underlying causal relations between covariates and individual preferences for certain attributes (i.e., IMCEs).
+Our recommendation is to use these exploratory insights to generate hypotheses that can subsequently be tested to inform political theory.
+
 \newpage

### 2024-12-13 1b2_Loop_Analysis_cjbart.R
updates and new plots

@@ -1,0 +1,606 @@
+################################################################################
+####### CJBART 
+################################################################################
+
+### Load Packages
+library(cjbart)
+library(haven)
+library(tidytext)
+library(dplyr)
+library(ggplot2)
+library(rpart)
+library(rpart.plot) # standard built-in plot function used in the paper
+library(dplyr)
+library(tidyr)
+library(ggtext)
+library(parallel)
+
+
+### Set WD
+# setwd(dirname(rstudioapi::getSourceEditorContext()$path))
+
+### Load Data 
+cj_tidy <- readRDS("0_Ukraine_Conjoint_Data/cj_tidy.rds")
+
+# get additional covariate data 
+add_covars <- 
+  readRDS("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.Rds")
+# get additional covariate data --> same data different files types?
+add_covars2 <- 
+  haven::read_dta("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.dta")
+rm(add_covars2)
+
+
+### Join the add_covars with the cj_tidy data 
+# for this, create c_id (country_id) variable in add_covars
+add_covars$country_id <- paste0(add_covars$Country, 
+                                "_",
+                                add_covars$ID)
+# Remove the covars in add_covars that are already present in cj_tidy
+which(!colnames(add_covars) %in% colnames(cj_tidy))
+add_covars_new <- add_covars[,which(!colnames(add_covars) %in% 
+                                      colnames(cj_tidy))]
+
+# join the new covariate data
+cj_tidy <- merge(cj_tidy,
+                 add_covars_new,
+                 by.x = "c_id",
+                 by.y = "country_id", 
+                 all.x = T) # left join
+
+
+
+# Rename Attributes
+colnames(cj_tidy)[which(colnames(cj_tidy) %in% c(paste0("attr",1:9)))] <-
+  c("Sold_killed_UKR",
+    "Sold_killed_RUS",
+    "Civ_killed_UKR",
+    "Infra_Destr_UKR",
+    "Perc_GDP_milit",
+    "Perc_GDP_econ",
+    "Risk_Nuke",
+    "Territ_Cession",
+    "Polit_Self_Det_UKR")
+
+
+
+#####' *Select variables of interest for the 2 different models*
+vars_ext = c(
+  # General variables
+  'y', 'c_id', 
+  'task',
+  # Attributes
[…]

### 2024-12-16 1b_Analysis_cjbart.R
updates: include cregg code for MMs, additional DT Plots

@@ -13,6 +13,7 @@ library(rpart.plot) # standard built-in plot function used in the paper
 library(dplyr)
 library(tidyr)
 library(ggtext)
+library(forcats)
 
 
 ### Set WD
@@ -716,9 +717,28 @@ dev.off()
 
 
 ####' *Additional Trees for exploration*
-
 # Sanity Check Infstructure Destroyed 100B
-fit <- rpart::rpart(formula = `100B` ~ Country + Age + Gender + `Left-Right-3` + `for Peace 01: No Concessions` + `Weapons if infra. destr. 7`,
+fit <- rpart::rpart(formula = `100B` ~ Country + Age + Gender + `Left-Right-3` + 
+                      `for Peace 01: No Concessions` + 
+                      `Weapons if infra. destr. 7`,
+                    imces_ext$imce
+                    , control = rpart.control(cp = 0.04)  # complexity param, default = 0.01, larger --> less complex 
+) 
+rpart.plot(fit, node.fun = node_fun, cex = 1.1, tweak = 2.8, 
+           # , main = paste('Target: IMCEs of', find_attr(fit$terms[[2]]), '=',  fit$terms[[2]])
+)
+
+# Ukrainian Soldiers killed (50k)
+fit <- rpart::rpart(formula = `50,000` ~ Country + Age + Gender + `Left-Right-3` + `for Peace 01: No Concessions` + `Weapons if infra. destr. 7`,
+                    imces_ext$imce
+                    , control = rpart.control(cp = 0.04)  # complexity param, default = 0.01, larger --> less complex 
+) 
+rpart.plot(fit, node.fun = node_fun, cex = 0.8, tweak = 2.8, 
+           # , main = paste('Target: IMCEs of', find_attr(fit$terms[[2]]), '=',  fit$terms[[2]])
+)
+
+# Ukrainian Soldiers killed (25k)
+fit <- rpart::rpart(formula = `25,000` ~ Country + Age + Gender + `Left-Right-3` + `for Peace 01: No Concessions` + `Weapons if infra. destr. 7`,
                     imces_ext$imce
                     , control = rpart.control(cp = 0.04)  # complexity param, default = 0.01, larger --> less complex 
 ) 
@@ -727,12 +747,13 @@ rpart.plot(fit, node.fun = node_fun, cex = 1.1, tweak = 2.8,
 )
 
 
+
 # Infrastructure destroyed 200B
[…]

### 2024-12-17 00_Custom_Source/cjbart_custom.R
custom IMCE function

@@ -238,6 +238,7 @@ cjbart_custom <- function(data, Y, type = NULL, id = NULL, round = NULL, use_rou
 #' @importFrom stats predict
 #' @example inst/examples/basic_workflow.R
 #' @export
+
 IMCE <- function(data,
                  model,
                  attribs,

### 2024-12-17 00_Custom_Source/cjbart_imce_custom.R

@@ -1,0 +1,482 @@
+#' *TR: Create Functions needed later on*
+
+# Convert character columns to factors with warning
+.char_to_fact <- function(data) {
+  
+  missing_factors <- sapply(data, is.character)
+  
+  if (sum(missing_factors) > 0) {
+    
+    missing_vars <- names(missing_factors)[missing_factors]
+    
+    data[,missing_vars] <- Map(as.factor, subset(data, select = missing_vars))
+    
+    # message("The following variables were converted to factors: ",
+    #         paste0(missing_vars, collapse = ", ")
+    # )
+    
+  }
+  
+  return(data)
+}
+
+# Suppress console output where verbose option not present
+.quiet <- function(x) {
+  
+  # Code from Hadley Wickham
+  # See: https://r.789695.n4.nabble.com/Suppressing-output-e-g-from-cat-td859876.html
+  
+  sink(tempfile())
+  on.exit(sink())
+  invisible(force(x))
+  
+}
+
+
+# Implementation of Rubin's combination rules
+.combine <- function(theta, var_theta) {
+  
+  m <- length(theta)
+  
+  Q_bar <- (1/m)*sum(theta)
+  U_bar <- (1/m)*sum(var_theta)
+  
+  demean <- (theta-Q_bar)^2
+  
+  B <- (1/(m-1)) * sum(demean)
+  
+  Q_bar_var <- U_bar + (1 + (1/m))*B
+  Q_bar_se <- sqrt(Q_bar_var)
+  
+  v_m <- (m-1)*(1+(U_bar/((1+m^-1)*B)))^2
+  
+  std_err = Q_bar_se
+  
+  return(std_err)
+  
+}
+
+
+
+#' *TR: IMCE function as used later in the package*
+#' Heterogeneous Effects Analysis of Conjoint Results
+#'
+#' @description \code{IMCE} calculates the individual-level marginal component effects from a BART-estimated conjoint model.
+#' @param data A data.frame, containing all attributes, covariates, the outcome and id variables to analyze.
+#' @param model A model object, the result of running \code{cjbart()}
+#' @param attribs Vector of attribute names for which IMCEs will be predicted
+#' @param ref_levels Vector of reference levels, used to calculate marginal effects
[…]

### 2024-12-17 1b_Analysis_cjbart.R

@@ -127,13 +127,28 @@ fit_cjbart_ext_s123 = cjbart(data = cj_tidy[, vars_ext],
 # sNumber provides the seed, cNumber provides the cores used 
 # these 2 numbers determine the randomness in the BART tree building 
 # saveRDS(fit_cjbart_ext6_noround, "1c_Model_Objects/2024-11-18_fit_cjbart_ext6_noround.rds")
-# fit_cjbart_ext <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
-saveRDS(fit_cjbart_ext_s123, "1c_Model_Objects/2024-12-09_fit_cjbart_ext_s123_c4.rds")
-fit_cjbart_ext <- readRDS("1c_Model_Objects/2024-12-09_fit_cjbart_ext_s123_c4.rds")
+fit_cjbart_ext <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
 
 
 
-#' *Fit the model with the custom as-if-non-unix function*
+#' *Fit extended model with larger (non-default) Burn-In/Draws for*
+#' *extended converegence assessment*
+fit_cjbart_ext_large = cjbart(data = cj_tidy[, vars_ext], 
+                             Y = "y",
+                             # type = "choice", 
+                             id = "c_id", 
+                             round = "task", 
+                             use_round = TRUE, 
+                             seed = 99,
+                             nskip = 1000, # Burn-In instead of 100 (default)
+                             ndpost = 5000, # Posterior Draws instead of 1000
+                             cores = 4)
+saveRDS(fit_cjbart_ext_large, "1c_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
+fit_cjbart_ext_large <- readRDS("1c_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
+
+
+
+#' *Fit the model with the custom as-if-non-unix cjbart function*
 source('00_Custom_Source/cjbart_custom.R')
 set.seed(42)
 cfit_cjbart_es42_is123_v1 = cjbart_custom(data = cj_tidy[, vars_ext], 
@@ -142,10 +157,13 @@ cfit_cjbart_es42_is123_v1 = cjbart_custom(data = cj_tidy[, vars_ext],
                              id = "c_id", 
                              round = "task", 
                              use_round = TRUE, 
-                             seed = 123,
[…]

### 2024-12-18 00_Custom_Source/cjbart_imce_custom.R
updates convergence diagnostics using traceplots

@@ -1,4 +1,4 @@
-#' *TR: Create Functions needed later on*
+#' *Comment TR: Create Functions needed later on*
 
 # Convert character columns to factors with warning
 .char_to_fact <- function(data) {
@@ -58,7 +58,7 @@
 
 
 
-#' *TR: IMCE function as used later in the package*
+#' *Comment TR: IMCE function as used later in the package*
 #' Heterogeneous Effects Analysis of Conjoint Results
 #'
 #' @description \code{IMCE} calculates the individual-level marginal component effects from a BART-estimated conjoint model.
@@ -85,11 +85,12 @@
 #' @example inst/examples/basic_workflow.R
 #' @export
 
-#' *TR: Set Arguments for IMCE dry-run to extract trace plots*
+#' *Insert TR: Set Arguments for IMCE dry-run to extract trace plots*
 data = cj_tidy[, vars_ext]
 keep_omce = TRUE
-model = fit_cjbart_ext # standard model  
-model_large = fit_cjbart_ext_large 
+# model = fit_cjbart_ext # standard model  
+model = fit_cjbart_ext_large 
+large = T
       # 'larger' model for longer Burn-In and More Draws
       # nskip = 2000 (vs. 250), ndraws = 5000 (vs. 1000)
 attribs = c("Sold_killed_UKR"
@@ -116,8 +117,10 @@ method = 'rubin'
 cores = 4
 skip_checks = T
 
-# IMCE Dry Run 
-# with the IMCE function structure being opened 
+#' *Comment TR: Dry Run of IMCE function*
+#' *Comment TR: after drilling on the IMCE function*
+
+# IMCE = function(args){
 
 data <- as.data.frame(data)
 
@@ -220,8 +223,8 @@ out_levels <- c()
 
 for (i in 1:length(attribs)) {
   
-  # i=1 --> Ukr. Soldiers Killed 
-  # i=9 --> Sovereignity/Polit. Self. Determination
+  # i=1 # --> Ukr. Soldiers Killed 
+  i=9 # --> Sovereignity/Polit. Self. Determination
   
   message("Calculating OMCEs for attribute: ", attribs[i], " [",i,"/",length(attribs),"]")
   
@@ -298,21 +301,31 @@ for (i in 1:length(attribs)) {
     # stats::pnorm(colMeans(pred_0$yhat.test))
     
     # Plot and Save Traceplots of the Draws
+    # dynamically generate plot names
+    if (large == T){
+      suffix = '_large'
+    } else {
[…]

### 2024-12-18 1b_Analysis_cjbart.R

@@ -140,10 +140,10 @@ fit_cjbart_ext_large = cjbart(data = cj_tidy[, vars_ext],
                              round = "task", 
                              use_round = TRUE, 
                              seed = 99,
-                             nskip = 1000, # Burn-In instead of 100 (default)
+                             nskip = 2000, # Burn-In instead of 100 (default)
                              ndpost = 5000, # Posterior Draws instead of 1000
                              cores = 4)
-saveRDS(fit_cjbart_ext_large, "1c_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
+# saveRDS(fit_cjbart_ext_large, "1c_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
 fit_cjbart_ext_large <- readRDS("1c_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
 
 

### 2024-12-18 00_Custom_Source/cjbart_imce_custom.R
updates Use Geweke's Approach for Convergence Diagnostik Plot sample p-vals for Geweke Tests

@@ -1,498 +1,0 @@
-#' *Comment TR: Create Functions needed later on*
-
-# Convert character columns to factors with warning
-.char_to_fact <- function(data) {
-  
-  missing_factors <- sapply(data, is.character)
-  
-  if (sum(missing_factors) > 0) {
-    
-    missing_vars <- names(missing_factors)[missing_factors]
-    
-    data[,missing_vars] <- Map(as.factor, subset(data, select = missing_vars))
-    
-    # message("The following variables were converted to factors: ",
-    #         paste0(missing_vars, collapse = ", ")
-    # )
-    
-  }
-  
-  return(data)
-}
-
-# Suppress console output where verbose option not present
-.quiet <- function(x) {
-  
-  # Code from Hadley Wickham
-  # See: https://r.789695.n4.nabble.com/Suppressing-output-e-g-from-cat-td859876.html
-  
-  sink(tempfile())
-  on.exit(sink())
-  invisible(force(x))
-  
-}
-
-
-# Implementation of Rubin's combination rules
-.combine <- function(theta, var_theta) {
-  
-  m <- length(theta)
-  
-  Q_bar <- (1/m)*sum(theta)
-  U_bar <- (1/m)*sum(var_theta)
-  
-  demean <- (theta-Q_bar)^2
-  
-  B <- (1/(m-1)) * sum(demean)
-  
-  Q_bar_var <- U_bar + (1 + (1/m))*B
-  Q_bar_se <- sqrt(Q_bar_var)
-  
-  v_m <- (m-1)*(1+(U_bar/((1+m^-1)*B)))^2
-  
-  std_err = Q_bar_se
-  
-  return(std_err)
-  
-}
-
-
-
-#' *Comment TR: IMCE function as used later in the package*
-#' Heterogeneous Effects Analysis of Conjoint Results
-#'
-#' @description \code{IMCE} calculates the individual-level marginal component effects from a BART-estimated conjoint model.
-#' @param data A data.frame, containing all attributes, covariates, the outcome and id variables to analyze.
-#' @param model A model object, the result of running \code{cjbart()}
-#' @param attribs Vector of attribute names for which IMCEs will be predicted
-#' @param ref_levels Vector of reference levels, used to calculate marginal effects
[…]

### 2024-12-18 00_Custom_Source/custom_cjbart_imce_convdiag.R

@@ -1,0 +1,675 @@
+#' *Comment TR: Create Functions needed later on*
+
+# Convert character columns to factors with warning
+.char_to_fact <- function(data) {
+  
+  missing_factors <- sapply(data, is.character)
+  
+  if (sum(missing_factors) > 0) {
+    
+    missing_vars <- names(missing_factors)[missing_factors]
+    
+    data[,missing_vars] <- Map(as.factor, subset(data, select = missing_vars))
+    
+    # message("The following variables were converted to factors: ",
+    #         paste0(missing_vars, collapse = ", ")
+    # )
+    
+  }
+  
+  return(data)
+}
+
+# Suppress console output where verbose option not present
+.quiet <- function(x) {
+  
+  # Code from Hadley Wickham
+  # See: https://r.789695.n4.nabble.com/Suppressing-output-e-g-from-cat-td859876.html
+  
+  sink(tempfile())
+  on.exit(sink())
+  invisible(force(x))
+  
+}
+
+
+# Implementation of Rubin's combination rules
+.combine <- function(theta, var_theta) {
+  
+  m <- length(theta)
+  
+  Q_bar <- (1/m)*sum(theta)
+  U_bar <- (1/m)*sum(var_theta)
+  
+  demean <- (theta-Q_bar)^2
+  
+  B <- (1/(m-1)) * sum(demean)
+  
+  Q_bar_var <- U_bar + (1 + (1/m))*B
+  Q_bar_se <- sqrt(Q_bar_var)
+  
+  v_m <- (m-1)*(1+(U_bar/((1+m^-1)*B)))^2
+  
+  std_err = Q_bar_se
+  
+  return(std_err)
+  
+}
+
+
+
+#' *Comment TR: IMCE function as used later in the package*
+#' Heterogeneous Effects Analysis of Conjoint Results
+#'
+#' @description \code{IMCE} calculates the individual-level marginal component effects from a BART-estimated conjoint model.
+#' @param data A data.frame, containing all attributes, covariates, the outcome and id variables to analyze.
+#' @param model A model object, the result of running \code{cjbart()}
+#' @param attribs Vector of attribute names for which IMCEs will be predicted
+#' @param ref_levels Vector of reference levels, used to calculate marginal effects
[…]

### 2024-12-18 Manuscript files/Manuscript.qmd
updates to manuscript

@@
 
+# Appendix
+## A1 Convergence Diagnostics - Attribute: Ukrainian Soldiers Killed
+
+```{r convergence-diagnostics-usk, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
+#| fig-subcap: "Exemplary Posterior Draw Traceplots for Convergence Assessment - Attribute 1"
+#| fig-cap: "Note.
+Rows 1 and 2 display Traceplots of Draws from the BART Posterior Distribution for the selection probabilities (p_hat_0 and p_hat_1) if Attribute 1 (Ukrainian Military Casualties) was set to the reference level (i.e., 12,500) or first level of interest (i.e., 25,000).
+Row 3 represents the associated OMCE 'draws' calculcate by taking the different of p_hat_1 and p_hat_0.
+Columns 1 and 2 contain draws from the default sized BART model (Burn-In: 100, Posterior Draws: 1000) and larger BART Models (Burn-In: 1000, Posterior Draws: 5000)\\linebreak Models were fit using parallel computation on 4 cores."
+#| label: convergence-diagnostics-usk
+# if needed add linebreaks in fig-cap via \\linebreak
+
+library(gridExtra)
+library(grid)
+library(png)
+
+# Load the images
+usk_p0_small <- rasterGrob(
+  png::readPNG("figures/Traceplots/Ukr_Sold_killed_phat0_12k_1.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+usk_p0_large <- rasterGrob(
+  png::readPNG("figures/Traceplots/Ukr_Sold_killed_phat0_12k_1_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+usk_p1_small <- rasterGrob(
+  png::readPNG("figures/Traceplots/Ukr_Sold_killed_phat1_25k_1.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+usk_p1_large <- rasterGrob(
+  png::readPNG("figures/Traceplots/Ukr_Sold_killed_phat1_25k_1_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+usk_omce_small <- rasterGrob(
+  png::readPNG("figures/Traceplots/Ukr_Sold_killed_omce_25k_1.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+usk_omce_large <- rasterGrob(
+  png::readPNG("figures/Traceplots/Ukr_Sold_killed_omce_25k_1_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+
+# Define column headers (centered)
+col_header1 <- textGrob("Default Sized Model", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
+col_subheader1 <- textGrob("Burn-In: 100 \nPosterior Draws: 1000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+
+col_header2 <- textGrob("Large Model", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
+col_subheader2 <- textGrob("Burn-In: 1000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+
+col_header1_combined <- arrangeGrob(col_header1, col_subheader1, ncol=1,
+                                    heights=c(unit(0.5,"lines"), unit(0.5,"lines")))
+col_header2_combined <- arrangeGrob(col_header2, col_subheader2, ncol=1,
+                                    heights=c(unit(0.5,"lines"), unit(0.5,"lines")))
+
+# Single grobs for rows with newline and adjusted lineheight
+row_header_combined_1 <- textGrob(paste0("p_hat_0\n",
+                                         "phat_0[,1]"), x=0, hjust=0, 
+                                  gp=gpar(fontsize=10, lineheight=1))
+row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
+                                         "phat_0[,1]"), x=0, hjust=0,
+                                  gp=gpar(fontsize=10, lineheight=1))
+row_header_combined_3 <- textGrob(paste0("omce_1\n",
+                                         "omces[,1]"), x=0, hjust=0,
+                                  gp=gpar(fontsize=10, lineheight=1))
+
+grid.arrange(
+  textGrob(""), col_header1_combined, col_header2_combined,
+  row_header_combined_1, usk_p0_small, usk_p0_large,
+  row_header_combined_2, usk_p1_small, usk_p1_large,
+  row_header_combined_3, usk_omce_small, usk_omce_large,
+  ncol=3,
+  widths=c(1,4,4),
+  heights=c(1.5,3,3,3)
+)
+```
+
+## A2 Convergence Diagnostics - Attribute: Sovereignity
+
+```{r convergence-diagnostics-sov, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
+#| fig-subcap: "Exemplary Posterior Draw Traceplots for Convergence Assessment - Attribute 9"
+#| fig-cap: "Note.
+Rows 1 and 2 display Traceplots of Draws from the BART Posterior Distribution for the selection probabilities (p_hat_0 and p_hat_1) if Attribute 9 (Sovereignity) was set to the reference level (i.e., 'Full') or first level of interest (i.e., 'EU/NATO').
+Row 3 represents the associated OMCE 'draws' calculcate by taking the different of p_hat_1 and p_hat_0.
+Columns 1 and 2 contain draws from the default sized BART model (Burn-In: 100, Posterior Draws: 1000) and larger BART Models (Burn-In: 1000, Posterior Draws: 5000).\\linebreak Models were fit using parallel computation on 4 cores."
+#| label: convergence-diagnostics-sov
+# if needed add linebreaks in fig-cap via \\linebreak
+
+library(gridExtra)
+library(grid)
+library(png)
+
+# Load the images
+sov_p0_small <- rasterGrob(
+  png::readPNG("figures/Traceplots/Sovereignity_phat0_Full_80088.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+sov_p0_large <- rasterGrob(
+  png::readPNG("figures/Traceplots/Sovereignity_phat0_Full_80088_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+sov_p1_small <- rasterGrob(
+  png::readPNG("figures/Traceplots/Sovereignity_phat1_EU_NATO_80088.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+sov_p1_large <- rasterGrob(
+  png::readPNG("figures/Traceplots/Sovereignity_phat1_EU_NATO_80088_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+sov_omce_small <- rasterGrob(
+  png::readPNG("figures/Traceplots/Sovereignity_omce_EU_NATO_80088.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+sov_omce_large <- rasterGrob(
+  png::readPNG("figures/Traceplots/Sovereignity_omce_EU_NATO_80088_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+
+# Define column headers (centered)
+col_header1 <- textGrob("Default Sized Model", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
+col_subheader1 <- textGrob("Burn-In: 100 \nPosterior Draws: 1000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+
+col_header2 <- textGrob("Large Model", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
+col_subheader2 <- textGrob("Burn-In: 1000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+
+col_header1_combined <- arrangeGrob(col_header1, col_subheader1, ncol=1,
+                                    heights=c(unit(0.5,"lines"), unit(0.5,"lines")))
+col_header2_combined <- arrangeGrob(col_header2, col_subheader2, ncol=1,
+                                    heights=c(unit(0.5,"lines"), unit(0.5,"lines")))
+
+# Single grobs for rows with newline and adjusted lineheight
+row_header_combined_1 <- textGrob(paste0("p_hat_0\n",
+                                         "phat_0[,1]"), x=0, hjust=0, 
+                                  gp=gpar(fontsize=10, lineheight=1))
+row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
+                                         "phat_0[,1]"), x=0, hjust=0,
+                                  gp=gpar(fontsize=10, lineheight=1))
+row_header_combined_3 <- textGrob(paste0("omce_1\n",
+                                         "omces[,1]"), x=0, hjust=0,
+                                  gp=gpar(fontsize=10, lineheight=1))
+
+grid.arrange(
+  textGrob(""), col_header1_combined, col_header2_combined,
+  row_header_combined_1, sov_p0_small, sov_p0_large,
+  row_header_combined_2, sov_p1_small, sov_p1_large,
+  row_header_combined_3, sov_omce_small, sov_omce_large,
+  ncol=3,
+  widths=c(1,4,4),
+  heights=c(1.5,3,3,3)
+)
+```
+
+```{r convergence-diagnostics-geweke, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
+#| fig-subcap: "P-Value Distribution of Geweke's Diagnostic Test for 100 Sample MCMC Draws"
+#| fig-cap: "Note.
+Images display the p-value distribution of Geweke's Convergence Diagnostic Test (as implemented in r package BART) applied to a random sample of 100 Random Markov Chains as generated using the BART model with larger-than-default values for Burn-In and Posterior Draws.
+Geweke's Test is used for diagnosing Markov Chain convergence via testing equality of means of the 10 and last 50 percent (default values) of the posterior draws."
+#| label: convergence-diagnostics-geweke
+# if needed add linebreaks in fig-cap via \\linebreak
+
+library(gridExtra)
+library(grid)
+library(png)
+
+# Load the images
+usk_gew_p0 <- rasterGrob(
+  png::readPNG("figures/Geweke_pvals/Ukr_Sold_killed_phat0_12k_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+usk_gew_p1 <- rasterGrob(
+  png::readPNG("figures/Geweke_pvals/Ukr_Sold_killed_phat1_25k_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+usk_gew_omce <- rasterGrob(
+  png::readPNG("figures/Geweke_pvals/Ukr_Sold_killed_omce_25k_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+sov_gew_p0 <- rasterGrob(
+  png::readPNG("figures/Geweke_pvals/Sovereignity_phat0_Full_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+sov_gew_p1 <- rasterGrob(
+  png::readPNG("figures/Geweke_pvals/Sovereignity_phat1_EU_NATO_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+sov_gew_omce <- rasterGrob(
+  png::readPNG("figures/Geweke_pvals/Sovereignity_omce_EU_NATO_large.png"), 
+  interpolate = TRUE, width=unit(1,"npc"), height=unit(1,"npc")
+)
+
+# Define column headers (centered)
+col_header1 <- textGrob("Attribute 1\nUkrainian Military Casualties", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
+col_subheader1 <- textGrob("Large Model\nBurn-In: 100 \nPosterior Draws: 1000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+
+col_header2 <- textGrob("Attribute 9\nSovereignity", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
+col_subheader2 <- textGrob("Large Model\nBurn-In: 100 \nPosterior Draws: 1000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+
+col_header1_combined <- arrangeGrob(col_header1, col_subheader1, ncol=1,
+                                    heights=c(unit(0.5,"lines"), unit(0.5,"lines")))
+col_header2_combined <- arrangeGrob(col_header2, col_subheader2, ncol=1,
+                                    heights=c(unit(0.5,"lines"), unit(0.5,"lines")))
+
+# Single grobs for rows with newline and adjusted lineheight
+row_header_combined_1 <- textGrob(paste0("p_hat_0\n",
+                                         "reference\nlevel"), x=0, hjust=0, 
+                                  gp=gpar(fontsize=10, lineheight=1))
+row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
+                                         "level of\ninterest"), x=0, hjust=0,
+                                  gp=gpar(fontsize=10, lineheight=1))
+row_header_combined_3 <- textGrob(paste0("omce_1\n",
+                                         "OMCE"), x=0, hjust=0,
+                                  gp=gpar(fontsize=10, lineheight=1))
+
+grid.arrange(
+  textGrob(""), col_header1_combined, col_header2_combined,
+  row_header_combined_1, usk_gew_p0, sov_gew_p0,
+  row_header_combined_2, usk_gew_p1, sov_gew_p1,
+  row_header_combined_3, usk_gew_omce, sov_gew_omce,
+  ncol=3,
+  widths=c(1,4,4),
+  heights=c(3,3,3,3)
+)
+```
+
+\newpage
+
 # References

### 2024-12-18 00_Custom_Source/custom_cjbart_imce_convdiag.R

@@ -328,7 +328,7 @@ rand_ind = sample(1:ncol(phat_0),size = 100, replace = F)
 z = gewekediag(phat_0[,rand_ind], frac1 = 0.1, frac2 = 0.5) 
 p_vals = pnorm(-1*abs(z$z),0,1) + (1-pnorm(abs(z$z),0,1))
 png(paste0("Manuscript files/figures/Geweke_pvals/",
-           "Ukr_Sold_killed_phat0_Full",
+           "Ukr_Sold_killed_phat0_12k",
            suffix, ".png"), 
     width = 800, height = 600)
 hist(p_vals, main = '') # cf. sample traceplots --> non convergence for most 
@@ -337,7 +337,7 @@ dev.off()
 
 # phat1
 png(paste0("Manuscript files/figures/Traceplots/",
-           "Ukr_Sold_killed_phat0_25k_1",
+           "Ukr_Sold_killed_phat1_25k_1",
            suffix, ".png"), 
     width = 800, height = 600)
 plot(phat_1[,1])
@@ -348,7 +348,7 @@ rand_ind = sample(1:ncol(phat_1),size = 100, replace = F)
 z = gewekediag(phat_1[,rand_ind], frac1 = 0.1, frac2 = 0.5) 
 p_vals = pnorm(-1*abs(z$z),0,1) + (1-pnorm(abs(z$z),0,1))
 png(paste0("Manuscript files/figures/Geweke_pvals/",
-           "Ukr_Sold_killed_phat1_Full",
+           "Ukr_Sold_killed_phat1_25k",
            suffix, ".png"), 
     width = 800, height = 600)
 hist(p_vals, main = '') # cf. sample traceplots --> non convergence for most 
@@ -368,7 +368,7 @@ rand_ind = sample(1:ncol(omce),size = 100, replace = F)
 z = gewekediag(omce[,rand_ind], frac1 = 0.1, frac2 = 0.5) 
 p_vals = pnorm(-1*abs(z$z),0,1) + (1-pnorm(abs(z$z),0,1))
 png(paste0("Manuscript files/figures/Geweke_pvals/",
-           "Ukr_Sold_killed_omce_Full",
+           "Ukr_Sold_killed_omce_25k",
            suffix, ".png"), 
     width = 800, height = 600)
 hist(p_vals, main = '') # cf. sample traceplots --> non convergence for most 
[…]

### 2024-12-18 00_Custom_Source/custom_cjbart_imce_convdiag.R
updated trace and geweke plots

@@ -316,7 +316,7 @@ png(paste0("Manuscript files/figures/Traceplots/",
            "Ukr_Sold_killed_phat0_12k_1",
            suffix, ".png"), 
     width = 800, height = 600)
-plot(phat_0[,1])
+plot(phat_0[,1], cex.lab=1.5, cex.axis = 1.8)
 dev.off()
 # use BART's geweke diagnostic
 # --> calculates a z-score test of equality of means for the first
@@ -331,7 +331,7 @@ png(paste0("Manuscript files/figures/Geweke_pvals/",
            "Ukr_Sold_killed_phat0_12k",
            suffix, ".png"), 
     width = 800, height = 600)
-hist(p_vals, main = '') # cf. sample traceplots --> non convergence for most 
+hist(p_vals, main = '', cex.lab=1.5, cex.axis = 1.8) # cf. sample traceplots --> non convergence for most 
 dev.off()
 
 
@@ -340,7 +340,7 @@ png(paste0("Manuscript files/figures/Traceplots/",
            "Ukr_Sold_killed_phat1_25k_1",
            suffix, ".png"), 
     width = 800, height = 600)
-plot(phat_1[,1])
+plot(phat_1[,1], cex.lab=1.5, cex.axis = 1.8)
 dev.off()
 # geweke
 set.seed(7)
@@ -351,7 +351,7 @@ png(paste0("Manuscript files/figures/Geweke_pvals/",
            "Ukr_Sold_killed_phat1_25k",
            suffix, ".png"), 
     width = 800, height = 600)
-hist(p_vals, main = '') # cf. sample traceplots --> non convergence for most 
+hist(p_vals, main = '', cex.lab=1.5, cex.axis = 1.8) # cf. sample traceplots --> non convergence for most 
 dev.off()
 
 # Sample OMCE 'Traceplot'
@@ -360,7 +360,7 @@ png(paste0("Manuscript files/figures/Traceplots/",
            "Ukr_Sold_killed_omce_25k_1",
            suffix, ".png"), 
     width = 800, height = 600)
-plot(omce[,1])
+plot(omce[,1], cex.lab=1.5, cex.axis = 1.8)
 dev.off()
 # geweke
 set.seed(7)
@@ -371,7 +371,7 @@ png(paste0("Manuscript files/figures/Geweke_pvals/",
            "Ukr_Sold_killed_omce_25k",
            suffix, ".png"), 
     width = 800, height = 600)
[…]

### 2024-12-18 00_Custom_Source/custom_cjbart_imce_convdiag.R
Updates to Plots

@@ -88,9 +88,10 @@
 #' *Insert TR: Set Arguments for IMCE dry-run to extract trace plots*
 data = cj_tidy[, vars_ext]
 keep_omce = TRUE
-# model = fit_cjbart_ext # standard model  
-model = fit_cjbart_ext_large 
-large = T
+model = fit_cjbart_ext # standard model  
+large = F
+# model = fit_cjbart_ext_large 
+# large = T
       # 'larger' model for longer Burn-In and More Draws
       # nskip = 2000 (vs. 250), ndraws = 5000 (vs. 1000)
 attribs = c("Sold_killed_UKR"

### 2024-12-18 Manuscript files/Manuscript.qmd
changes to manuscript

@@
 col_header2 <- textGrob("Large Model", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
-col_subheader2 <- textGrob("Burn-In: 1000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+col_subheader2 <- textGrob("Burn-In: 2000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
 
@@
 col_header1 <- textGrob("Attribute 1\nUkrainian Military Casualties", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
-col_subheader1 <- textGrob("Large Model\nBurn-In: 100 \nPosterior Draws: 1000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+col_subheader1 <- textGrob("Large Model\nBurn-In: 2000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
 
 col_header2 <- textGrob("Attribute 9\nSovereignity", x=0.5, hjust=0.5, gp=gpar(fontface="bold", fontsize=10))
-col_subheader2 <- textGrob("Large Model\nBurn-In: 100 \nPosterior Draws: 1000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
+col_subheader2 <- textGrob("Large Model\nBurn-In: 2000 \nPosterior Draws: 5000", x=0.5, hjust=0.5, gp=gpar(fontsize=8))
 

### 2024-12-19 1b_Analysis_cjbart.R
changes to repo folder structure and code cleaning

@@ -63,19 +63,7 @@ colnames(cj_tidy)[which(colnames(cj_tidy) %in% c(paste0("attr",1:9)))] <-
     "Polit_Self_Det_UKR")
 
 
-#####' *Select variables of interest for the 2 different models*
-# reduced set of covars 
-vars_red = c(
-  # General variables
-  'y', 'c_id', 'task',
-  # Attributes
-  "Sold_killed_UKR", "Sold_killed_RUS", "Civ_killed_UKR",
-  "Infra_Destr_UKR", "Perc_GDP_milit", "Perc_GDP_econ",
-  "Risk_Nuke", "Territ_Cession", "Polit_Self_Det_UKR", 
-  # Covariates
-  'Country', 'age', 'gender', 'leftright3'
-  )
-
+#####' *Select variables of interest*
 vars_ext = c(
   # General variables
   'y', 'c_id', 
@@ -93,27 +81,10 @@ vars_ext = c(
 
 
 
-#####' *Fit the models*
-### Fit the reduced model
-set.seed(13.9238239)
-
-# function has default seed 99 implented 
-fit_cjbart_red = cjbart(data = cj_tidy[, vars_red], 
-                        Y = "y",
-                        type = "choice", 
-                        id = "c_id", 
-                        round = "task", 
-                        use_round = TRUE, 
-                        cores = 4,
-                        seed = 99)
-
-# saveRDS(fit_cjbart_red, "1c_Model_Objects/2024-11-18_fit_cjbart_red_2.rds")
-fit_cjbart_red <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_red.rds")
-
-
-### Fit the extended model
+#####' *Fit the model*
+# function has default seed 99 implemented 
 # set.seed(123)
-fit_cjbart_ext_s123 = cjbart(data = cj_tidy[, vars_ext], 
+fit_cjbart_ext = cjbart(data = cj_tidy[, vars_ext], 
                         Y = "y",
                         # type = "choice", 
                         id = "c_id", 
@@ -122,16 +93,12 @@ fit_cjbart_ext_s123 = cjbart(data = cj_tidy[, vars_ext],
                         seed = 123,
                         cores = 4)
 
-
-
-# sNumber provides the seed, cNumber provides the cores used 
-# these 2 numbers determine the randomness in the BART tree building 
[…]

### 2024-12-19 1c_cjbart_robustness.R

@@ -64,7 +64,7 @@ colnames(cj_tidy)[which(colnames(cj_tidy) %in% c(paste0("attr",1:9)))] <-
 
 
 
-#####' *Select variables of interest for the 2 different models*
+#####' *Select variables of interest for the model*
 vars_ext = c(
   # General variables
   'y', 'c_id', 
@@ -87,7 +87,7 @@ no_of_cores = parallel::detectCores()
 no_iterations = 11:20 # be careful as the fit objects has ~1GB 
 
 # Set Seeds for the iterations
-# seeds = round(runif(20,1,1000),0)
+# seeds = round(runif(20,1,1000),0) # used to determine random seeds
 seeds = c(79, 27, 340, 508, 43,
           157, 886, 918, 70, 972,
           373, 960, 999, 826, 984,

### 2024-12-19 1c_cjbart_testscript.R

@@ -1,245 +1,0 @@
-# Re-Do the simulation of the paper
-rm(list = ls())
-simdat = function(n = 500, rounds = 5, profiles_per_round = 2){
-
-n = 500
-rounds = 5 
-profiles_per_round = 2
-obs = n*rounds*profiles_per_round
-
-  obs = n*rounds*profiles_per_round
-  
-  # Get profile attributes
-  a1 = sample(c('a','b'), 
-              obs, 
-              replace = T, 
-              prob = c(.5, .5))
-  a2 = sample(c('c','d'), 
-              obs, 
-              replace = T, 
-              prob = c(.5, .5))
-  a3 = sample(c('e','f'), 
-              obs, 
-              replace = T, 
-              prob = c(.5, .5))
-  
-  # Get the profile attribute dataframe
-  participants_full = rep(1:n, each = rounds*profiles_per_round)
-  rounds_full = rep(rep(1:rounds, each = profiles_per_round), n)
-  profiles_full = rep(1:profiles_per_round, n*rounds)
-  
-  # Get subject level covariates
-  c1_vec <- rbinom(n, 1, 0.5)          # Binary covariate for each user
-  c2_vec <- runif(n, -1, 1)
-  
-  # Repeat covariates to match the number of observations per user
-  c1_full <- rep(c1_vec, each = rounds * profiles_per_round)
-  c2_full <- rep(c2_vec, each = rounds * profiles_per_round)
-  
-  # Combine df
-  df = data.frame(participants_full,
-                  rounds_full,
-                  profiles_full,
-                  a1, a2, a3,
-                  c1_full, c2_full)
-  colnames(df) = c('user_id', 'round_id', 'profile_id', 
-                   'a1', 'a2', 'a3',
-                   'c1', 'c2')
-  
-  # Calculate Changes in Utilities
-  # df$delta_U1 = mapply(function(c1) 
-  #   ifelse(c1 == 1, rnorm(1,1,1), rnorm(1,-1,1)), df$c1)
-  # df$delta_U2 = mapply(function(c2) 
-  #   rnorm(1, mean = abs(c2 - 0.2), sd = 1), df$c2)
-  # df$delta_U3 = rnorm(obs,0,0.5)
-  
-  
-  # Calculate Changes in Utilities per user
-  # Generate delta_U1, delta_U2, delta_U3 for each user
[…]

### 2024-12-19 1e_cjbart_demo.R

@@ -1,28 +1,0 @@
-set.seed(89)
-library(ggplot2)
-library(cjbart)
-
-subjects <- 100
-rounds <- 5
-profiles <- 2
-obs <- subjects*rounds*profiles
-
-fake_data <- data.frame(A = sample(c("a1","a2","a3"), obs, replace = TRUE),
-                        B = sample(c("b1","b2","b3"), obs, replace = TRUE),
-                        C = sample(c("c1","c2","c3"), obs, replace = TRUE),
-                        D = sample(c("d1","d2","d3"), obs, replace = TRUE),
-                        E = sample(c("e1","e2","e3"), obs, replace = TRUE),
-                        
-                        covar1 = rep(runif(subjects, 0 ,1),
-                                     each = rounds),
-                        covar2 = rep(sample(c(1,0),
-                                            subjects,
-                                            replace = TRUE),
-                                     each = rounds),
-                        
-                        id1 = rep(1:subjects, each=rounds),
-                        stringsAsFactors = TRUE)
-
-fake_data$Y <- ifelse(fake_data$E == "e2",
-                      rbinom(obs, 1, fake_data$covar1),
-                      sample(c(0,1), obs, replace = TRUE))

### 2024-12-19 1f_OnlineReplication.R

@@ -1,104 +1,0 @@
-set.seed(seed)
-
-subjects = 500
-rounds = 5
-
-
-# Define individual-level utilities
-utilities <- data.frame(id = 1:subjects,
-                        c1 = rbinom(subjects, 1, 0.5),
-                        c2 = runif(subjects, -1,1)) %>% 
-  mutate(X1_1 = ifelse(c1 == 1, 
-                       rnorm(subjects, 1, sd = 1),
-                       rnorm(subjects, -1, sd = 1)),
-         X2_1 = rnorm(subjects, abs(c2-0.2), sd = 1),
-         X3_1 = rnorm(subjects, 0,sd = 0.5))
-
-# Use utilities to determine hypothetical conjoint behaviour
-conjoint_data <- data.frame(id = rep(1:subjects, each = rounds*2),
-                            round = rep(1:rounds, each = 2),
-                            profile = 1:2,
-                            X1 = rbinom(subjects*rounds*2, 1, 0.5),
-                            X2 = rbinom(subjects*rounds*2, 1, 0.5),
-                            X3 = rbinom(subjects*rounds*2, 1, 0.5)) %>% 
-  left_join(utilities, by = "id") %>% 
-  mutate(U = X1*X1_1 + X2*X2_1 + X3*X3_1 + rnorm(subjects*rounds*2, 0,0.0005)) %>% 
-  group_by(id, round) %>%
-  mutate(Y = ifelse(U == max(U),1,0)) %>% 
-  ungroup()
-
-# Mutate data for cleaner presentation
-train_data <- conjoint_data %>% select(id, X1, X2, X3, c1, c2, Y) %>% 
-  mutate(X1 = ifelse(X1 == 1, "A1: Binary heterogeneity (c1)","a"),
-         X2 = ifelse(X2 == 1, "A2: Interval heterogeneity (c2)","c"),
-         X3 = ifelse(X3 == 1, "A3: Random heterogeneity","e"))
-
-
-
-
-
-set.seed(89)
-
-# Function for simulating subject preferences and resulting conjoint data
-preference_sim <- function(subjects = 500, rounds = 5, seed = 89) {
-  
-  set.seed(seed)
-  
-  # Define individual-level utilities
-  utilities <- data.frame(id = 1:subjects,
-                          c1 = rbinom(subjects, 1, 0.5),
-                          c2 = runif(subjects, -1,1)) %>% 
-    mutate(X1_1 = ifelse(c1 == 1, 
[…]

### 2024-12-19 1g_cjbart_age_categorical.R

@@ -1,341 +1,0 @@
-################################################################################
-####### CJBART 
-################################################################################
-
-### Load Packages
-library(cjbart)
-library(haven)
-library(tidytext)
-library(dplyr)
-library(ggplot2)
-library(rpart)
-library(rpart.plot) # standard built-in plot function used in the paper
-
-### Set WD
-# setwd(dirname(rstudioapi::getSourceEditorContext()$path))
-
-### Load Data 
-cj_tidy <- readRDS("0_Ukraine_Conjoint_Data/cj_tidy.rds")
-
-# get additional covariate data 
-add_covars <- 
-  readRDS("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.Rds")
-# get additional covariate data --> same data different files types?
-add_covars2 <- 
-  haven::read_dta("0_Ukraine_Conjoint_Data/CJ_Ukraine_NewCovariates.dta")
-rm(add_covars2)
-
-
-### Join the add_covars with the cj_tidy data 
-# for this, create c_id (country_id) variable in add_covars
-add_covars$country_id <- paste0(add_covars$Country, 
-                                "_",
-                                add_covars$ID)
-# Remove the covars in add_covars that are already present in cj_tidy
-which(!colnames(add_covars) %in% colnames(cj_tidy))
-add_covars_new <- add_covars[,which(!colnames(add_covars) %in% 
-                                      colnames(cj_tidy))]
-
-# join the new covariate data
-cj_tidy <- merge(cj_tidy,
-                 add_covars_new,
-                 by.x = "c_id",
-                 by.y = "country_id", 
-                 all.x = T) # left join
-
-
-
-# Rename Attributes
-colnames(cj_tidy)[which(colnames(cj_tidy) %in% c(paste0("attr",1:9)))] <-
-  c("Sold_killed_UKR",
-    "Sold_killed_RUS",
-    "Civ_killed_UKR",
-    "Infra_Destr_UKR",
-    "Perc_GDP_milit",
-    "Perc_GDP_econ",
-    "Risk_Nuke",
-    "Territ_Cession",
-    "Polit_Self_Det_UKR")
-
-
-# Recode age to categoricals 
-# get age into 4 groups, <30, <=50, <=70, >70
-cj_tidy$age_cat <- ifelse(cj_tidy$age > 70, 4,
-                          ifelse(cj_tidy$age <= 70, 3,
[…]

### 2024-12-20 1b_Analysis_cjbart.R
Updates

@@ -94,8 +94,8 @@ fit_cjbart_ext = cjbart(data = cj_tidy[, vars_ext],
                         cores = 4)
 
 # sNumber provides the seed --> determines randomness in the BART tree growing 
-# saveRDS(fit_cjbart_ext, "1c_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
-fit_cjbart_ext <- readRDS("1c_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
+# saveRDS(fit_cjbart_ext, "1b_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
+fit_cjbart_ext <- readRDS("1b_Model_Objects/2024-11-18_fit_cjbart_ext.rds")
 
 
 #' *Fit model with larger (non-default) Burn-In/Draws for*
@@ -110,8 +110,8 @@ fit_cjbart_ext_large = cjbart(data = cj_tidy[, vars_ext],
                              nskip = 2000, # Burn-In instead of 100 (default)
                              ndpost = 5000, # Posterior Draws instead of 1000
                              cores = 4)
-# saveRDS(fit_cjbart_ext_large, "1c_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
-fit_cjbart_ext_large <- readRDS("1c_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
+# saveRDS(fit_cjbart_ext_large, "1b_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
+fit_cjbart_ext_large <- readRDS("1b_Model_Objects/2024-12-17_fit_cjbart_ext_large.rds")
 
 
 #' *Fit model with the custom as-if-non-unix cjbart function*
@@ -128,9 +128,9 @@ cfit_cjbart_es42_is123_v1 = cjbart_custom(data = cj_tidy[, vars_ext],
                              seed = 123, # returns warning --> no seed needed
                              cores = 4)
 # saveRDS(cfit_cjbart_es42_is123_v1,
-#         '1c_Model_Objects/2024-11-18_cfit_cjbart_es42_is123_v1.rds')
+#         '1b_Model_Objects/2024-11-18_cfit_cjbart_es42_is123_v1.rds')
 # cfit_cjbart_es42_is123_v1 = 
[…]

### 2024-12-20 1c_cjbart_robustness.R

@@ -109,7 +109,8 @@ for (iter in no_iterations){
                       seed = seeds[iter],
                       cores = no_of_cores)
   # save model 
-  model_name = paste0("1b1_objects/models/fit_cjbart_s",seeds[iter],'.rds')
+  model_name = paste0("1c_robustness_objects/models/fit_cjbart_s",
+                      seeds[iter],'.rds')
   saveRDS(fit_cjbart, model_name)
   
   print(paste('# Finished model fit', iter, 'of', length(no_iterations)))
@@ -141,7 +142,7 @@ for (iter in no_iterations){
                 alpha = 0.05,
                 cores = no_of_cores)
   # save amces 
-  amce_name = paste0("1b1_objects/amces/amces_s",seeds[iter],'.rds')
+  amce_name = paste0("1c_robustness_objects/amces/amces_s",seeds[iter],'.rds')
   saveRDS(amces, amce_name)
   
   print(paste('# Finished amces', iter, 'of', length(no_iterations)))
@@ -175,7 +176,7 @@ for (iter in no_iterations){
                 , cores = no_of_cores)
   
   # save imces 
-  imce_name = paste0("1b1_objects/imces/imces_s",seeds[iter],'.rds')
+  imce_name = paste0("1c_robustness_objects/imces/imces_s",seeds[iter],'.rds')
   saveRDS(imces, imce_name)
   
   print(paste('# Finished imces', iter, 'of', length(no_iterations)))
@@ -186,14 +187,14 @@ for (iter in no_iterations){
 }
 
 
-
+###' *Plot AMCE Variability across different Modeling Iterations*
 ### Compare the AMCEs across the different draws 
 # Load AMCEs
-amce_files = list.files('1b1_objects/amces/')
+amce_files = list.files('1c_robustness_objects/amces/')
 rm(amce_df)
 for (amce_file in amce_files){
   iter = which(amce_files %in% amce_file)
-  path = paste0('1b1_objects/amces/', amce_file)
+  path = paste0('1c_robustness_objects/amces/', amce_file)
   amce_temp = readRDS(path)
   amce_df_temp = data.frame(amce_temp$amces$attribute,
                             amce_temp$amces$level,
@@ -211,19 +212,8 @@ for (amce_file in amce_files){
   }
 }
 
-# Plot AMCEs of the iterations
-# amce_long <- amce_df %>%
-#   pivot_longer(
-#     cols = starts_with("iter_"), 
-#     names_to = "iteration", 
-#     values_to = "estimate",
-#     mutate(
[…]

### 2024-12-20 Manuscript files/Manuscript.qmd
Changes to manuscript
updates to manuscript

@@
 These AMCEs are supplemented with the AMCEs reported in the original article by @rudolph_citizens_2024, presented in @fig-amces-preprint.
+ <!-- Vielleicht den Plot aus Ihrem preprint einfach in den Appendix? -->
+ <!-- Ich habe den Plot auch nochmal selbst nachgebaut, falls wir das lieber wollen als einfach einen Screenshot zu nehmen -->
 
 ![Preprint AMCEs](figures/AMCEs_Original_Preprint.png){#fig-amces-preprint}
-
-<!-- Aproach to get the 2 figures on the same page...  -->
-<!-- ::: {.figure} -->
-<!--   ![AMCEs](figures/AMCEs_as_cjbart.png){#fig-amces width="100%"} -->
-
-<!--   ![Preprint AMCEs](figures/AMCEs_Original_Preprint.png){#fig-amces-preprint width="100%"} -->
-
-<!-- ::: -->
 
@@
 
-![Ext VarImps](figures/RF_VarImps_ext_v4.png){#fig-varimps-ext}
+![Ext VarImps](figures/RF_VarImps_ext.png){#fig-varimps-ext}
 
@@
 # Appendix
-## A1 Convergence Diagnostics - Attribute: Ukrainian Soldiers Killed
 
+## A1 AMCE Stability across Multiple Model Fitting Iterations
+
+::: {#amce-robustness style="text-align:left;"}
+![Stability of AMCE Point Estimates](figures/Robustness_AMCEs.png)
+Note. AMCE point estimates across 20 model fitting iterations using different seed values.\
+:::
+
+## A2 IMCE Stability across Multiple Model Fitting Iterations
+::: {#imce-robustness style="text-align:left;"}
+
+![Within-Individual Variability of IMCE Estimates](figures/Robustness_IMCEs.png)
+
+Note.
+Distribution of Within-Person IMCE Range across 20 model fitting iterations using different seed values.
+Each data point used to generate the empirical distribution describes the range of the IMCE values calculated for each individuals' IMCEs.
+:::
+
+## A3 Convergence Diagnostic Traceplot - Attribute: Ukrainian Soldiers Killed 
 ```{r convergence-diagnostics-usk, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
@@
 
-## A2 Convergence Diagnostics - Attribute: Sovereignity
+## A4 Convergence Diagnostic Traceplot - Attribute: Sovereignity
 
@@
 
+## A5 Convergence Diagnostics - Geweke's Diagnostic Criterion
+
 ```{r convergence-diagnostics-geweke, echo=FALSE, fig.align='center', fig.fullwidth=TRUE, out.width="100%"}
@@
 
+## A6 2-Cluster Solution of the FactorHet Models
+::: {#imce-robustness style="text-align:left;"}
+
+![FactorHet 2-Cluster Solution](figures/2024-12-06_FactorHet_2C_AMCEs.png)
+
+Note. AMCEs estimated using a FactorHet Model with a pre-set number of 2 clusters.
+:::
+
+## A6 3-Cluster Solution of the FactorHet Models
+::: {#imce-robustness style="text-align:left;"}
+
+![FactorHet 3-Cluster Solution](figures/2024-12-06_FactorHet_3C_AMCEs.png)
+
+Note. AMCEs estimated using a FactorHet Model with a pre-set number of 3 clusters.
+:::
+
 \newpage

### 2024-12-20 Manuscript files/Manuscript.qmd
ToC, LoF, LoT

@@
 author:
-  - name: Thomas Reiter
-    email: t.reiter@psy.lmu.de
-  - name: Philipp Sterner
-    email: p.sterner@psy.lmu.de
-format: pdf
+  - "Thomas Reiter"
+  - "Philipp Sterner"
+date: "2024-12-20"
+format:
+  pdf:
+    toc: true
+    lof: true
+    lot: true
+    title-page: true
 pdf-engine: xelatex
@@
   - \setlength{\extrarowheight}{2pt}
-  - \renewcommand{\arraystretch}{1.5}  # Adjust row spacing
+  - \renewcommand{\arraystretch}{1.5}
+  - \usepackage{etoolbox}
+  - \usepackage{footmisc}
+  - \pretocmd{\tableofcontents}{\clearpage\setcounter{page}{2}}{}{}
 floatsintext: yes
@@
 ---
+
+\newpage
+
+# Abstract
+
+This report explores the application of an advanced statistical model based on Bayesian additive regression trees [*cjbart*\; @robinson_how_2024] model, to analyze effect heterogeneity in high-dimensional conjoint analyses.
+The primary focus is on examining citizens' preferences from five NATO-member countries --- USA, UK, Germany, Italy, and France --- regarding support for Ukraine amid the Russian aggression. 
+Using conjoint experiment data involving over 10,000 participants, the report investigates how different attributes of support strategies influence decision-making.
+
+Following cjbart approach, we investigate different nested causal quantities.
+The study shows heterogeneity in attribute-level importance influenced by demographic covariates and political opinions, such as participants' nationality, gender, and political attitudes.
+This heterogeneity is further explored using interpretable machine learning techniques, such as variable importance measures of random forests and single decision tree partitioning.
+For example, UK participants differed to other countries with regard to selection probability changes, particularly regarding the impact of civilian casualties and risks of nuclear strikes. 
+Additionally, the attitudes toward general concessions gave rise to differences in selection probabilities.
+
+We discuss methodological caveats, such as robustness of the cjbart model.
+We highlight possible issues such as model convergence and the exploratory interpretation of the analysis. 
+The report concludes that cjbart is a powerful exploratory tool for high-dimensional conjoint data, offering nuanced insights into heterogeneous treatment effects. 
+These findings can be used to generate new hypotheses, informing subsequent confirmatory research and political theory.
+
+# Author Contribution
+
+Both authors contributed equally with regard to Formal Analysis, Methodology, Visualization, Writing - Original Draft Preparation, Writing - Review & Editing.
+
+\newpage
 
@@
 Arguably the most commonly estimated causal quantity in conjoint analyses is the *average marginal component effect* (AMCE).
-The AMCE is the effect of a specific attribute level of interest compared to another level of the same attribute, holding equal the joint distribution of all other attributes and averaged over this joint distribution as well as the sampling distribution from the population [@robinson_how_2024].
+The AMCE is the effect of a specific attribute level of interest compared to a reference level of the same attribute, holding equal the joint distribution of all other attributes and averaged over this joint distribution as well as the sampling distribution from the population [@robinson_how_2024].
 This quantity is estimable by regression models and provides us an effect of an attribute on the probability that a certain option (or profile) will be chosen.
-<!-- TR: compared to the probability of a baseline attribute level -->
 As the name AMCE suggests, this estimate is an average.
@@
 First, it is not clear how to a priori define the subgroups let alone how and where to include certain interactions.
-<!-- often lack of theory, risk of multiple testing issue -->
 If a continuous covariate age is included in the data, arbitrary splits into distinct groups are necessary.
 Potential interaction effects would have to be included manually with the likely chance to miss important ones.
-<!-- TR: with this issue increasing exponentially if subgroups are to be defined based on multiple covariates -->
 Needless to say, sample sizes in the subgroups are always smaller than in the whole sample as well, increasing the uncertainty in estimations.
-<!-- Vielleicht diesen allgemeinen high-dim part weiter nach oben zu den attribut levels? -->
-<!-- dann kann man das Fass mit der double high dimensionality hier aufmachen so nach dem Motto, dass die noch kleineren Subgruppen hier das Problem noch schlimmer machen? -->
 This leads to a second issue: conjoint data can quickly become high-dimensional due to many different pairings of different attribute levels (across attributes).
@@
 @robinson_how_2024 detail this estimation procedure using Bayesian additive regression trees (BART) but other appropriate models that can estimate this potentially complex functional relationship could be used as well.
-<!-- habe hier noch ein bisschen was dazu geschrieben  -->
 BART is a supervised learning model somewhat similar to a boosting procedure: across multiple iterations *B*, *M* small decision trees are trained subsequently, each one aiming to explain the residual variance of the outcome variable which was not explained by the $M-1$ previously grown trees.
@@
 Moreover, priors are placed on growing the trees to favor shallow trees and values in child nodes close to zero.
-<!-- auch noch was zu MCMC?  -->
 An advantage of BART is its robustness to the choice of hyperparameters (e.g., the number of individual trees) but they could be tuned if necessary, for example by cross-validation.
@@
 Following the nested structure of causal quantities outlines above, IMCEs are calculated by averaging the OMCEs for each individual.
-Specifically, the OMCE estimates from step 2 are summed and divided by $J \times K$, that is, the number of profiles times the number of rounds (which is the number of total observations).
-<!-- Sollen wir (wie im Paper) noch dazuschreiben, dass man basierend auf den Posterior Draws der OMCEs auch Credibility Intervals basteln kann, dann würde vielleicht auch der Bayesian Aspekt nochmal betont werden -->
+Specifically, the OMCE estimates from step 2 are summed and divided by $J \times K$, that is, the number of profiles times the number of rounds (which is the number of total observations per person).
+Because the OMCEs result from draws of a posterior distribution, credibility intervals for the IMCE can be constructed by using the empirical quantiles of this distribution.
 
@@
 Subsequently, variable importance measures (VIMPs) are derived to assess which covariates are driving the data partitioning.
-Briefly, the VIMPs are calculated by permuting the covariates (i.e., by introducing random noise to its values).
-<!-- nit: is random noise introduced (in terms of: added) or more the complete information on the variable destroyed by permuting all the values in X -->
+Briefly, the VIMPs are calculated by permuting the covariates (i.e., by perturbing its values).
 If predictions change noticeably, this is an indication that the covariate is important for predicting the outcome (i.e., IMCE distributions).
@@
 
-<!-- falls wir Platz sparen oder die Tabelle auf eine Seite bekommen wollen: Reference Category mit Asterisk oder so anzeichnen, dann haben wir nur 2 Spalten und weniger Zeilenumbrüche vermutlich -->
-<!-- Sollen wir hier noch ihre theoretischen 4 Cluster kurz reinschreiben?
-Also im Text oder in der Tabelle?
-Diese Aufteilung in Human Costs, Costs of Aid, Strategic Risks, Containment of Aggression (resolve)?
--->
 ```{r attributes, echo=FALSE}
@@
 
+All analyses including a reproducible can be found at \url{https://github.com/T-Reiter/Statistical_Consulting}.
+
 In @fig-amces we present the AMCEs estimated by averaging the IMCEs calculated using the cjbart model.
@@
 These AMCEs are supplemented with the AMCEs reported in the original article by @rudolph_citizens_2024, presented in @fig-amces-preprint.
- <!-- Vielleicht den Plot aus Ihrem preprint einfach in den Appendix? -->
- <!-- Ich habe den Plot auch nochmal selbst nachgebaut, falls wir das lieber wollen als einfach einen Screenshot zu nehmen -->
 
@@
 
-<!-- This is how it should work using quarto syntax but doesnt display captions properly and is weirdly centered -->
-<!-- ::::{#fig-group_label layout-ncol=2 layout-nrow=2} -->
-
-<!-- :::{#firstcol .column width="50%"} -->
-
-<!-- ![test1](figures/DecTree_ext_Civ_killed_Ukr_16k.png){#fig-civ_UKR} -->
-
-<!-- ![test2](figures/DecTree_ext_RUS_Sold_killed_100k.png){#fig-sold_RUS} -->
-<!-- ::: -->
-
-<!-- :::{#secondcol .column width="50%"} -->
-
-<!-- ![test3](figures/DecTree_ext_Risk_Nuke_Moderate.png){#fig-nuke} -->
-<!-- ![test4](figures/DecTree_ext_Territ_Cession_8perc.png){#fig-territ} -->
-<!-- ::: -->
-
-<!-- Exemplary Single Decision Tree Partitions for Predicting IMCEs -->
-<!-- :::: -->
-
 # Discussion
@@
 In order to reason about the absolute selection probability for a given attribute level using the associated AMCE, the absolute selection probability for the respective reference level must be known. 
-The often applied approach of calculating marginal means, provides exactly these marginalized absolute profile selection probabilities for different attribute levels. 
+The often applied approach of calculating marginal means provides exactly these marginalized absolute profile selection probabilities for different attribute levels. 
 This allows for straightforward reading off the absolute profile selection probabilities. 
@@
 Tuning hyperparameters would also be possible for the random forest when calculating variable importances.
-However, random forests have been shown to have good performance with default values of its hyperparameters (CITE), so we believe the focus should be on the hyperparameters of the upstream BART model.
+However, random forests have been shown to have good performance with default values of its hyperparameters [@strobl2009introduction], so we believe the focus should be on the hyperparameters of the upstream BART model.
 
@@
 Future research concerning FactorHet could develop model selection strategies, like information criteria, that are comparable across solutions with differing numbers of clusters and allow for a statistical decision.
+We complemented our analyses with an exemplary run of the FactorHet method.
+The results of this analysis (with a two- and three-cluster solution) can be found in Appendix A6.
 The other method, CRT by @ham_using_2024, is a statistical hypothesis testing approach based on conditional randomization tests.
@@
 Because our goal was to complement the existing analyses reported by @rudolph_citizens_2024 with a maximally exploratory approach, potentially informing future more confirmatory research, we found that cjbart best fits this purpose.
+
+## A Note on Robustness
+
+In the course of the project, our project partner and we noticed that solutions of cjbart differ (slightly) when rerunning the analysis (using different seeds or no prespecified seed on Windows machines).
+One possible reason was that the models failed to converge.
+To investigate this issue in more detail, we reran the analysis 20 times (i.e., estimating the model with BART and extracting the OMCEs/IMCEs/AMCEs).
+The results of this analysis can be found in appendices A1-5.
+In A1, the point estimates of AMCEs across the 20 iterations are displayed.
+As can be seen, AMCEs do not fluctuate noticeably.
+When looking at the ranges of IMCEs per person (A2), we observe that the IMCEs for some attributes fluctuate by around five to seven percentage points (most noticeably for attributes "Territorial cessions of Ukraine to Russia" and "How much political self-determination of Ukraine").
+Because we assumed that failed convergence might be an issue, we explored exemplary traceplots, showing the draws from the reference level and the level of interest posterior distribution (the difference of which corresponds to the OMCE).
+These traceplots are shown in A3 and A4.
+We can see that for none of the displayed chains, the values of draws converge to a stable value which in turn leads to fluctuations in OMCEs.
+This is the case for both the default sized model and a larger model with increased burn-in and posterior draws.
+Consequently, the model seems to have convergence issues.
+This finding is corroborated by the figure in A5, which shows the distribution of p-values for the Geweke's test [@geweke1992evaluating] whether the Markov chain converged (where the null hypothesis can be interpreted as convergence).
+Thus, we would be cautious to interpret IMCE results, especially for attributes which show a high range of person-specific IMCEs in A2.
 
@@
 With AMCE estimates similar to the primary analysis reported by @rudolph_citizens_2024, we believe that the newly developed cjbart-method provides a powerful tool to investigate effect heterogeneity in high-dimensional conjoint data.
-As with any new method, further methodological research is needed to assess to capabilities of the method under different conditions.
+As with any new method, further methodological research is needed to assess the capabilities of the method under different conditions.
 Most importantly, the results of cjbart should always be interpreted as what they are: an exploratory peek into underlying causal relations between covariates and individual preferences for certain attributes (i.e., IMCEs).
@@
 # Single grobs for rows with newline and adjusted lineheight
-row_header_combined_1 <- textGrob(paste0("p_hat_0\n",
+row_header_combined_1 <- textGrob(paste0("$p^{hat}_{0}$\n",
                                          "phat_0[,1]"), x=0, hjust=0, 

### 2024-12-20 Manuscript files/Manuscript.qmd
Title page

@@
 title: "What really matters (and to whom): Investigating heterogeneous effects in high-dimensional conjoint analyses"
+
 author:
-  - "Thomas Reiter"
-  - "Philipp Sterner"
+  - name: "Thomas Reiter"
+    affiliations: [stat-consulting]
+  - name: "Philipp Sterner"
+    affiliations: [stat-consulting]
+
+affiliations:
+  - id: stat-consulting
+    name: "Statistical Consulting, Master Statistics and Data Science, LMU Munich, Institute of Statistics"
+
+abstract: |
+  **Supervisor:** Prof. Dr. David Rügamer
+
+  **Project Partners:** Prof. Dr. Paul Thurner and Fabian Haggerty  
+  (Geschwister Scholl Institute of Political Science)
+
 date: "2024-12-20"
+
 format:
@@
     title-page: true
+    title-block-style: fancy
+    # Ensure the order: title, authors, affiliations, abstract, date
+    title-block-components: [title, author, affiliations, abstract, date]
+
 pdf-engine: xelatex
+
 header-includes:
@@
   - \pretocmd{\tableofcontents}{\clearpage\setcounter{page}{2}}{}{}
+
 floatsintext: yes

### 2024-12-23 Manuscript files/title.tex
Title page (to be included manually)

\documentclass{article}
\usepackage{graphicx}

\begin{document}

\begin{titlepage}
    \thispagestyle{empty} 
    \centering
    \vspace*{1 cm}

    {\LARGE \textbf{What Really Matters (and to Whom): Investigating Heterogeneous Effects in High-Dimensional Conjoint Analyses}}\\[1.5 cm]

    {\Large \textbf{Thomas Reiter} \quad \textbf{Philipp Sterner}}\\[1 cm]

    {\large Statistical Consulting, Master Statistics and Data Science\\
    LMU Munich, Institute of Statistics}\\[1.5 cm]

    {\large \textbf{Supervisor:} Prof. Dr. David Rügamer}\\[1 cm]

    {\large \textbf{Project Partners:} Prof. Dr. Paul Thurner and Fabian Haggerty\\
    (Geschwister-Scholl Institute of Political Science)}\\[2 cm]

    {\large December 23, 2024}

    \vfill
\end{titlepage}
\clearpage
\pagenumbering{arabic}

\end{document}

### 2025-01-02 Manuscript files/Manuscript.qmd
Title page and typos
Title page and figures

@@
 author:
-  - name: "Thomas Reiter"
-    affiliations: [stat-consulting]
-  - name: "Philipp Sterner"
-    affiliations: [stat-consulting]
+  - name: | 
+          | Thomas Reiter
+          | t.reiter@psy.lmu.de
 
-affiliations:
-  - id: stat-consulting
-    name: "Statistical Consulting, Master Statistics and Data Science, LMU Munich, Institute of Statistics"
+  - name: | 
+          | Philipp Sterner
+          | p.sterner@psy.lmu.de
+
+  - name: |
+          | Statistical Consulting
+          | Master Statistics and Data Science
+          | LMU Munich, Institute of Statistics
 
 abstract: |
-  **Supervisor:** Prof. Dr. David Rügamer
+  | **Supervisor:** 
+  | Prof. Dr. David Rügamer
 
-  **Project Partners:** Prof. Dr. Paul Thurner and Fabian Haggerty  
-  (Geschwister Scholl Institute of Political Science)
+  | **Project Partners:** 
+  | Prof. Dr. Paul Thurner and Fabian Haggerty 
+  | (Geschwister Scholl Institute of Political Science)
 
-date: "2024-12-20"
+  | **Date:** 
+  | Munich, January 2, 2024
 
@@
 
-All analyses including a reproducible can be found at \url{https://github.com/T-Reiter/Statistical_Consulting}.
+The code to reproduce the analyses can be found at \url{https://github.com/T-Reiter/Statistical_Consulting}.
 
@@
 #| label: convergence-diagnostics-usk
-# if needed add linebreaks in fig-cap via \\linebreak
 
@@
 
-# Single grobs for rows with newline and adjusted lineheight
-row_header_combined_1 <- textGrob(paste0("$p^{hat}_{0}$\n",
-                                         "phat_0[,1]"), x=0, hjust=0, 
-                                  gp=gpar(fontsize=10, lineheight=1))
-row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
-                                         "phat_0[,1]"), x=0, hjust=0,
-                                  gp=gpar(fontsize=10, lineheight=1))
-row_header_combined_3 <- textGrob(paste0("omce_1\n",
-                                         "omces[,1]"), x=0, hjust=0,
-                                  gp=gpar(fontsize=10, lineheight=1))
+# Single grobs for rows (using expressions for hats)
+row_header_combined_1 <- textGrob(
+  expression(paste(hat(p)[0], "[,1]")),
+  x=0, hjust=0, 
+  gp=gpar(fontsize=10, lineheight=1)
+)
+row_header_combined_2 <- textGrob(
+  expression(paste(hat(p)[1], "[,1]")),
+  x=0, hjust=0,
+  gp=gpar(fontsize=10, lineheight=1)
+)
+row_header_combined_3 <- textGrob(
+  paste0("omces[,1]"), 
+  x=0, hjust=0,
+  gp=gpar(fontsize=10, lineheight=1)
+)
 
@@
 # Single grobs for rows with newline and adjusted lineheight
-row_header_combined_1 <- textGrob(paste0("p_hat_0\n",
-                                         "phat_0[,1]"), x=0, hjust=0, 
-                                  gp=gpar(fontsize=10, lineheight=1))
-row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
-                                         "phat_0[,1]"), x=0, hjust=0,
-                                  gp=gpar(fontsize=10, lineheight=1))
-row_header_combined_3 <- textGrob(paste0("omce_1\n",
-                                         "omces[,1]"), x=0, hjust=0,
-                                  gp=gpar(fontsize=10, lineheight=1))
+row_header_combined_1 <- textGrob(
+  expression(paste(hat(p)[0], "[,1]")),
+  x=0, hjust=0, 
+  gp=gpar(fontsize=10, lineheight=1)
+)
+row_header_combined_2 <- textGrob(
+  expression(paste(hat(p)[1], "[,1]")),
+  x=0, hjust=0,
+  gp=gpar(fontsize=10, lineheight=1)
+)
+row_header_combined_3 <- textGrob(
+  paste0("omces[,1]"), 
+  x=0, hjust=0,
+  gp=gpar(fontsize=10, lineheight=1)
+)
 
@@
 # Single grobs for rows with newline and adjusted lineheight
-row_header_combined_1 <- textGrob(paste0("p_hat_0\n",
-                                         "reference\nlevel"), x=0, hjust=0, 
-                                  gp=gpar(fontsize=10, lineheight=1))
-row_header_combined_2 <- textGrob(paste0("p_hat_1\n",
-                                         "level of\ninterest"), x=0, hjust=0,
-                                  gp=gpar(fontsize=10, lineheight=1))
-row_header_combined_3 <- textGrob(paste0("omce_1\n",
-                                         "OMCE"), x=0, hjust=0,
-                                  gp=gpar(fontsize=10, lineheight=1))
+row_header_combined_1 <- textGrob(
+  expression(
+    atop(
+      paste(hat(p)[0], "[,1]"),
+      "reference"
+    )
+  ),
+  x = 0, hjust = 0,
+  gp = gpar(fontsize = 10, lineheight = 1)
+)
+row_header_combined_2 <- textGrob(
+  expression(
+    atop(
+      paste(hat(p)[1], "[,1]"),
+      "interest"
+    )
+  ),
+  x = 0, hjust = 0,
+  gp = gpar(fontsize = 10, lineheight = 1)
+)
+row_header_combined_3 <- textGrob(
+  expression(
+    atop(
+      paste("omces[,1]"),
+      "OMCE"
+    )
+  ),
+  x = 0, hjust = 0,
+  gp = gpar(fontsize = 10, lineheight = 1)
+)
 
